### 2020-12-06 paper/main.tex
first commit of the text; contains the state of the paper so far; many contributions from msv and hogg

% to-do
% -----
% - Audit for the use of "points" and "locations" and "data" to make sure all is consistent. The ts are locations, the ys are data.
% - Audit for use of the words "fit" and "prediction" and "model". All okay?
% - Audit for use of \, as the multiply operator? Fix the kerning around the ^\top items?
% - Audit for design matrix, feature matrix, and so on. We should mention design matrix but stick with feature matrix as our terminology.
% - Audit for hyphens in under-parameterization and re-weighting and so on? Hyphenated words or single words? Make decisions and stick to them.
% - Needs a bibliography; should we use bibtex?
% - Add acknowledgements: Sam Roweis (deceased), Dan Foreman-Mackey (Flatiron), Teresa Huang (JHU), Rachel Ward (UT Austin), Bernhard Sch\"olkopf (MPI-IS); who else??

\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}

% Price-Whelan's figure hacks
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{shadows}
\definecolor{captiongray}{HTML}{555555}
\mdfsetup{%
  innertopmargin=2ex,
  innerbottommargin=1.8ex,
  linecolor=captiongray,
  linewidth=0.5pt,
  roundcorner=5pt,
  shadow=true,
  shadowcolor=black!05,
  shadowsize=4pt
}

% Hogg's issues
\setlength{\topmargin}{-0.40in}
\setlength{\headsep}{4ex}
\setlength{\textheight}{9.20in}
\setlength{\oddsidemargin}{-0.20in}
\setlength{\textwidth}{5.00in}
\setlength{\parindent}{0.18in}
\pagestyle{myheadings}
\markright{\textcolor{gray}{\textsf{\upshape Fitting very flexible models / Hogg \& Villar}}}
\frenchspacing\sloppy\sloppypar\raggedbottom

% Math operators and definitions
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\DeclareMathOperator{\FT}{FT}

% text definitions
\newcommand{\documentname}{\textsl{Note}}
\newcommand{\sectionname}{Section}
\newcommand{\foreign}[1]{\textsl{#1}}

\begin{document}\thispagestyle{plain}

\section*{\raggedright Fitting very flexible models: Linear regression with large numbers of parameters\footnote{Hello world?}}

\noindent
\textbf{David W. Hogg} \\
\textsl{\footnotesize Flatiron Institute, a division of the Simons Foundation \\
Center for Cosmology and Particle Physics, Dept. Physics, New York University \\
Center for Data Science, New York University \\
Max-Planck-Institut f\"ur Astronomie, Heidelberg}

\medskip
\noindent
\textbf{Soledad Villar} \\
\textsl{\footnotesize Department of Applied Mathematics \& Statistics, Johns Hopkins University \\
Mathematical Institute for Data Science, Johns Hopkins University}

\medskip
\noindent
2020 December

\paragraph{Abstract:} There are many uses for linear fitting; the context we consider here is interpolation and denoising of data, as (for example) when you have calibration data and you want to fit a smooth, flexible function to those data.
Or you want to fit a flexible function to de-trend a time series or normalize a spectrum.
In these contexts, investigators often choose a polynomial basis, or a Fourier basis, or wavelets, or something equally general.
They also choose an order, or number of basis functions to fit, and (often) some kind of regularization.
Here we discuss how this basis-function fitting is done, with ordinary least squares and extensions thereof.
We emphasize that it is often valuable to choose \emph{far more parameters than data points}, despite folk rules to the contrary.
It is even possible to take the limit of infinite parameters, at which, if the basis and regularization are chosen correctly, the least-squares fit becomes the mean of a Gaussian process (or, equivalently, a Wiener filter or kriging).
Although there are often good fits with small numbers of parameters and also with very large numbers of parameters, the dangerous regime for linear fitting is when the number of parameters is comparable to the number of data points (the double-descent or peaking-phenomenon regime); we discuss this problem and how to ameliorate or avoid it.

\section{Introduction}

In contexts in which we want to fit a flexible function to data, for interpolation or denoising, we often perform linear fitting in a generic basis, such as polynomials, fourier modes, wavelets, or spherical harmonics.
This kind of linear fitting arises in astronomy when, for example, we want to calibrate the relationship between wavelength and position on the detector in a spectrograph:
We have noisy measurements of calibration data and we want to fit a smooth function of position that de-noises and interpolates the calibration data.
It also arises when we want to make a data-driven interpolation, extrapolation, or local averaging of data, as with light-curve detrending, continuum estimation, and interpolation or extrapolation of instrument housekeeping (or other) data.

When faced with problems of this kind, investigators have three general kinds of choices that they have to make:
They have to choose the basis in which they are working (Fourier, polynomial, wavelet, etc.).
They have to choose to what order they extend the basis---that is, how many components to use in the fit.
And they have to decide how (or whether) to regularize the fit, or discourage fit coefficients from getting out of line when the data are noisy or the basis functions are close to (or strictly) degenerate.
In what follows, we will discuss all three of these kinds of choices.

If you have encountered and solved problems like these, you have made these three kinds of choices (sometimes implcitly).
The second choice---about the number of coefficients to fit---is usually made heuristically, and often subject to the strongly believed opinion that you \emph{must have fewer parameters than data points}.
Here we are going to show that this folk rule is not valid; you can go to extremely large numbers of coefficients without trouble.
But like most folk rules, it has a strong basis in reality: There are extremely bad choices possible for the number of coefficients, and especially when the number of parameters is close or comparable to the number of data points.
As we will discuss below, these choices ought to be avoided, or made with care.

In many cases the third kind of choice---about regularization---is made implicitly, not explicitly.
Here we are going to emphasize this choice and its importance, and its value in improving your results.

Alternatively, if you are unhappy with the three choices of basis, and order, and regularization, you might decide to avoid such decisions and go fully \emph{non-parametric}:
Instead of fitting a basis expansion, you can use a strict interpolator (like a cubic spline), or you can fit a Gaussian process to your data.
Here we will show that the choice of any Gaussian process kernel function is equivalent to choosing a basis and a regularization and letting the number of fit components go to infinity (in a certain way).
That is, going non-parametric doesn't really get you out of making these choices.
It just makes these choices more implicit.
And it is a pleasure to note that any time you have gone non-parametric you have implicitly chosen to use a basis with way more fit parameters than data points!
The fact that non-parametrics work so well is strong evidence against the folk rule about the number of parameters needing to be less than the number of data points.

Fundamentally the assumption or setting in what follows will be that you care about predicting new data or interpolating the data, but you explicitly don't care about the parameters of the fit or the weights of the basis functions \foreign{per se}.
In this setting there are no important meanings to the components of the model.
That is---for us---only the data exist.
The details of the model are just choices that permit high-quality interpolations and predictions.

In some contexts you have strong beliefs about the noise affecting your measurements. In other cases you don't.
In some cases you have strong reasons to use a particular basis.
In other cases you don't.
The differences in these beliefs and the differences in your objectives will change what methods you choose and how you use and analyze them.
We'll try to come back to these important \emph{subjective} aspects of regression as we go.

\section{\raggedright Standard linear fitting: Ordinary least squares with a feature embedding}

Our setup will be that there are $n$ scalar data points $y_i$.
Each of these data points has an associated coordinate or location $t_i$.
This location $t_i$ could be thought of as a time at which the data point was taken, or a position, or it can be a higher dimensional vector or blob of housekeeping data associated with the data point.
Critically, we are going to imagine that the $t_i$ are known very well (not very uncertain or noisy), while the $y_i$ are possibly very uncertain or noisy measurements.
We'll return to these assumptions at the end.

We are going to fit these data $y_i$ with a linear sum of $p$ basis functions $g_j(t)$. These basis functions are functions of the coordinates $t$. That is, our implicit generative model is
\begin{equation}
    y_i = \sum_{j=1}^p \beta_j\,g_j(t_i) + \mathrm{noise}
    ~,
\end{equation}
where the $p$ values $\beta_j$ are parameters or coefficients of the linear fit. We can assemble the evaluations of the $p$ functions $g_j(t)$ at the $n$ data coordinates $t_i$ into a $n\times p$ design matrix or feature matrix $X$ such that
\begin{equation}
    [X]_{ij} = g_j(t_i)
    ~.
\end{equation}
The transformation of the $n$ locations $t_i$ into a $n\times p$ matrix $X$ is the opposite of a dimensionality reduction.
It is called variously a \emph{feature map} or a \emph{feature embedding}.
We like ``embedding'' because it (almost always) raises the dimensionality of the locations $t$ into the $p$-dimensional space of the rows of $X$.

For a concrete example, one common choice is to make the feature embedding functions $g_j()$ terms in a Fourier series
\begin{align}\label{eq:basis}
    g_j(t) &= \left\{\begin{array}{ll}
            \cos\omega_j\,t & \mbox{for $j$ odd} \\
            \sin\omega_j\,t & \mbox{for $j$ even}\end{array}\right.
    \\
    \omega_j &= \frac{\pi}{T}\,\floor{\frac{j}{2}}
    ~,
\end{align}
where $T$ is a (large) length-scale in the coordinate space ($t$ space) and $\floor{j/2}$ indicates the floor of $j/2$ (integer division).
Example functions $g_j(t)$ from this basis are shown in \figurename~\ref{fig:basis}.
Alternative common choices would be to make the embedding fumctions $g_j()$ polynomials or other kinds of ordered basis functions, such as wavelets or spherical harmonics (the latter if, say, the $t_i$ are positions on the sphere).
\begin{figure}[t]
    \begin{mdframed}
    \caption{Examples of basis functions $g_j(t)$ from the basis given in equation~(\ref{eq:basis}). This basis was constructed with length-scale parameter $T=3$. The wavelength in the location space decreases, and the frequency increases, with index $j$.}
    \label{fig:basis}
    \end{mdframed}
\end{figure}

The idea of least-squares fitting is that the ``best'' values of the parameters $\beta_j$ are the values that minimize the sum of squares of the differences between the data and the linear combination of features:
\begin{equation}\label{eq:opt1}
    \hat{\beta} = \arg\min_\beta \|Y - X\,\beta\|_2^2
    ~,
\end{equation}
where $\hat{\beta}$ is the $p$-vector (column vector) of the $p$ best-fit values $\hat{\beta}_j$ of the parameters $\beta_j$, and $\|q\|_2^2$ denotes the squared L2-norm, or the \emph{sum of squares} of the components of $q$
\begin{equation}
    \|q\|_2^2 \equiv q^\top\,q
    ~.
\end{equation}
This optimization objective (\ref{eq:opt1}) is convex and the optimization problem has a solution in closed form as long as the number of parameters (and features) $p$ is less than the number of training points $n$ (and the matrix $X^\top X$ is invertible):
\begin{equation}
    \hat{\beta} = (X^\top\,X)^{-1}\,X^\top\,Y
    ~.
\end{equation}
We will treat the case in which the matrix is not invertible below.
When the investigator knows uncertainties on the training data points $y_i$, this expression will change a bit; we begin to discuss that in the next \sectionname.

But recall our setting:
We are using the linear fit to interpolate the data, or de-noise the data, or predict new data.
In these contexts, we don't care about the parameter vector $\hat{\beta}$ itself.
We care only about the predictions at a set of new ``test'' locations $t_\ast$, which will usually be different from the training locations $t_j$
From the new test times $t_\ast$ we create the test feature matrix $X_\ast$ (by the same feature embedding functions $g_j(t)$).
The prediction $\hat{Y}_\ast$ for the $y$ values at the test locations $t_\ast$ becomes
\begin{equation}\label{eq:OLS}
    \hat{Y}_\ast = X_\ast\,(X^\top\,X)^{-1}\,X^\top\,Y
    ~.
\end{equation}
Examples of OLS applied to some toy data are shown in \figurename~\ref{fig:ols1}.
This form (\ref{eq:OLS}) of the prediction of new test data is called ordinary least squares (OLS). It has many good properties, some of which are encoded in the Gauss--Markov theorem.
SOLEDAD: PUT WORDS HERE ABOUT WHAT IS PROMISED BY GAUSS--MARKOV. ALSO: REFERENCE?
\begin{figure}[t]
    \begin{mdframed}
    \caption{Ordinary least-squares (OLS) fits (continuous lines) to a set of example data points (black dots). Fits are shown for different values of the number of basis functions $p$; there are $n=23$ data points. The data points $y_i$ were generated using a function that does not reside in the function space spanned by the basis. Here the $X_\ast$ matrices used in the predictions $\hat{Y}_\ast$ were generated from a fine grid of points in the location coordinate $t$; the plots of the fine grid of predictions are the continuous lines. The fits with larger $p$ have more flexibility to fit the data than the fit with $p=3$, but the fit at the highest $p$ shows evidence of over-fitting.}
    \label{fig:ols1}
    \end{mdframed}
\end{figure}

\section{Discussion and extensions of OLS}

The prediction (\ref{eq:OLS}) when $p<n$ (the under-paraemeterized or traditional regime) is \emph{affine invariant} in that $p$-dimensional rotations or rescalings of the rectangular $X$ design matrix do not affect predictions.
That is, if $R$ is an invertible $p\times p$ matrix, the prediction using $X'\leftarrow X\,R$ will be identical to the prediction using the original $X$.
This affine invariance will return in a different form in the over-parameterized regime, below.

Although the OLS prediction (\ref{eq:OLS}) is affine invariant with respect to $p$-dimensional transformations, it is \emph{not} affine invariant with respect to $n$-dimensional transformations, such as a re-weighting of the input data. Indeed, if you know weights or inverse variances for your data points, conceptually you can put them into a weight matrix $C^{-1}$ (written this way to emphasize that reweighting is usually inverse-variance weighting) and write
\begin{equation}
    \hat{Y}_\ast = X_\ast\,(X^\top\,C^{-1}\,X)^{-1}\,X^\top\,C^{-1}\,Y
    ~,
\end{equation}
where the weight matrix $C^{-1}$ is $n\times n$ (and often diagonal in standard applications). This form of least squares is called \emph{weighted least squares} (WLS) because of the data weighting (not to be confused with \emph{feature} weighting, to appear below).
It is also called chi-squared fitting because it optimizes the scalar objective commonly called chi-squared:
\begin{equation}
    \chi^2 = (Y - X\,\beta)^\top\,C^{-1}\,(Y - X\,\beta)
    ~.
\end{equation}
(If that isn't obviously chi-squared to you, recall that $C^{-1}$ is often diagonal and has the inverses of the squares of the data uncertainties on that diagonal.)
In \figurename~\ref{fig:wls} a comparison of OLS and WLS is shown, for a case of non-trivial data weights, where the data weights are set to be the inverse squares of individual data-point uncertainties.
\begin{figure}[t]
    \begin{mdframed}
    \caption{Comparison of ordinary least-squares (OLS) and weighted least-squares (WLS) fits (continuous lines) to the example data (black dots). In order to illustrate the differences, we assigned non-trivial error bars to the data. The error bars are ignored in the OLS fit, but in the WLS fit, the weight matrix $C^{-1}$ is diagonal with the diagonal entries set to the inverses of the squares of those error bars. The WLS fit ``pays less attention to'' the points on the left with the largest error bars.}
    \label{fig:wls}
    \end{mdframed}
\end{figure}

We will say more about noisy data and the propagation of uncertainties below in \sectionname~\ref{sec:uncertainty}.
It might be crossing your mind that there are uncertainties not just in the data points $y_i$, but also often in the \emph{locations} $t_i$ of the data points as well. It turns out that taking the latter into account is a much harder problem; we return to this also in \sectionname~\ref{sec:uncertainty} (HOGG: DO WE OR IS IT JUST IN THE DISCUSSION??).

It is common to include a regularization that discourages the fit from making use of large amplitudes $\beta_j$.
There are many options, but the simplest is ridge regression (or Tikhonov regularization or L2 regularization), which looks like
\begin{equation}
    \hat{\beta} = \arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\beta\|_2^2
    ~,
\end{equation}
where $\lambda>0$ is a regularization parameter that penalizes large values for elements $\beta_j$ of the parameter vector.
This optimization is also convex.
The ridge-regularized prediction for new data looks like
\begin{equation}
    \hat{Y}_\ast = X_\ast\,(X^\top\,X + \lambda\,I)^{-1}\,X^\top\,Y
    ~,
\end{equation}
where $I$ is the $p\times p$ identity.
In the language of Bayesian inference, $\lambda$ can be seen as a prior variance for the parameters $\beta_j$.
The salutary effect of the ridge regularization is shown in \figurename~\ref{fig:ridge}.
\begin{figure}[t]
    \begin{mdframed}
    \caption{Comparison of ordinary least-squares (OLS) and ridge-regression fits (continuous lines) to the example data (black dots). In order to illustrate the differences, we chose the $p=21$-parameter fit, which shows evidence of over-fitting at the edges of the fit range. The regularized fit looks more sensible, though it fits the individual data points less precisely. The choice of regularization parameter $\lambda$ matters; here we used $\lambda=0.1$ (chosen arbitrarily).}
    \label{fig:ridge}
    \end{mdframed}
\end{figure}

The ridge brings with it a choice: How to set the hyper-parameter $\lambda$?
We generally recommend cross-validation, to be discussed below in \sectionname~\ref{sec:dd}.
Ridge regression is not affine invariant in the sense that the standard OLS prediction (\ref{eq:OLS}) is; that is, the effect of the regularization depends on the amplitudes and linear combinations of features placed in the feature matrix.
This will become important later when we consider feature weights below.
It is also case that the regularization need not be proportional to the identity matrix; in principle any positive definite matrix $\Lambda$ could be used in place of $\lambda\,I$; this makes sense to consider when you have detailed prior beliefs about all the parameters $\beta_j$ or if those parameters are measured with different units (say).

HOGG: Connect here to the Gaussian product refactor note.

You can combine both the point weighting from WLS and the generalized ridge regression into a weighted ridge that looks like
\begin{equation}
    \hat{Y}_\ast = X_\ast\,(X^\top\,C^{-1}\,X + \Lambda)^{-1}\,X^\top\,C^{-1}\,Y
    ~.
\end{equation}
This form has good properties for many real-world physics applications, where data-point error bars are often known, and functions are often expected to be smooth.
HOGG: Say something about units here, to set up a subsequent discussion.

\section{\raggedright Over-parameterization}

We are taught folklore, at a young age, that we can never fit for more parameters than we have data. That is, we can never work at $p>n$.
This isn't true!
The only limits on inference are given by information theory, and information theory makes no reference to the \emph{number} of anything, parameters or data.
But it is true that the $p>n$ regime is indeed strange!
In the over-parameterized case, there are many settings of the parameters $\beta_j$ that will literally zero out the differences between the data $Y$ and the linear prediction $X\,\beta$.
The OLS solution, in this case, is defined (somewhat arbitrarily) to be the minimum-norm parameter vector $\beta$ that interpolates the data:
\begin{equation}
    \hat{\beta} = \arg\min_\beta \|\beta\|_2^2 ~~\mbox{subject to}~~ Y = X\,\beta
    ~.
\end{equation}
Technically this formulation depends on an additional assumption that the feature matrix $X$ is full rank or that the data $Y$ lie in the subspace spanned by $X$.
This is true almost always when $p>n$.
This optimization is again convex and has a unique solution, although that solution will depend on feature weights that we discuss in a moment.
When the investigator knows uncertainties on the training data points $y_i$, this expression will change a bit; we return to that in the HOGG WHICH \sectionname\ (HOGG: DO WE?).
The under-parameterized and over-parameterized optimizations can be unified into one form by considering the limit of light L2 regularization:
\begin{equation}
    \hat{\beta} = \lim_{\lambda\rightarrow 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\beta\|_2^2\right]
    ~;
\end{equation}
in the limit, this delivers the min-norm OLS solution.

In the over-parameterized case ($p>n$), the prediction looks like
\begin{equation}\label{eq:OLS2}
    \hat{Y}_\ast = X_\ast\,X^\top\,(X\,X^\top)^{-1}\,Y
    ~,
\end{equation}
provided that $X\,X^\top$ is invertible (which will usually be the case).
Like (\ref{eq:OLS}), this prediction is \emph{also} called ordinary least squares (OLS), or sometimes ``min-norm least-squares'' to emphasize the degeneracy-breaking choice.
Examples of OLS fits in the over-parameterized regime are shown in \figurename~\ref{fig:ols2}.
Note that the fits with different numbers of parameters $p$ lead to very different predictions, but they all go through the data points exactly.
\begin{figure}[t]
    \begin{mdframed}
    \caption{Ordinary least-squares (OLS) or min-norm least-squares fits (continuous lines) to a set of example data points (black dots), but now for a few over-parameterized cases. There are $n=23$ data points. As in \figurename~\ref{fig:ols1}, the data points $y_i$ were generated using a function that does not precisely reside in the function space spanned by the basis. The three fits are very different, but they all go through all the data points exactly. As $p$ gets large, the fit function approaches $y=0$ almost everywhere; this is a consequence of Parseval's Theorem (see text).}
    \label{fig:ols2}
    \end{mdframed}
\end{figure}

It is slightly off-topic to notice that in \figurename~\ref{fig:ols2}, as $p$ gets very large, the OLS solution approaches $y=0$ everywhere that it can.
This behavior is a direct consequence of Parseval's Theorem (CITE), which states that the Fourier transform is unitary.
This means that the integral over frequency of the square of the Fourier transform is equal (up to a factor of $2\pi$) to the integral over location of the square of the original function.
Thus the min-norm solution delivered by OLS, which chooses the interpolating function that minimizes the squares of the component amplitudes in the Fourier basis used to make \figurename~\ref{fig:ols2} will also choose the interpolating function that minimizes the square of the value of the function.
It will try to stay as close to $y=0$ as possible.
SOLEDAD: CHECK WORDING.

The two equations for OLS---(\ref{eq:OLS}) and (\ref{eq:OLS2})---can be unified into one equation (and also generalized to handle non-invertible matrices $X^\top X$ and $X\,X^\top$) if we define the pseudo-inverse $X^\dagger$:
\begin{equation}\label{eq:OLS3}
    \hat{Y}_\ast = X_\ast\,X^\dagger\,Y
    ~,
\end{equation}
where the pseudo-inverse is the matrix made by inverting the singular values and transposing.
That is, if the singular-value decomposition (SVD) of $X$ is $U\,S\,V$, with $S$ diagonal, the SVD of $X^\dagger$ is $V^\top\,S_{\text{nonzero}}^{-1}\,U^\top$, where $S_{\text{nonzero}}^{-1}$ contains the inverses of the non-zero elements of $S$, and zeros where $S$ is zero. SOLEDAD IS THERE A BETTER NOTATION OR EXPLANATION HERE? SHOULD I BREAK THIS OUT INTO EQUATIONS? (SOLEDAD SAYS: Define pseudo-inverse for a diagonal matrix and then use SVD and reduce to the previously stated definition.)
This pseudo-inverse form (\ref{eq:OLS3}) of OLS is extremely general: It works for both the $p\le n$ and $p>n$ cases, and it works when the $X\,X^\top$ or $X^\top\,X$ matrices are not invertible.
There can be significant numerical issues with implementing the pseudo-inverse; we comment on those in \sectionname~\ref{sec:implementation}.

\section{\raggedright Feature weighting}\label{sec:fwols}

The OLS prediction for $p>n$ is \emph{not} affine invariant with respect to $p$-dimensional rotations or rescalings.
That is, rotations and scalings in the feature space \emph{will} affect predictions.
It behooves us to re-scale the features (the $p$ $n$-vectors of the design matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features.
We can encode these feature weights in a $p\times p$ diagonal weight matrix $\Lambda^{-1}$ and the prediction becomes
\begin{equation}
    \hat{Y}_\ast = X_\ast\,\Lambda^{-1}\,X^\top\,(X\,\Lambda^{-1}\,X^\top)^{-1}\,Y
\end{equation}
This can be seen as the prediction for new data resulting from the following optimization:
\begin{equation}
    \hat{\beta} = \arg\min_\beta \|\Lambda^{1/2}\,\beta\|_2^2 ~~\mbox{subject to}~~ Y = X\,\beta
    ~,
\end{equation}
which can also be written as
\begin{equation}
    \hat{\beta} = \lim_{\lambda\rightarrow 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\Lambda^{1/2}\beta\|_2^2\right]
    ~.
\end{equation}
This optimization penalizes more strongly the parameters $\beta_j$ corresponding to features $g_j()$ with larger values of $[\Lambda^{1/2}]_{jj}$.

HOGG: Remind the readers who prefer obvious scalar forms that $\|\Lambda^{-1/2}\,\beta\|_2^2 = \beta^\top\,\Lambda^{-1}\,\beta$. That's a gauge-invariant object (if $\beta$ and $\Lambda$ are gauge-invariant objects themselves).

In the Fourier case this re-weighting can be very straightforward: Each of the $p$ embedding functions $g_j(t)$ has an associated frequency $\omega_j$; we can control the fit by weighting the $j$ features by a function $f(\omega)$.
For demonstration purposes, we can choose
\begin{equation}\label{eq:f}
    f(\omega) = \frac{1}{s^2\,\omega^2 + 1}
    ~,
\end{equation}
where $s$ is a hyper-parameter controlling the (inverse) width of the weighting function in frequency space, and the frequency input will be $\omega_j$ for each feature $j$. That is,
\begin{equation}\label{eq:lambdainv}
    [\Lambda^{-1}]_{jj} = [f(\omega_j)]^2
    ~.
\end{equation}
We have chosen this form (\ref{eq:f}) for $f(\omega)$ for specific reasons that will become obvious below.
The introduction of the feature weights dramatically changes the predictions; this is shown in \figurename~\ref{fig:fwols}.
High frequencies are suppressed and the prediction becomes smooth.
\begin{figure}[t]
    \begin{mdframed}
    \caption{Comparison of ordinary least squares (OLS) to OLS with a specific feature weighting. The feature-weighting function is given in the text in equations~(\ref{eq:f}) and (\ref{eq:lambdainv}). When the high-frequency features are weighted down, the min-norm solution gives them small amplitudes, making the fit smoother.}
    \label{fig:fwols}
    \end{mdframed}
\end{figure}

This all illustrates that, while OLS is affine invariant in the under-parameterized setting, the affine non-invariance in the over-parameterized setting is a property that can be exploited.
When the different features are weighted or normalized differently, the amplitudes of the components $\beta_j$ of the parameter vector $\beta$ have to change in response, which in turn changes its norm $\|\beta\|_2^2$.
That is, the details of the min-norm data-fitting parameter vector depends on the details of how the features are normalized or weighted.
In feature-weighted OLS, this property can be exploited to make the fits smooth, or meet other desiderata.

HOGG: Now do the full generalization with $C$ and $\Lambda$ and explain how the matrix inversion formula (CITE SOMETHING) makes these two expressions equivalent:
\begin{align}\label{eq:LambdaC1}
    \hat{Y} &= X_\ast\,(X^\top\,C^{-1}\,X + \Lambda)^{-1}\,X^\top\,C^{-1}\,Y
    \\ \label{eq:LambdaC2}
    \hat{Y} &= X_\ast\,\Lambda^{-1}\,X^\top\,(X\,\Lambda^{-1}\,X^\top + C)^{-1}\,Y
    ~.
\end{align}
Either leave the proof to the reader or make it an exercise HOGG: Check the units. And continue discussion of connections to Bayesian inference. Explain that these forms are good because they relieve the fits of the burden of going exactly through every data point. This is more responsive to the real situation of noisy data, and permits smoother solutions.

\section{\raggedright How to set the number of parameters (and other hyper-parameters)}\label{sec:dd}

There is a lot of literature analyzing the performance of linear regressions as a function of the sizes $n$ and $p$, regularization strengths and forms, and so on (for example, SOLEDAD CITE AND CITE).
They often refer to the ``risk'', which is a statistics term for the expected squared error (mistake) made when predicting new data not in your training set.
In order to deliver values or bounds on the risk, this literature depends on knowing how the data were generated, or the family of distributions from which the data ($X$ and $Y$ in our nomenclature) were drawn.
In the Real World~(tm), you don't get this luxury.
The data are given to you without documentation!
Indeed, understanding the generating process of the world is the goal of investigations in the natural sciences (such as astronomy); the investigator does not know the generating process at the outset.

... How do we look at the empirical risk as a function of $p$? That is, introduce cross-validation. Emphasize its particular value for very small values of $n$, where you don't want to hold out lots of data.

... HOGG: PLOTS showing cross-validation; the method and the results.

Now say things about how things go to h*ck when the number of parameters $p$ gets close to the number of data points $n$.

... The CV MSE gets really bad at $p\approx n$. That's not a coincidence. Reasons. Citations.

... You can avoid this with.... reasons. Citations.

HOGG: The CV MSE gets really \emph{good} at particular values of $p$. That's not surprising; there are places where the fit basis is just appropriate for your specific problem. These are the best places to work, if you can afford to search for them and find them.

HOGG: ADD SOMEWHERE ABOVE HERE: You might feel uncomfortable with dropping individual points in this problem, since the points are regularly spaced to begin with, and become irregularly spaced when you leave one out. How much does this matter? It probably does matter in detail, but you don't have much choice in problems like this. All empirical measures of predictive accuracy have these kinds of problems.

\section{\raggedright The Gaussian process: The limit of infinite features}

The Gaussian process (GP) is a non-parametric regression that takes training data $y_i$ at coordinates $t_i$, plus a kernel function, and makes predictions $\hat{y}_\ast$ for new data at new positions $t_\ast$.
The Gaussian process math looks like
\begin{equation}
    \hat{Y}_\ast = K_\ast\,K^{-1}\,Y
    ~,
\end{equation}
where $K_\ast$ is the rectangular kernel matrix between test locations $t_\ast$ and training locations $t_i$, while $K$ is the square kernel matrix between training locations and themselves
\begin{equation}
    [K]_{i,i'} = k(t_i,t_{i'})
    ~,
\end{equation}
where $k()$ is a non-negative definite definite kernel function.

HOGG: What does it mean for a kernel function to be non-negative definite?

HOGG: Note that this is not a full GP, which has both a mean and a variance. This is strictly just the MEAN of a GP. Also that this is a Wiener filter or kriging.

HOGG: Note that $K$ can have extremely bad or even infinite condition number; see the implementation notes in \sectionname~\ref{sec:implementation}.

There is a strong connection between OLS and the GP. In particular, when the features $x_j$ form [some kind of] basis, and we take the limit of infinite features ($p\rightarrow\infty$) we get kernel matrices in place of the $X\,\Lambda^{-1}\,X^\top$ matrix products;
\begin{align}
    \lim_{p\rightarrow\infty} X\,\Lambda^{-1}\,X^\top &= K
    \\
    \lim_{p\rightarrow\infty} X_\ast\,\Lambda^{-1}\,X^\top &= K_\ast
    ~,
\end{align}
where $\Lambda^{-1}$ is the diagonal matrix of weights, and element $i,i'$ of $K$ is obtained by evaluating a kernel function $k(t_i,t_{i'})$.
Equivalently, the limit is
\begin{equation}
    \lim_{p\rightarrow\infty} \sum_{j=1}^p [\Lambda^{-1}]_{jj}\,g_j(t)\,g_{j}(t') = k(t, t')
    ~,
\end{equation}
where we have used the diagonality of $\Lambda$ to make a single sum over $j$.
The specific form of the kernel function $k(\cdot,\cdot)$ depends on the basis (the features) we choose, and the weighting of the basis functions in the OLS.

The connection between the infinite basis chosen (the form and weighting of the features) and the kernel function is governed by Mercer's theorem (CITE).
However, if the basis is Fourier, as we chose above in (\ref{eq:basis}), and the spacing between modes ($\Delta\omega =\omega_{j+2}-\omega_j$) is small enough, the kernel becomes very close to the Fourier transform of the square of the weighting function $f(\omega)$ we use to weight the features.

That is, in the case of the specific example of weight function $f(\omega)$ given in equation (\ref{eq:f}), we can connect our feature-weighted OLS to an equivalent GP if we know the fourier transform of the square of $f(\omega)$. We chose that specific form for $f(\omega)$ because it has a square that is a member of a Fourier-transform pair:
\begin{align}
    \FT[F(t)] &= [f(\omega)]^2
    \\ \label{eq:F}
    F(t) &= \sqrt{\frac{\pi}{8}}\,\left(1 + \frac{|t|}{s}\right)\,\exp -\frac{|t|}{s}
    ~.
\end{align}
This latter function is also known as the Mat\'ern $3/2$ kernel function; it will become the kernel function for the Gaussian process when we take the limit.
In the limit $p\rightarrow\infty$, then, the specific example of a feature-weighted OLS given here becomes, in the limit, a GP with a kernel function very close to
\begin{align}
    k(t_i,t_{i'}) &= F(t_i-t_{i'})
    \\
    &= \sqrt{\frac{\pi}{8}}\,\left(1 + \frac{|t_i - t_{i'}|}{s}\right)\,\exp -\frac{|t_i - t_{i'}|}{s}
    ~.
\end{align}
The comparison of the GP with this kernel to the equivalent feature-weighted OLS with large (but finite) number of parameters $p$ is shown in \figurename~\ref{fig:gp}.
\begin{figure}[t]
    \begin{mdframed}
    \caption{Comparison of feature-weighted ordinary least squares with a Gaussian process. The figure shows the OLS fit, the feature-weighted version with the particular feature weighting given in (\ref{eq:f}), and the GP fit using the kernel (\ref{eq:F}) that is the Fourier transform of the square of the feature weighting. The feature-weighted fit and the GP are essentially identical, as expected.}
    \label{fig:gp}
    \end{mdframed}
\end{figure}

HOGG: Remind the reader that there are hundreds of known kernel functions you can have here, and hundreds of corresponding weighting functions $f(\omega)$, and that is just in this Fourier basis; there are more in other bases (polynomial, wavelet, and so on).

RANDOM CONJECTURAL SENTENCE; move earlier: Provided that the spacing of the Fourier modes in frequency space is $\Delta\omega\ll 1 / \Delta t_{\max}$ and the maximum frequency $\floor{p / 2}\,\Delta\omega \gg 1 / \min(s, \Delta t_{\min})$, where
\begin{align}
    \Delta t_{\min} = \min_{i\ne j}|t_i - t_j|
    \\
    \Delta t_{\max} = \max_{i,j}|t_i - t_j|
    ~,
\end{align}
the OLS with feature weights $f(\omega)$ will be very similar to the mean of a GP with kernel $k(\Delta t) = \FT[f^2]$.

At the end of \sectionname~\ref{sec:fwols}, we discussed including not just feature weights in a matrix $\Lambda^{-1}$ but also data weights in a matrix $C^{-1}$. The GP also permits this, and it is often a very good idea. The generalization of equations (\ref{eq:LambdaC1}) and (\ref{eq:LambdaC2}) to the GP case is 
\begin{equation}
    \hat{Y}_\ast = K_\ast\,(K + C)^{-1}\,Y
    ~.
\end{equation}
As before, in contexts where you have independent uncertainties on each element $y_i$ of your training data $Y$, $C^{-1}$ would naturally be set to the diagonal matrix containing the inverses of the variances of those uncertainties.
This form is used a lot in astronomy and physics (HOGG CITE SOME THINGS?) and it is also the standard form given for the Wiener filter (CITE).

\section{\raggedright Interpolators, running means, filters, and so forth}

HOGG: MAYBE THIS BECOMES JUST PART OF THE DISCUSSION?

HOGG: In what sense are all these things the same things? All I got is that if they are linear---meaning that the prediction $\hat{Y}_\ast$ can be written as a linear operator acting on the training data $Y$---then they probably can be written in some form like feature-weighted OLS in the $p>>n$ regime.

\section{Uncertainties on the predictions}\label{sec:uncertainty}

Often you need to compute not just a prediction, but also an uncertainty on that prediction.
How faithfully you must compute that uncertainty will depend strongly on the context in which you are doing the fitting or interpolation.
However, it is often the case in the physical sciences that predictions are required to come with good or conservative estimates of uncertainty.
There are four-ish sources of uncertainty in the predictions you are making in problems like these:
(1)~The data points you have $y_i$ are individually noisy.
(2)~There are finitely many of those data points (there are $n$ of them) and there are gaps between them in the location space $t$.
(3)~The data points might have uncertain locations or location measurements $t_i$.
(4)~And the predictions you make depend on hyper-parameter choices, such as the form of the basis, the number of parameters $p$, and any regularization or feature weighting.
These four different sources of uncertainty propagate differently and are differently ``simple'' to deal with.

In particular... (1) and (2) easy, (3) and (4) hard.

HOGG: If you have a full likelihood function, you can use it to get uncertainties. Give example! But this is not conservative; or it makes many strong assumptions. Sometimes you don't even know enough about your data to write down a LF you believe. Give some examples for the different regimes.

HOGG: Bayes has even more assumptions than the LF uncertainty estimates. But gives well-defined uncertainties automatically.

HOGG: If you want to be conservative, use jackknife to get the uncertainties. Explain how this works, and how to implement in the large-$n$ case. Repeat some of the fitting examples but showing the uncertainties as well.
Give the explicit formula for jackknife, with its dimensionless prefactor.
Note the similarity between jackknife and cross-validation; that's relevant and important!

HOGG: As for (3): Resample the $t_i$ values maybe? As for (4): Brute-force search? It isn't really possible to do (4) without a model for the behavior of a scientist!! Refer back to the subjectivity of it all.

\section{Implementation notes}\label{sec:implementation}

All of the code used to make the figures for this \documentname\ is available publicly at HOGG WHERE?
Although the examples are toy, the implementation of everything can be generalized for real-data situations.

Things here about inv(), solve(), lstsq(), and so on. Be sure to talk about the GP as well as the OLS cases here.

How to do a pseudo-inverse that is numerically safe. It requires an RCOND or equivalent.

Note that once $p$ is large enough, if you are using a feature weighting that declines with $p$, at some point, at machine precision, the additional columns you are adding to $X$ are effectively all zeros. That's not a problem if you implement your linear algebra well, but it does mean that your cross-validations will saturate at some $p$ (see the \figurename).

Things here about not constructing operators that are almost entirely zeros.

Set your hyper-parameters by cross-validation. Set $p$, choice of basis, choice of weighting, regularization parameters all this way. Get explicit about CV.

\section{Discussion}

HOGG: What main points did we make; what do we want you to take home? HOGG: Related: Why were we motivated to write this document?

(HOGG: Say something about the case in which you have prior beliefs about the expected values of the parameters. THERE IS A PLACEHOLDER for this in the section about the over-parameterized case.)

TODO:
\begin{itemize}
    \item Higher dimensions for the ambient space. Spherical harmonics.
    \item The practice: design features for linear regression, how many do you choose, avoid pitfalls, when to go to Gaussian processes. Cross-validation. Everything an astronomer needs to know.
    \item Discuss L1 and sparsity. In general in these flexible contexts, sparsity is usually not important. But if it is important, L1 is a good tool. AND you can get both the smoothness you want AND the sparsity if you do feature weighting and L1 (instead of feature weighting and L2, as we do here). Cite (https://arxiv.org/pdf/1308.0759.pdf).
    \item make a bibliography and cite stuff!
    \item Make sure this appears above in the uncertainties section: What do you do when your locations $t_i$ are themselves noisy or uncertain? Recall our fundamental assumption. There is a literature on this, and it isn't easy. One option: Linearize and add variances. Only works for uncertainties that are small wrt model features. Another option: Infer the $t_i$. That's often extremely hard.
\end{itemize}

\end{document}

### 2020-12-08 paper/main.tex
Updates from Overleaf

@@
 \usepackage{xcolor}
+\usepackage{natbib}
+\usepackage{hyperref}
 
@@
 }
+% and...
+\newlength{\figurewidth}
+\setlength{\figurewidth}{0.88\textwidth}
 
@@
 \setlength{\textheight}{9.20in}
-\setlength{\oddsidemargin}{-0.20in}
+\setlength{\oddsidemargin}{0.75in}
 \setlength{\textwidth}{5.00in}
@@
 \frenchspacing\sloppy\sloppypar\raggedbottom
+
+% Hogg's really severe issues
+\makeatletter
+\renewcommand\section{\@startsection {section}{1}{\z@}%
+  {-3.5ex \@plus -1ex \@minus -.2ex}%
+  {2.3ex \@plus.2ex}%
+  {\raggedright\normalfont\Large\bfseries}}
+\makeatother
 
@@
 \newcommand{\foreign}[1]{\textsl{#1}}
+\newcommand{\code}[1]{\texttt{#1}}
 
@@
 
-\section{\raggedright Standard linear fitting: Ordinary least squares with a feature embedding}
+\section{Standard linear fitting: Ordinary least squares with a feature embedding}
 
@@
     ~,
+\label{eq.model}
 \end{equation}
@@
 
-For a concrete example, one common choice is to make the feature embedding functions $g_j()$ terms in a Fourier series
+For a concrete example, one common choice is to make the feature embedding functions $g_j(t)$ terms in a Fourier series
 \begin{align}\label{eq:basis}
@@
 Example functions $g_j(t)$ from this basis are shown in \figurename~\ref{fig:basis}.
-Alternative common choices would be to make the embedding fumctions $g_j()$ polynomials or other kinds of ordered basis functions, such as wavelets or spherical harmonics (the latter if, say, the $t_i$ are positions on the sphere).
+Alternative common choices would be to make the embedding fumctions $g_j(t)$ polynomials or other kinds of ordered basis functions, such as wavelets or spherical harmonics (the latter if, say, the $t_i$ are positions on the sphere).
 \begin{figure}[t]
     \begin{mdframed}
-    \caption{Examples of basis functions $g_j(t)$ from the basis given in equation~(\ref{eq:basis}).
+    \includegraphics[width=\figurewidth]{paper/fourier.pdf}
+    \caption{Examples of basis functions $g_j(t)$ from the basis given in equation~\eqref{eq:basis}.
 This basis was constructed with length-scale parameter $T=3$.
@@
 \end{equation}
-This optimization objective (\ref{eq:opt1}) is convex and the optimization problem has a solution in closed form as long as the number of parameters (and features) $p$ is less than the number of training points $n$ (and the matrix $X^\top X$ is invertible):
+This optimization objective \eqref{eq:opt1} is convex and the optimization problem has a solution in closed form as long as the number of parameters (and features) $p$ is less than the number of training points $n$ (and the matrix $X^\top X$ is invertible):
 \begin{equation}
@@
 Examples of OLS applied to some toy data are shown in \figurename~\ref{fig:ols1}.
-This form (\ref{eq:OLS}) of the prediction of new test data is called ordinary least squares (OLS). It has many good properties, some of which are encoded in the Gauss--Markov theorem.
-SOLEDAD: PUT WORDS HERE ABOUT WHAT IS PROMISED BY GAUSS--MARKOV. ALSO: REFERENCE?
+This form \eqref{eq:OLS} of the prediction of new test data is called ordinary least squares (OLS). It has many good properties, some of which are encoded in the Gauss--Markov theorem.
+In particular, if the noise contributions in the model given in equation \eqref{eq.model} are uncorrelated, has zero mean, and equal variances for $i=1,\ldots, n$ then the Gauss--Markov theorem states that the OLS estimator has the lowest variance within the class of unbiased estimators that are linear in $Y$ (see, for example, \citealt{esl}, Ch 3).
+
 \begin{figure}[t]
     \begin{mdframed}
+    \includegraphics[width=\figurewidth]{paper/OLS-under.pdf}
     \caption{Ordinary least-squares (OLS) fits (continuous lines) to a set of example data points (black dots).
@@
 
-The prediction (\ref{eq:OLS}) when $p<n$ (the under-paraemeterized or traditional regime) is \emph{affine invariant} in that $p$-dimensional rotations or rescalings of the rectangular $X$ design matrix do not affect predictions.
+The prediction \eqref{eq:OLS} when $p<n$ (the under-paraemeterized or traditional regime) is \emph{affine invariant} in that $p$-dimensional rotations or rescalings of the rectangular $X$ design matrix do not affect predictions.
 That is, if $R$ is an invertible $p\times p$ matrix, the prediction using $X'\leftarrow X\,R$ will be identical to the prediction using the original $X$.
@@
 
-Although the OLS prediction (\ref{eq:OLS}) is affine invariant with respect to $p$-dimensional transformations, it is \emph{not} affine invariant with respect to $n$-dimensional transformations, such as a re-weighting of the input data.
+Although the OLS prediction \eqref{eq:OLS} is affine invariant with respect to $p$-dimensional transformations, it is \emph{not} affine invariant with respect to $n$-dimensional transformations, such as a re-weighting of the input data.
 Indeed, if you know weights or inverse variances for your data points, conceptually you can put them into a weight matrix $C^{-1}$ (written this way to emphasize that reweighting is usually inverse-variance weighting) and write
@@
     \begin{mdframed}
+    \includegraphics[width=\figurewidth]{paper/WLS.pdf}
     \caption{Comparison of ordinary least-squares (OLS) and weighted least-squares (WLS) fits (continuous lines) to the example data (black dots).
@@
     \begin{mdframed}
+    \includegraphics[width=\figurewidth]{paper/ridge.pdf}
     \caption{Comparison of ordinary least-squares (OLS) and ridge-regression fits (continuous lines) to the example data (black dots).
@@
 We generally recommend cross-validation, to be discussed below in \sectionname~\ref{sec:dd}.
-Ridge regression is not affine invariant in the sense that the standard OLS prediction (\ref{eq:OLS}) is; that is, the effect of the regularization depends on the amplitudes and linear combinations of features placed in the feature matrix.
+Ridge regression is not affine invariant in the sense that the standard OLS prediction \eqref{eq:OLS} is; that is, the effect of the regularization depends on the amplitudes and linear combinations of features placed in the feature matrix.
 This will become important later when we consider feature weights below.
@@
 
-\section{\raggedright Over-parameterization}
+\section{Over-parameterization}
 
@@
 provided that $X\,X^\top$ is invertible (which will usually be the case).
-Like (\ref{eq:OLS}), this prediction is \emph{also} called ordinary least squares (OLS), or sometimes ``min-norm least-squares'' to emphasize the degeneracy-breaking choice.
+Like \eqref{eq:OLS}, this prediction is \emph{also} called ordinary least squares (OLS), or sometimes ``min-norm least-squares'' to emphasize the degeneracy-breaking choice.
 Examples of OLS fits in the over-parameterized regime are shown in \figurename~\ref{fig:ols2}.
@@
     \begin{mdframed}
+    \includegraphics[width=\figurewidth]{paper/OLS-over.pdf}
     \caption{Ordinary least-squares (OLS) or min-norm least-squares fits (continuous lines) to a set of example data points (black dots), but now for a few over-parameterized cases.
@@
 It will try to stay as close to $y=0$ as possible.
-SOLEDAD: CHECK WORDING.
 
-The two equations for OLS---(\ref{eq:OLS}) and (\ref{eq:OLS2})---can be unified into one equation (and also generalized to handle non-invertible matrices $X^\top X$ and $X\,X^\top$) if we define the pseudo-inverse $X^\dagger$:
+The two equations for OLS---\eqref{eq:OLS} and \eqref{eq:OLS2}---can be unified into one equation (and also generalized to handle non-invertible matrices $X^\top X$ and $X\,X^\top$) if we define the pseudo-inverse $X^\dagger$:
 \begin{equation}\label{eq:OLS3}
     \hat{Y}_\ast = X_\ast\,X^\dagger\,Y
-    ~,
+    ~.
 \end{equation}
-where the pseudo-inverse is the matrix made by inverting the singular values and transposing.
-That is, if the singular-value decomposition (SVD) of $X$ is $U\,S\,V$, with $S$ diagonal, the SVD of $X^\dagger$ is $V^\top\,S_{\text{nonzero}}^{-1}\,U^\top$, where $S_{\text{nonzero}}^{-1}$ contains the inverses of the non-zero elements of $S$, and zeros where $S$ is zero.
-SOLEDAD IS THERE A BETTER NOTATION OR EXPLANATION HERE?
-SHOULD I BREAK THIS OUT INTO EQUATIONS?
-(SOLEDAD SAYS: Define pseudo-inverse for a diagonal matrix and then use SVD and reduce to the previously stated definition.)
-This pseudo-inverse form (\ref{eq:OLS3}) of OLS is extremely general: It works for both the $p\le n$ and $p>n$ cases, and it works when the $X\,X^\top$ or $X^\top\,X$ matrices are not invertible.
+The pseudo-inverse of a diagonal matrix is defined as the diagonal matrix made by inverting the non-zero diagonal entries.
+And for a non-diagonal matrix the pseudo-inverse is defined by taking the singular-value decomposition (SVD) of $X$, $X=U\,S\,V$, with $S$ diagonal and $U,V$ orthogonal, then $X^\dagger \equiv V^\top\,S^{\dagger}\,U^\top$.
+
+This pseudo-inverse form \eqref{eq:OLS3} of OLS is extremely general: It works for both the $p\le n$ and $p>n$ cases, and it works when the $X\,X^\top$ or $X^\top\,X$ matrices are not invertible.
 There can be significant numerical issues with implementing the pseudo-inverse; we comment on those in \sectionname~\ref{sec:implementation}.
 
-\section{\raggedright Feature weighting}\label{sec:fwols}
+\section{Feature weighting}\label{sec:fwols}
 
@@
 \end{equation}
-This optimization penalizes more strongly the parameters $\beta_j$ corresponding to features $g_j()$ with larger values of $[\Lambda^{1/2}]_{jj}$.
+This optimization penalizes more strongly the parameters $\beta_j$ corresponding to features $g_j(t)$ with larger values of $[\Lambda^{1/2}]_{jj}$.
 
@@
 \end{equation}
-We have chosen this form (\ref{eq:f}) for $f(\omega)$ for specific reasons that will become obvious below.
+We have chosen this form \eqref{eq:f} for $f(\omega)$ for specific reasons that will become obvious below.
 The introduction of the feature weights dramatically changes the predictions; this is shown in \figurename~\ref{fig:fwols}.
@@
     \begin{mdframed}
+    \includegraphics[width=\figurewidth]{paper/weighted-OLS.pdf}
     \caption{Comparison of ordinary least squares (OLS) to OLS with a specific feature weighting.
-The feature-weighting function is given in the text in equations~(\ref{eq:f}) and (\ref{eq:lambdainv}).
+The feature-weighting function is given in the text in equations~\eqref{eq:f} and \eqref{eq:lambdainv}.
 When the high-frequency features are weighted down, the min-norm solution gives them small amplitudes, making the fit smoother.}
@@
 
-\section{\raggedright How to set the number of parameters (and other hyper-parameters)}\label{sec:dd}
+\section{How to set the number of parameters (and other hyper-parameters)}\label{sec:dd}
 
-There is a lot of literature analyzing the performance of linear regressions as a function of the sizes $n$ and $p$, regularization strengths and forms, and so on (for example, SOLEDAD CITE AND CITE).
+There is a lot of literature analyzing the performance of linear regressions as a function of the sizes $n$ and $p$, regularization strengths and forms, and so on (for example, \citealt{bartlett2020benign}, \citealt{hastie2019surprises} ).
 They often refer to the ``risk'', which is a statistics term for the expected squared error (mistake) made when predicting new data not in your training set.
@@
 
-... HOGG: PLOTS showing cross-validation; the method and the results.
+... HOGG: Figure~\ref{fig:LOO1} illustrates the process of leave-one-out fitting and prediction.
+\begin{figure}[t]
+    \begin{mdframed}
+    \includegraphics[width=\figurewidth]{paper/LOO.pdf}
+    \caption{A demonstration of leave-one-out cross-validation for one particular model.
+The 23 lines are the 23 fits, for each of which one data point was held out.
+Also ploted on each of the 23 lines is the prediction made for that fit's held-out data point.
+HOGG anything else to say here?}
+    \label{fig:LOO1}
+    \end{mdframed}
+\end{figure}
+
+...
+HOGG: Figure~\ref{fig:LOO2} shows the mean-squared leave-one-out cross-validation estimate of mean squared prediction error as a function of the number of features $p$ for the feature-weighted OLS and for the limiting Gaussian process.
+\begin{figure}[t]
+    \begin{mdframed}
+    \includegraphics[width=\figurewidth]{paper/cross-validation.pdf}
+    \caption{Leave-one-out cross-validation estimates of mean squared prediction error for the feature-weighted OLS fits, as a function of the number of features $p$.
+In detail the first (lowest-$t$) and last (highest-$t$) data points were not used in computing the mean squared error.
+Note that the predictions are much, much worse at $p\approx n$ than they are at very low or very high $p$.
+HOGG THIS FIGURE CAPTION IS NOT COMPLETE}
+    \label{fig:LOO2}
+    \end{mdframed}
+\end{figure}
+For the cross-validation we excluded the end points; that is, for robustness, we didn't leave out and predict the first and last point.
+That choice isn't necessarily justifiable!
+HOGG say more things here.
 
@@
 
-\section{\raggedright The Gaussian process: The limit of infinite features}
+\section{The Gaussian process: The limit of infinite features}
 
@@
 \end{equation}
-where $k()$ is a non-negative definite definite kernel function.
+where $k(\cdot,\cdot)$ is a non-negative definite definite kernel function.
 
@@
     ~,
+    \label{eq.limit}
 \end{align}
@@
 The connection between the infinite basis chosen (the form and weighting of the features) and the kernel function is governed by Mercer's theorem (CITE).
-However, if the basis is Fourier, as we chose above in (\ref{eq:basis}), and the spacing between modes ($\Delta\omega =\omega_{j+2}-\omega_j$) is small enough, the kernel becomes very close to the Fourier transform of the square of the weighting function $f(\omega)$ we use to weight the features.
+However, if the basis is Fourier, as we chose above in \eqref{eq:basis}, and the spacing between modes ($\Delta\omega =\omega_{j+2}-\omega_j$) is small enough, the kernel becomes very close to the Fourier transform of the square of the weighting function $f(\omega)$ we use to weight the features.
 
-That is, in the case of the specific example of weight function $f(\omega)$ given in equation (\ref{eq:f}), we can connect our feature-weighted OLS to an equivalent GP if we know the fourier transform of the square of $f(\omega)$.
+That is, in the case of the specific example of weight function $f(\omega)$ given in equation \eqref{eq:f}, we can connect our feature-weighted OLS to an equivalent GP if we know the fourier transform of the square of $f(\omega)$.
 We chose that specific form for $f(\omega)$ because it has a square that is a member of a Fourier-transform pair:
@@
     k(t_i,t_{i'}) &= F(t_i-t_{i'})
-    \\
+    \\ \label{eq:k}
     &= \sqrt{\frac{\pi}{8}}\,\left(1 + \frac{|t_i - t_{i'}|}{s}\right)\,\exp -\frac{|t_i - t_{i'}|}{s}
@@
 \end{align}
-The comparison of the GP with this kernel to the equivalent feature-weighted OLS with large (but finite) number of parameters $p$ is shown in \figurename~\ref{fig:gp}.
+Provided that the spacing of the Fourier modes in frequency space is $\Delta\omega\ll 1 / \Delta t_{\max}$ and the maximum frequency $\floor{p / 2}\,\Delta\omega \gg 1 / \min(s, \Delta t_{\min})$, where
+\begin{align}
+    \Delta t_{\min} \equiv \min_{i\ne j}|t_i - t_j|
+    \\
+    \Delta t_{\max} \equiv \max_{i,j}|t_i - t_j|
+    ~,
+\end{align}
+it will be true that the OLS with feature weights $f(\omega)$ will be very similar to the mean of a GP with kernel $k(\Delta t) = \FT[f^2]$.
+The comparison of the OLS and GP is shown in \figurename~\ref{fig:gp}.
 \begin{figure}[t]
     \begin{mdframed}
+    \includegraphics[width=\figurewidth]{paper/GP.pdf}
     \caption{Comparison of feature-weighted ordinary least squares with a Gaussian process.
-The figure shows the OLS fit, the feature-weighted version with the particular feature weighting given in (\ref{eq:f}), and the GP fit using the kernel (\ref{eq:F}) that is the Fourier transform of the square of the feature weighting.
+The figure shows the OLS fit, the feature-weighted version with the particular feature weighting given in \eqref{eq:f}, and the GP fit using the kernel \eqref{eq:F} that is the Fourier transform of the square of the feature weighting.
 The feature-weighted fit and the GP are essentially identical, as expected.}
@@
 
-RANDOM CONJECTURAL SENTENCE; move earlier: Provided that the spacing of the Fourier modes in frequency space is $\Delta\omega\ll 1 / \Delta t_{\max}$ and the maximum frequency $\floor{p / 2}\,\Delta\omega \gg 1 / \min(s, \Delta t_{\min})$, where
-\begin{align}
-    \Delta t_{\min} = \min_{i\ne j}|t_i - t_j|
-    \\
-    \Delta t_{\max} = \max_{i,j}|t_i - t_j|
-    ~,
-\end{align}
-the OLS with feature weights $f(\omega)$ will be very similar to the mean of a GP with kernel $k(\Delta t) = \FT[f^2]$.
+HOGG: The kernel in equation \eqref{eq:k} is a stationary kernel, meaning it depends only on absolute values of time differences $|t - t'|$.
+Not all $p\rightarrow\infty$ kernels will be stationary.
+The limit $p\rightarrow\infty$ of $X\,\Lambda^{-1}\,X^\top$ in \eqref{eq.limit} leads to a stationary kernel $k(\cdot,\cdot)$ because the feature embedding in $X$ is a set of sines and cosines.
+Sines and cosines form a basis for translation-invariant function spaces. SOLEDAD: IS THIS WORDING OKAY?
 
@@
 The GP also permits this, and it is often a very good idea.
-The generalization of equations (\ref{eq:LambdaC1}) and (\ref{eq:LambdaC2}) to the GP case is
-\begin{equation}
+The generalization of equations \eqref{eq:LambdaC1} and \eqref{eq:LambdaC2} to the GP case is
+\begin{equation}\label{eq:gpC}
     \hat{Y}_\ast = K_\ast\,(K + C)^{-1}\,Y
@@
 \end{equation}
-As before, in contexts where you have independent uncertainties on each element $y_i$ of your training data $Y$, $C^{-1}$ would naturally be set to the diagonal matrix containing the inverses of the variances of those uncertainties.
-This form is used a lot in astronomy and physics (HOGG CITE SOME THINGS?) and it is also the standard form given for the Wiener filter (CITE).
-
-\section{\raggedright Interpolators, running means, filters, and so forth}
-
-HOGG: MAYBE THIS BECOMES JUST PART OF THE DISCUSSION?
-
-HOGG: In what sense are all these things the same things?
-All I got is that if they are linear---meaning that the prediction $\hat{Y}_\ast$ can be written as a linear operator acting on the training data $Y$---then they probably can be written in some form like feature-weighted OLS in the $p>>n$ regime.
+As before, in contexts where you have independent uncertainties on each element $y_i$ of your training data $Y$, $C^{-1}$ would naturally be set to the diagonal matrix containing the inverses of the variances of those uncertainties (so $C$ would contain the variances).
+This form \eqref{eq:gpC} is used a lot in astronomy and physics (HOGG CITE SOME THINGS?) and it is also the standard form given for the Wiener filter (CITE).
 
@@
 In particular... (1) and (2) easy, (3) and (4) hard.
+
+SOLEDAD SAYS: Maybe re-order 1 - 3 - 2 - 4.
 
@@
 HOGG: As for (3): Resample the $t_i$ values maybe?
-As for (4): Brute-force search?
-It isn't really possible to do (4) without a model for the behavior of a scientist!!
-Refer back to the subjectivity of it all.
+Another option is to linearize if the uncertainties are small wrt function changes (see, eg GP literature).
+Or infer and marginalize out (ferociously expensive).
+
+HOGG: As for (4): Brute-force search? It isn't really possible to do (4) without a model for the behavior of a scientist!! Refer back to the subjectivity of it all.
 
@@
 All of the code used to make the figures for this \documentname\ is available publicly at HOGG WHERE?
-Although the examples are toy, the implementation of everything can be generalized for real-data situations.
+Although the examples are toys, the implementation of everything can be generalized for real-data situations.
+In that code, there are some aspects of the linear-algebra implementation that might seem odd....HOGG
 
-Things here about inv(), solve(), lstsq(), and so on. Be sure to talk about the GP as well as the OLS cases here.
+Things here about \code{inv(A) @ b}, \code{solve(A, b)}, \code{lstsq(A, b, rcond=tiny)}, and so on. Be sure to talk about the GP as well as the OLS cases here.
 
@@
 Cite (https://arxiv.org/pdf/1308.0759.pdf).
-    \item make a bibliography and cite stuff!
-    \item Make sure this appears above in the uncertainties section: What do you do when your locations $t_i$ are themselves noisy or uncertain?
-Recall our fundamental assumption.
-There is a literature on this, and it isn't easy.
-One option: Linearize and add variances.
-Only works for uncertainties that are small wrt model features.
-Another option: Infer the $t_i$.
-That's often extremely hard.
+    \item cite stuff!
 \end{itemize}
 
+HOGG: In what sense are these flexible models the same as things like interpolators, running means, filters, and so on?
+All I got is that if they are linear---meaning that the prediction $\hat{Y}_\ast$ can be written as a linear operator acting on the training data $Y$---then they probably can be written in some form like feature-weighted OLS in the $p>>n$ regime.
+
+\raggedright
+\bibliographystyle{authordate1}
+\bibliography{references}
+
 \end{document}

### 2020-12-09 paper/main.tex
Updates from Overleaf

@@
 \usepackage{natbib}
-\usepackage{hyperref}
+\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}
 
@@
   roundcorner=5pt,
-  shadow=true,
+  shadow=false,
   shadowcolor=black!05,
@@
 }
-% and...
-\newlength{\figurewidth}
-\setlength{\figurewidth}{0.88\textwidth}
 
@@
 \setlength{\textheight}{9.20in}
-\setlength{\oddsidemargin}{0.75in}
-\setlength{\textwidth}{5.00in}
+\setlength{\oddsidemargin}{0.5in}
+\setlength{\textwidth}{5.50in}
 \setlength{\parindent}{0.18in}
@@
 \markright{\textcolor{gray}{\textsf{\upshape Fitting very flexible models / Hogg \& Villar}}}
+\newlength{\figurewidth}
+\setlength{\figurewidth}{0.94\textwidth}
+\setlength{\textfloatsep}{1ex}
+\setlength{\floatsep}{1ex}
 \frenchspacing\sloppy\sloppypar\raggedbottom
@@
 \textsl{\footnotesize Flatiron Institute, a division of the Simons Foundation \\
-Center for Cosmology and Particle Physics, Dept. Physics, New York University \\
+Center for Cosmology and Particle Physics, Deptartment of Physics, New York University \\
 Center for Data Science, New York University \\
@@
 Mathematical Institute for Data Science, Johns Hopkins University}
-
-\medskip
-\noindent
-2020 December
 
@@
 
-Fundamentally the assumption or setting in what follows will be that you care about predicting new data or interpolating the data, but you explicitly don't care about the parameters of the fit or the weights of the basis functions \foreign{per se}.
+HOGG: There are other contexts in which, recently, regressions have gone to very large numbers of parameters.
+For example, when there are many possible natural features...
+Pixels in an image or spectrum...
+etc...
+Deep learning and etc.
+This isn't our context!
+But it is relevant and related.
+Many good books exist, for example (HOGG CITE VARIOUS).
+
+An important assumption or setting in what follows will be that you care about predicting new data or interpolating the data, but you explicitly don't care about the parameters of the fit or the weights of the basis functions \foreign{per se}.
 In this setting there are no important meanings to the components of the model.
@@
 Alternative common choices would be to make the embedding fumctions $g_j(t)$ polynomials or other kinds of ordered basis functions, such as wavelets or spherical harmonics (the latter if, say, the $t_i$ are positions on the sphere).
+Another choice that isn't common in the natural sciences, but highly studied in machine learning (for example, SOLEDAD CITE RANDOM FEATURES PAPER), is to choose the features randomly from a distribution (rather than on a regular grid in frequency, as we do here).
+That is beyond our scope, but we come back to it in \sectionname~\ref{sec:discussion}.
 \begin{figure}[t]
@@
 It might be crossing your mind that there are uncertainties not just in the data points $y_i$, but also often in the \emph{locations} $t_i$ of the data points as well.
-It turns out that taking the latter into account is a much harder problem; we return to this also in \sectionname~\ref{sec:uncertainty} (HOGG: DO WE OR IS IT JUST IN THE DISCUSSION??).
+It turns out that taking the latter into account is a much harder problem; we return to this also in \sectionname~\ref{sec:uncertainty}.
 
@@
 
-HOGG: Connect here to the Gaussian product refactor note.
-
 You can combine both the point weighting from WLS and the generalized ridge regression into a weighted ridge that looks like
-\begin{equation}
+\begin{equation}\label{eq:foo}
     \hat{Y}_\ast = X_\ast\,(X^\top\,C^{-1}\,X + \Lambda)^{-1}\,X^\top\,C^{-1}\,Y
@@
 This form has good properties for many real-world physics applications, where data-point error bars are often known, and functions are often expected to be smooth.
-HOGG: Say something about units here, to set up a subsequent discussion.
+We'll discuss this form \eqref{eq:foo} more below in \sectionname~\ref{sec:fwols},
+but briefly we can say here that it appears in Bayesian inference contexts where the data points $y_i$ are treated as having Gaussian noise associated with them (with known variance tensor $C$) and there is a Gaussian prior on the parameter vector $\beta$ (with known variance $\Lambda$).
+We have discussed that model elsewhere (\citealt{products}).
+It is also useful sometimes to think of the ``units'' or dimensions of the quantities in \eqref{eq:foo}: In the Bayesian setting, the units of $C$ would be the square of the units of $Y$ and the units of $\Lambda$ would be the square of the units of the ratio $Y/X$ (the square of the units of $\beta$).
 
@@
 This optimization is again convex and has a unique solution, although that solution will depend on feature weights that we discuss in a moment.
-When the investigator knows uncertainties on the training data points $y_i$, this expression will change a bit; we return to that in the HOGG WHICH \sectionname\ (HOGG: DO WE?).
+When the investigator knows uncertainties on the training data points $y_i$, this expression will change a bit; we return to that in the next \sectionname.
 The under-parameterized and over-parameterized optimizations can be unified into one form by considering the limit of light L2 regularization:
@@
 It is slightly off-topic to notice that in \figurename~\ref{fig:ols2}, as $p$ gets very large, the OLS solution approaches $y=0$ everywhere that it can.
-This behavior is a direct consequence of Parseval's Theorem (CITE), which states that the Fourier transform is unitary.
+This behavior is a direct consequence of Parseval's identity, which states that the Fourier transform is unitary.
 This means that the integral over frequency of the square of the Fourier transform is equal (up to a factor of $2\pi$) to the integral over location of the square of the original function.
@@
 It will try to stay as close to $y=0$ as possible.
+That's probably not desirable in most applications! We will fix that problem in the next \sectionname.
 
@@
 The pseudo-inverse of a diagonal matrix is defined as the diagonal matrix made by inverting the non-zero diagonal entries.
-And for a non-diagonal matrix the pseudo-inverse is defined by taking the singular-value decomposition (SVD) of $X$, $X=U\,S\,V$, with $S$ diagonal and $U,V$ orthogonal, then $X^\dagger \equiv V^\top\,S^{\dagger}\,U^\top$.
+And for any non-diagonal (or any non-square) matrix $X$ the pseudo-inverse is defined by taking the singular-value decomposition (SVD) of $X$, $X=U\,S\,V$, with $S$ diagonal and $U,V$ orthogonal, then $X^\dagger \equiv V^\top\,S^\dagger\,U^\top$.
 
@@
 That is, rotations and scalings in the feature space \emph{will} affect predictions.
-It behooves us to re-scale the features (the $p$ $n$-vectors of the design matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features.
+It behooves us to re-scale the features (the $p$ $n$-vectors of the design matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features (SOLEDAD CITE WARD; OTHERS?).
 We can encode these feature weights in a $p\times p$ diagonal weight matrix $\Lambda^{-1}$ and the prediction becomes
@@
 This optimization penalizes more strongly the parameters $\beta_j$ corresponding to features $g_j(t)$ with larger values of $[\Lambda^{1/2}]_{jj}$.
-
-HOGG: Remind the readers who prefer obvious scalar forms that $\|\Lambda^{-1/2}\,\beta\|_2^2 = \beta^\top\,\Lambda^{-1}\,\beta$.
-That's a gauge-invariant object (if $\beta$ and $\Lambda$ are gauge-invariant objects themselves).
+If you are a physicist and you don't like the mathematical $\|\cdot\|_2^2$ notation---if you prefer to look at quantities that are obvious scalar forms---then recall that $\|\Lambda^{-1/2}\,\beta\|_2^2 = \beta^\top\,\Lambda^{-1}\,\beta$.
+That latter object is a gauge-invariant object so long as $\beta$ and $\Lambda$ are also gauge-invariant objects themselves.
+Yes, data analysis can have this kind of geometric structure!
 
@@
 This is more responsive to the real situation of noisy data, and permits smoother solutions.
+HOGG: AND return to units again. And cite products again.
 
@@
 
-...
-How do we look at the empirical risk as a function of $p$?
-That is, introduce cross-validation.
-Emphasize its particular value for very small values of $n$, where you don't want to hold out lots of data.
-
-... HOGG: Figure~\ref{fig:LOO1} illustrates the process of leave-one-out fitting and prediction.
+Given a data set (location--data pairs $t_i, y_i$), what is the best way to empirically estimate, from those data, the out-of-sample prediction error---that is, how do you estimate how well you are likely to predict new data?
+The only good answer to this is cross-validation:
+In cross-validation, we leave out a part of the data (in the most extreme form, leave out one single data point at a time), train the model using all but the left-out part, and predict the left-out part.
+Then this process is iterated over all choices of what part (or point) to leave out.
+This process is illustrated in \figurename~\ref{fig:LOO1}, where we show $23$ fits, each of which is trained to the 22 points left when we leave one of the $n=23$ points out.
+Also shown is the prediction, in each leave-one-out fit, for the left-out point.
 \begin{figure}[t]
@@
 
-...
-HOGG: Figure~\ref{fig:LOO2} shows the mean-squared leave-one-out cross-validation estimate of mean squared prediction error as a function of the number of features $p$ for the feature-weighted OLS and for the limiting Gaussian process.
+The prediction for the mean-squared error (MSE) for new data is the mean of the square of the differences between the leave-one-out predictions and the left-out data.
+This leave-one-out cross-validation MSE (CVMSE) will be different for different choices for the basis, size ($p$), and regularization of the fits you do.
+It is a fairly reliable and well-studied method for assessing predictive accuracy (HOGG: WHAT TO CITE HERE?), although it does depend on some assumptions (for example, about the distribution of predictive information across individual data points, maybe).
+An example of CVMSE for two models (the feature-weighted OLS and the ridge regression) are shown for our toy data, as a function of the number of features $p$, in \figurename~\ref{fig:LOO2}.
+The predictive accuracy is a strong function of $p$!
 \begin{figure}[t]
@@
     \caption{Leave-one-out cross-validation estimates of mean squared prediction error for the feature-weighted OLS fits, as a function of the number of features $p$.
-In detail the first (lowest-$t$) and last (highest-$t$) data points were not used in computing the mean squared error.
-Note that the predictions are much, much worse at $p\approx n$ than they are at very low or very high $p$.
-HOGG THIS FIGURE CAPTION IS NOT COMPLETE}
+Also shown are the same for ridge regression with $\lambda=0.1$ and also the Gaussian process introduced in \sectionname~\ref{sec:gp} and shown in \figurename~\ref{fig:gp}.
+The GP result is shown as a flat line because it doesn't have an associated number $p$.
+In detail the first (lowest-$t$) and last (highest-$t$) data points were not used in computing the mean squared error; that choice is debatable, but we are imagining an assessment of the quality of the \emph{interpolations}, not extrapolations, of these models.
+Note that the OLS predictions are much, much worse at $p\approx n$ (notice all the orders of magnitude on the vertical axis) than they are at very low or very high $p$, but that ridge regression protects the fits.}
     \label{fig:LOO2}
@@
 \end{figure}
-For the cross-validation we excluded the end points; that is, for robustness, we didn't leave out and predict the first and last point.
-That choice isn't necessarily justifiable!
-HOGG say more things here.
 
-Now say things about how things go to h*ck when the number of parameters $p$ gets close to the number of data points $n$.
+In particular, the CVMSE for the feature-weighted OLS fits is bad when $p\approx n$, and much better at $p\ll n$ and $p \gg n$.
+This phenomenology is not particular to this problem.
+It is extremely general.
+There is an effect known in many kinds of regression called ``double descent'' or ``peaking phenomenon'' in which predictive accuracy becomes very poor when the number of free parameters $p$ comes close to the number of data points $n$ (SOLEDAD CITE THINGS).
+The fundamental reason for this phenomenon is ... SOLEDAD WORDS HERE.
 
-... The CV MSE gets really bad at $p\approx n$. That's not a coincidence. Reasons. Citations.
+The CVMSE gets better and worse at different values of $p$;
+and it even gets really \emph{good} at particular values of $p$.
+That's not surprising; there are places where the fit basis is just appropriate for your specific problem.
+These good-CVMSE places are the best places to work, if you can afford to search for them and find them.
+In general, if you care about predictive accuracy, it is worth doing a search for the values of $p$ (and other hyper-parameters, like regularization strengths and feature-weighting function parameters) that minimize the CVMSE.
+The minimum-CVMSE choices for $p$ and the hyper-parameters will generally be very close to the choices that lead to the best predictions for new data.
 
-... You can avoid this with.... reasons. Citations.
-
-HOGG: The CV MSE gets really \emph{good} at particular values of $p$.
-That's not surprising; there are places where the fit basis is just appropriate for your specific problem.
-These are the best places to work, if you can afford to search for them and find them.
-
-HOGG: ADD SOMEWHERE ABOVE HERE: You might feel uncomfortable with dropping individual points in this problem, since the points are regularly spaced to begin with, and become irregularly spaced when you leave one out.
+By the way, you might have felt uncomfortable with dropping individual points in this problem, since the points are regularly spaced in the location space (the $t$ space) to begin with, and become irregularly spaced when you leave one out.
 How much does this matter?
-It probably does matter in detail, but you don't have much choice in problems like this.
+It probably \emph{does} matter in detail, but you don't have much choice in problems like this.
 All empirical measures of predictive accuracy have these kinds of problems.
 
-\section{The Gaussian process: The limit of infinite features}
+\section{The Gaussian process: The limit of infinite features}\label{sec:gp}
 
 The Gaussian process (GP) is a non-parametric regression that takes training data $y_i$ at coordinates $t_i$, plus a kernel function, and makes predictions $\hat{y}_\ast$ for new data at new positions $t_\ast$.
-The Gaussian process math looks like
-\begin{equation}
+The Gaussian process mean prediction looks like%
+\begin{equation}\label{eq:gpmean}
     \hat{Y}_\ast = K_\ast\,K^{-1}\,Y
@@
 where $K_\ast$ is the rectangular kernel matrix between test locations $t_\ast$ and training locations $t_i$, while $K$ is the square kernel matrix between training locations and themselves
-\begin{equation}
+\begin{equation}\label{eq:Kmatrix}
     [K]_{i,i'} = k(t_i,t_{i'})
@@
 where $k(\cdot,\cdot)$ is a non-negative definite definite kernel function.
+Stated this simply, the GP looks like magic; our goal here is to connect this to the feature-weighted OLS from \sectionname~\ref{sec:fwols}.
 
-HOGG: What does it mean for a kernel function to be non-negative definite?
+First, what does it mean for a kernel function $k(\cdot,\cdot)$ to be non-negative definite?
+It means that no matter what set of $n$ locations $t_i$ you choose, the kernel matrix $K$ made from the function according to \eqref{eq:Kmatrix} has only non-negative, real eigenvalues.
+The kernel function must be non-negative definite because, among other things, it is describing the variance of a function, and variances are always non-negative.
+It turns out that you can guarantee that a kernel function is non-negative definite if you can show that it is, itself, the Fourier transform of a non-negative function.
+(It is \emph{not} required, however, that the function $k(\cdot,\cdot)$ itself be non-negative at all values of the inputs; non-negative definiteness is a different condition.)
 
-HOGG: Note that this is not a full GP, which has both a mean and a variance. This is strictly just the MEAN of a GP. Also that this is a Wiener filter or kriging.
+Although the kernel matrix $K$ is, by construction, always non-negative definite, it can have extremely bad or even infinite condition number.
+That is, it can lead your code or implementation into very unstable linear-algebra operations.
+We discuss these issues below in \sectionname~\ref{sec:implementation}.
 
-HOGG: Note that $K$ can have extremely bad or even infinite condition number; see the implementation notes in \sectionname~\ref{sec:implementation}.
+Above, we called the GP prediction the ``mean''. This is because the Gaussian process is a model for a mean \emph{and variance} in function space.
+In addition to the mean $\hat{Y}_\ast$ predicted in \eqref{eq:gpmean}, the GP also predicts a \emph{variance} in the $Y_\ast$ space around that mean.
+In this \documentname, we are going to treat the GP as producing only a mean prediction, where the shape of the kernel function matters, but the amplitude of the kernel function does not (the prediction is a ratio of kernel matrices, so the kernel amplitudes cancel).
+However, in Bayesian-inference contexts the amplitude of the GP kernel is important, and the predicted variances are important.
+(There is an additional point worthy of mention here, which is that the expression \eqref{eq:gpmean} is implicitly for a GP with a zero prior mean; there is a more general expression that subtracts a prior mean function from the $Y$ values and adds the prior mean back in to the $\hat{Y}_\ast$ values.)
+When we consider only the mean prediction of the GP, as we do here, then the GP is a kind of linear filter that operates on data $Y$ and predicts or interpolates to new data $Y_\ast$.
+Classically, this linear filter is sometimes called a Wiener filter (more on this in a moment) or \emph{kriging} (HOGG CITE).
 
-There is a strong connection between OLS and the GP.
-In particular, when the features $x_j$ form [some kind of] basis, and we take the limit of infinite features ($p\rightarrow\infty$) we get kernel matrices in place of the $X\,\Lambda^{-1}\,X^\top$ matrix products;
+Importantly for us, there is a strong connection between the feature-weighted OLS and the GP.
+In particular, when the features $x_j$ form some kind of (SOLEDAD: WHAT TO SAY HERE?) basis, and we take the limit of infinite features ($p\rightarrow\infty$) we get kernel matrices in place of the $X\,\Lambda^{-1}\,X^\top$ matrix products;
 \begin{align}
@@
 
-HOGG: Remind the reader that there are hundreds of known kernel functions you can have here, and hundreds of corresponding weighting functions $f(\omega)$, and that is just in this Fourier basis; there are more in other bases (polynomial, wavelet, and so on).
+In our toy examples, we use the feature weighting that generates the Mat\'ern 3/2 kernel.
+It is important to emphasize that there are literally infinite alternative choices that can be made here, and hundreds even if you restrict to kernels with known closed forms.
+Indeed, any function $F(t-t')$ that has a finite, all-positive Fourier transform $f^2(\omega)$ can be substituted for the Mat\'ern kernel and associated frequency weighting function we use here.
 
-HOGG: The kernel in equation \eqref{eq:k} is a stationary kernel, meaning it depends only on absolute values of time differences $|t - t'|$.
+The particular kernel we obtain in equation \eqref{eq:k} is a stationary kernel, meaning it depends only on absolute values of time differences $|t - t'|$.
 Not all $p\rightarrow\infty$ kernels will be stationary.
@@
 Sines and cosines form a basis for translation-invariant function spaces. SOLEDAD: IS THIS WORDING OKAY?
+If we had made a different choice for our basis, such as polynomials or wavelets, we would have obtained a non-stationary kernel in the $p\rightarrow\infty$ limit.
 
@@
 As before, in contexts where you have independent uncertainties on each element $y_i$ of your training data $Y$, $C^{-1}$ would naturally be set to the diagonal matrix containing the inverses of the variances of those uncertainties (so $C$ would contain the variances).
-This form \eqref{eq:gpC} is used a lot in astronomy and physics (HOGG CITE SOME THINGS?) and it is also the standard form given for the Wiener filter (CITE).
+This form \eqref{eq:gpC} is used a lot in astronomy and physics (HOGG CITE SOME THINGS?) and it is also the standard form given for the Wiener filter, where the kernel function generating $K$ is the Fourier tranform of the ``signal power'' and the kernel function generating $C$ is the Fourier transform of the ``noise power''.
 
@@
 These four different sources of uncertainty propagate differently and are differently ``simple'' to deal with.
-
-In particular... (1) and (2) easy, (3) and (4) hard.
-
-SOLEDAD SAYS: Maybe re-order 1 - 3 - 2 - 4.
+In particular it turns out that the easiest sources of uncertainty to understand and propagate are those coming from (1)~the noise in the $y_i$ and (2)~the number $n$ and locations $t_i$ of the data.
+The uncertainty coming from (3)~uncertainties in the locations $t_i$, and (4)~model choices are much harder to model and propagate.
 
@@
 
-\section{Discussion}
+\section{Discussion}\label{sec:discussion}
 
@@
 
+HOGG: Instead of WEIGHTING features that are regularly spaced in frequency space with a weighting function $f(\omega)$, we could have generated RANDOM features from a distribution $f^2(\omega)$.
+That is the approach in some machine-learning contexts (SOLEDAD CITE HERE).
+The same GP limit would appear at $p\rightarrow\infty$ (provided we choose some random phases too).
+These random-feature approaches have rarely been used in the natural sciences, but they are potentially of interest in the future.
+
 \raggedright
@@
 
+\appendix
+\section{Mathematical arguments and results}
+
+SOLEDAD says: \emph{Hello World!}
+
 \end{document}

### 2020-12-10 paper/main.tex

@@
 Then this process is iterated over all choices of what part (or point) to leave out.
-This process is illustrated in \figurename~\ref{fig:LOO1}, where we show $23$ fits, each of which is trained to the 22 points left when we leave one of the $n=23$ points out.
+This process is illustrated in \figurename~\ref{fig:loo}, where we show $23$ fits, each of which is trained to the 22 points left when we leave one of the $n=23$ points out.
 Also shown is the prediction, in each leave-one-out fit, for the left-out point.
@@
 HOGG anything else to say here?}
-    \label{fig:LOO1}
+    \label{fig:loo}
     \end{mdframed}
@@
 It is a fairly reliable and well-studied method for assessing predictive accuracy (HOGG: WHAT TO CITE HERE?), although it does depend on some assumptions (for example, about the distribution of predictive information across individual data points, maybe).
-An example of CVMSE for two models (the feature-weighted OLS and the ridge regression) are shown for our toy data, as a function of the number of features $p$, in \figurename~\ref{fig:LOO2}.
+An example of CVMSE for two models (the feature-weighted OLS and the ridge regression) are shown for our toy data, as a function of the number of features $p$, in \figurename~\ref{fig:cv}.
 The predictive accuracy is a strong function of $p$!
@@
 In detail the first (lowest-$t$) and last (highest-$t$) data points were not used in computing the mean squared error; that choice is debatable, but we are imagining an assessment of the quality of the \emph{interpolations}, not extrapolations, of these models.
-Note that the OLS predictions are much, much worse at $p\approx n$ (notice all the orders of magnitude on the vertical axis) than they are at very low or very high $p$, but that ridge regression protects the fits.}
-    \label{fig:LOO2}
+Note that the OLS predictions are much, much worse at $p\approx n$ (check out all the orders of magnitude on the vertical axis) than they are at very low or very high $p$, but that ridge regression doesn't show this behavior.}
+    \label{fig:cv}
     \end{mdframed}
@@
 In particular it turns out that the easiest sources of uncertainty to understand and propagate are those coming from (1)~the noise in the $y_i$ and (2)~the number $n$ and locations $t_i$ of the data.
-The uncertainty coming from (3)~uncertainties in the locations $t_i$, and (4)~model choices are much harder to model and propagate.
+The uncertainties coming from (3)~uncertainties in the locations $t_i$, and (4)~model choices, are both much harder to model and propagate.
 
@@
 Give the explicit formula for jackknife, with its dimensionless prefactor.
-Note the similarity between jackknife and cross-validation; that's relevant and important!
+\begin{equation}
+    \hat{\Sigma}_\ast = \frac{n-1}{n}\,\sum_i \hat{Y}_{\ast i}\,\hat{Y}_{\ast i}^\top
+    ~,
+\end{equation}
+where $\hat{\Sigma}_\ast$ is the jackknife estimate of the variance tensor of the uncertainty on the full-data prediction $\hat{Y}_\ast$,
+and $\hat{Y}_{\ast i}$ is the estimate of $Y_\ast$ made after \emph{leaving out} the one training point $t_i, y_i$.
+The square-root of the trace of this uncertainty variance (that is, what you might call the jackknife estimate of the standard error) is shown in \figurename~\ref{fig:uncertainty}.
+Note the similarity between jackknife and cross-validation; that's relevant and important; these empirical estimates of uncertainty and prediction error are closely related.
+\begin{figure}[t]
+    \begin{mdframed}
+    \includegraphics[width=\figurewidth]{paper/uncertainty.pdf}
+    \caption{The jackknife-estimated uncertainty on an ordinary least squares fit.
+What is shown is the diagonal of the empirical jackknife estimate $\hat{\Sigma}$ of the variance tensor on the prediction $\hat{Y}_\ast$ of an OLS fit.
+In other words, the off-diagonal entries of $\hat{\Sigma}_\ast$ are being ignored here; there are important covariances that are hard to visualize (and beyond our scope).
+The one-sigma region is larger than the span of the jackknife trials; this is because the jackknife trials are strongly correlated (see text HOGG IS IT THERE?).}
+    \label{fig:uncertainty}
+    \end{mdframed}
+\end{figure}
 
@@
 Although the examples are toys, the implementation of everything can be generalized for real-data situations.
-In that code, there are some aspects of the linear-algebra implementation that might seem odd....HOGG
+In that code, there are some aspects of the linear-algebra implementation that might seem odd.
+Here are some comments.
 
-Things here about \code{inv(A) @ b}, \code{solve(A, b)}, \code{lstsq(A, b, rcond=tiny)}, and so on. Be sure to talk about the GP as well as the OLS cases here.
+Mostly, linear algebra stability comes down to the condition number of the matrix in question.
+This, for our purposes, is the ratio of the largest eigenvalue (for non-negative definite matrices) to the smallest \emph{non-zero} eigenvalue.
+For rectangular matrices it is the ratio of the largest singular value (that is, what you get out of a singular value decomposition) to the smallest nonzero singular value.
 
-How to do a pseudo-inverse that is numerically safe. It requires an RCOND or equivalent.
+When the condition number is large, different linear-algebra approaches will differ.
+For example, the function call \code{solve(A, b)} should give you the best estimate it can for the product $A^{-1}\,b$, whereas the function call \code{dot(inv(A), b)}, which is the same on paper, will give you the dot product between \code{b} and the best estimate that \code{inv()} can find for the inverse of \code{A}.
+When the condition number of $A$ is large, these two values will diverge, and the \code{solve()} will be better (this claim contradicts what is stated in the abstract of \citealt{solve}, but this claim is based on real experiments on real matrices, so we stand by it).
+Use \code{solve(A, b)} and never \code{dot(inv(A), b)}.
 
-Note that once $p$ is large enough, if you are using a feature weighting that declines with $p$, at some point, at machine precision, the additional columns you are adding to $X$ are effectively all zeros.
-That's not a problem if you implement your linear algebra well, but it does mean that your cross-validations will saturate at some $p$ (see the \figurename).
+If your condition number gets very large, even \code{solve()} can give bad results, because very small eigenvalues of the matrix are being poorly estimated and then inverted.
+That's unstable.
+It is better to zero out those small eigenvalues---it is better to destroy bad information than to use it---and perform a pseudo-inverse in those cases.
+So if you really want to be safe (and you do, here) you should really use \code{lstsq(A, b, rcond=tiny)} instead of \code{solve(A, b)}.
+The \code{lstsq()} function requires a \code{rcond} input, which says at what (dimensionless) precision to zero-out low eigenvalues.
+It usually makes sense to set this dimensionless \code{rcond} input to something like machine precision, which is about \code{1e-16} for our current hardware--software setups.
 
-Things here about not constructing operators that are almost entirely zeros.
+You might think that all of this is academic, but it really isn't when the number of features $p$ is within a factor of a few of the number of data points $n$.
+For example, in our toy-data OLS experiments in this paper with $n=23$, the matrix $X^\top\,X$ has a condition number (ratio of largest eigenvalue to smallest nonzero eigenvalue) that saturates machine precision for the entire range $12 < p < 50$!
 
-Set your hyper-parameters by cross-validation. Set $p$, choice of basis, choice of weighting, regularization parameters all this way. Get explicit about CV.
+Related to this, if you have a choice between formulations that involve an inverse $(X^\top\,X)^{-1}\,X^\top\,Y$ and formulations that involve a pseudo-inverse $X^\dagger\,Y$, you should do the latter, because $X^\top\,X$ has the \emph{square} of the condition number of $X$.
+When you want to execute $X^\dagger\,Y$, as we do in \eqref{eq:OLS3}, you should again use \code{lstsq()}, which was literally designed for these applications; use \code{lstsq(X, Y, rcond=tiny)}.
+This function returns the best estimate it can for $X^\dagger\,Y$, so
+it should be better than computing a pseudo-inverse \code{pinv(X)} and then matrix-multiplying \code{pinv(X)} with \code{Y}.
+Again here it usually makes sense to set this \code{rcond} input to something like machine precision.
+
+Once $p$ is large enough, if you are using a feature weighting with $\Lambda^{-1}$ with diagonal entries $[\Lambda^{-1}]_{jj}$ that decline with $j$, at some point, at machine precision, the additional columns you are adding to $X$ are effectively all zeros.
+They will literally underflow the linear-algebra representation.
+That's not a problem if you implement your linear algebra well (that is, use \code{lstsq()} appropriately), but it does mean that your predictions and cross-validations will saturate at some $p$ (as we see them do in \figurename~\ref{fig:cv}).
+
+In multiple places, but especially \eqref{eq:LambdaC1} and \eqref{eq:LambdaC2}, you are performing operations on matrices that are diagonal ($C$ and $\Lambda$ and their inverses are all diagonal).
+You should avoid ever constructing diagonal matrices.
+You can multiply $X$ or $X^\top$ by a diagonal matrix by just multiplying the rows (or columns) by the diagonal entries.
+And you can invert by just inverting the diagonal entries.
+Avoid constructing and operating on operators that are almost entirely zeros.
 
@@
 
-\raggedright
+{\raggedright
 \bibliographystyle{authordate1}
 \bibliography{references}
+}
 
@@
 
-SOLEDAD says: \emph{Hello World!}
+SOLEDAD: Maybe how you get from the optimization statements to the closed-form solutions, for the under- and over-parameterized cases?
+
+SOLEDAD: Maybe prove the equivalence of the expressions with $C$ and $\Lambda$.
+
+SOLEDAD: Maybe sketch some arguments about double descent?
+
+SOLEDAD: Other math details?
+
+HOGG: Maybe show that lstsq beats solve, which beats inv?
 

### 2020-12-10 paper/main.tex
uncertainties

@@
 
-Alternatively, if you are unhappy with the three choices of basis, and order, and regularization, you might decide to avoid such decisions and go fully \emph{non-parametric}:
+Alternatively, if you are unhappy with the three choices of basis, order, and regularization, you might decide to avoid such decisions and go fully \emph{non-parametric}:
 Instead of fitting a basis expansion, you can use a strict interpolator (like a cubic spline), or you can fit a Gaussian process to your data.
@@
 
-HOGG: If you have a full likelihood function, you can use it to get uncertainties.
-Give example!
-But this is not conservative; or it makes many strong assumptions.
-Sometimes you don't even know enough about your data to write down a LF you believe.
-Give some examples for the different regimes.
+In the best-case scenario, you might have accurate estimates of the variances $[C]_{ii} = \sigma_i^2$ of the noise contributions affecting your training data values $y_i$, the noise might be Gaussian with zero mean, you might have locations $t_i$ that are extremely accurately known, and you might have justifiable prior variances $[\Lambda]_{jj}$ on your parameters $\beta_j$.
+In this case, you can assume that the linear model with $p$ parameters is a good model for your data, and write down a likelihood function and a prior.
+In this best-case scenario, you can turn the Bayesian crank and and deliver a posterior density or a marginalized likelihood for the predicted values $Y_\ast$ at the test locations $t_\ast$.
+The second derivative of the ln of the marginalized likelihood can then be processed into an uncertainty on the predictions $\hat{Y}_\ast$.
+The details of this are way beyond the scope of this \documentname, but this (or a closely related) problem is discussed in some detail by us elsewhere (\citealt{products}).
 
-HOGG: Bayes has even more assumptions than the LF uncertainty estimates. But gives well-defined uncertainties automatically.
+That scenario is best-case, but it does involve a lot of assumptions.
+That is, if you don't trust your estimates of the noise variances, or if you think the noise might be non-Gaussian, or if you don't have plausible prior information, then the likelihood approaches will give poor uncertainty estimates.
+In this sense, it is more conservative to make use of more empirical methods for uncertainty estimation.
+The leading candidates are jackknife or bootstrap resamplings (HOGG CITE SOMETHING?).
+Here we will focus on jackknife.
 
-HOGG: If you want to be conservative, use jackknife to get the uncertainties.
-Explain how this works, and how to implement in the large-$n$ case.
-Repeat some of the fitting examples but showing the uncertainties as well.
-Give the explicit formula for jackknife, with its dimensionless prefactor.
-\begin{equation}
-    \hat{\Sigma}_\ast = \frac{n-1}{n}\,\sum_i \hat{Y}_{\ast i}\,\hat{Y}_{\ast i}^\top
+The idea of jackknife resampling is that we make $k$ subsamples of the data, in each of which we have dropped (or held out) a unique fraction $1/k$ of the data.
+The variance of the results (in this case the prediction $\hat{Y}_\ast$) across the jackknife samples can be transformed into an estimate of the variance of the estimator acting on the full data set.
+In the most extreme form---leave-one-out jackknife---we set $k=n$.
+In this case, the jackknife estimate $\hat{\Sigma}_\ast$ of the variance of the best-fit predictions $\hat{Y}_\ast$ is given by
+\begin{equation}\label{eq:jackknife}
+    \hat{\Sigma}_\ast = \frac{n-1}{n}\,\sum_{i=1}^n (\hat{Y}_{\ast i} - \hat{Y}_\ast)\,(\hat{Y}_{\ast i} - \hat{Y}_\ast)^\top
     ~,
 \end{equation}
-where $\hat{\Sigma}_\ast$ is the jackknife estimate of the variance tensor of the uncertainty on the full-data prediction $\hat{Y}_\ast$,
-and $\hat{Y}_{\ast i}$ is the estimate of $Y_\ast$ made after \emph{leaving out} the one training point $t_i, y_i$.
-The square-root of the trace of this uncertainty variance (that is, what you might call the jackknife estimate of the standard error) is shown in \figurename~\ref{fig:uncertainty}.
+where $\hat{Y}_{\ast i}$ is the estimate of $Y_\ast$ made after \emph{leaving out} the one training point $t_i, y_i$, and $\hat{Y}_\ast$ is the estimate made using \emph{all} the data.
+The pre-factor $(n-1)/n$ in \eqref{eq:jackknife} is not anything like the $1/(n-1)$ that you use when you estimate a standard variance; this difference comes from the fact that the jackknife subsamples are extremely correlated; the pre-factor is computed to amplify the jackknife variance into an unbiased estimate of the variance of the estimator $\hat{Y}_\ast$.
+The square-root of the trace of this uncertainty variance $\hat{\Sigma}$ (that is, what you might call the jackknife estimate of the standard error) is shown in \figurename~\ref{fig:uncertainty}.
 Note the similarity between jackknife and cross-validation; that's relevant and important; these empirical estimates of uncertainty and prediction error are closely related.
@@
 In other words, the off-diagonal entries of $\hat{\Sigma}_\ast$ are being ignored here; there are important covariances that are hard to visualize (and beyond our scope).
-The one-sigma region is larger than the span of the jackknife trials; this is because the jackknife trials are strongly correlated (see text HOGG IS IT THERE?).}
+The one-sigma region is larger than the span of the jackknife trials; this is because the jackknife trials are strongly correlated.}
     \label{fig:uncertainty}
@@
 
-HOGG: As for (3): Resample the $t_i$ values maybe?
-Another option is to linearize if the uncertainties are small wrt function changes (see, eg GP literature).
-Or infer and marginalize out (ferociously expensive).
+These methods---full likelihood analysis and jackknife---take into account (1)~the noise in the data $y_i$ and (2)~the number and spacing of the training data points.
+They do not, by themselves, take into account (3)~the uncertainties on the locations $t_i$.
+There are no simple methods for uncertainty propagation from the locations $t_i$ into the predictions $\hat{Y}_\ast$.
+One option is to resample the $t_i$ according to your uncertainty estimates, and re-do the fits.
+That's potentially expensive, and overly conservative (because it ignores the information about the $t_i$ coming from the $y_i$).
+Another is to linearize the first derivative of the best-fit curve $y(t)$ and propagate uncertainty using those derivatives.
+This is not conservative, because it only works if the location uncertainties are small relative to substantial changes in the slope of the predictions with $t$.
+The most extreme option would be to \emph{simultaneously fit} for the prediction $\hat{Y}_\ast$ and \emph{all} of the noisily measured $t_i$.
+That's a great idea, but that fit would be extremely computationally expensive, and no reasonable fit objective would be convex.
+All of these ideas are out of scope here.
 
-HOGG: As for (4): Brute-force search? It isn't really possible to do (4) without a model for the behavior of a scientist!! Refer back to the subjectivity of it all.
+Finally, in order to take account of (4)~the uncertainty coming from your choices of basis, $p$, regularization, you might have to know (or learn) the distribution over \emph{these} things.
+Since these choices are hyper-parameters, any inference that propagates uncertainties coming from these choices would have to be hierarchical in structure.
+That is way, way out of scope.
 
@@
 
-Mostly, linear algebra stability comes down to the condition number of the matrix in question.
-This, for our purposes, is the ratio of the largest eigenvalue (for non-negative definite matrices) to the smallest \emph{non-zero} eigenvalue.
-For rectangular matrices it is the ratio of the largest singular value (that is, what you get out of a singular value decomposition) to the smallest nonzero singular value.
+Mostly, linear algebra stability comes down to the \emph{condition number} of the matrix in question.
+The condition number, for our purposes, is the ratio of the largest eigenvalue (for non-negative definite matrices) to the smallest \emph{non-zero} eigenvalue.
+For rectangular feature matrices it is the ratio of the largest singular value (that is, what you get out of a singular value decomposition) to the smallest nonzero singular value.
 
@@
 
-Related to this, if you have a choice between formulations that involve an inverse $(X^\top\,X)^{-1}\,X^\top\,Y$ and formulations that involve a pseudo-inverse $X^\dagger\,Y$, you should do the latter, because $X^\top\,X$ has the \emph{square} of the condition number of $X$.
+Related to this, if you have a choice between formulations that involve an inverse of a square, like $(X^\top\,X)^{-1}\,X^\top\,Y$, and formulations that involve a pseudo-inverse, like $X^\dagger\,Y$, you should do the latter, because $X^\top\,X$ has the \emph{square} of the condition number of $X$.
 When you want to execute $X^\dagger\,Y$, as we do in \eqref{eq:OLS3}, you should again use \code{lstsq()}, which was literally designed for these applications; use \code{lstsq(X, Y, rcond=tiny)}.
@@
 Avoid constructing and operating on operators that are almost entirely zeros.
+
+And finally, it is most numerically stable to operate on the smallest matrices you can.
+For example, when you have the choice between the formulation in equation \eqref{eq:LambdaC1} and that in equation \eqref{eq:LambdaC2}, you should choose the former when $p<n$ and the latter when $p>n$.
+That way you are always doing the heavy linear algebra (\code{solve()} and \code{lstsq()} function calls) at a size $\min(p, n)$, which is both faster and more stable than linear algebra at $\max(p, n)$.
+And it is much faster when you make these choices correctly:
+Linear algebra scales naively as the dimension \emph{cubed}.
+(In practice---with excellent packages---it actually scales with a power more like 2.6 than 3, but still!)
 
@@
 
+SOLEDAD: Maybe words or thoughts about Mercer's theorem and when the Fourier-transform correspondence we use here is applicable (and when it is not)?
+
 SOLEDAD: Other math details?

### 2020-12-11 paper/main.tex
references, SV content, tweaks

@@
 % -----
+% - Make sure that what we say about kriging and Wiener are correct.
+% - Are we clear that the feature weighting is a kind of regularization?
+I (DWH) think it IS because it affects how the L2 on beta affects different parameters.
+SV says that maybe we should get explicit about the regularization points, and when the regularization is implicit or hidden.
+% - In uncertainties, we talk about Bayesian. Should we also talk about frequentist and/or information theory?
 % - Audit for the use of "points" and "locations" and "data" to make sure all is consistent. The ts are locations, the ys are data.
@@
 % - Audit for hyphens in under-parameterization and re-weighting and so on? Hyphenated words or single words? Make decisions and stick to them.
-% - Needs a bibliography; should we use bibtex?
-% - Add acknowledgements: Sam Roweis (deceased), Dan Foreman-Mackey (Flatiron), Teresa Huang (JHU), Rachel Ward (UT Austin), Bernhard Sch\"olkopf (MPI-IS); who else??
 
@@
 
-\section*{\raggedright Fitting very flexible models: Linear regression with large numbers of parameters\footnote{Hello world?}}
+\section*{\raggedright Fitting very flexible models: Linear regression with large numbers of parameters%
+\footnote{%
+It is a pleasure to thank
+Dan Foreman-Mackey (Flatiron),
+Teresa Huang (JHU),
+Sam Roweis (deceased),
+Adrian Price-Whelan (Flatiron),
+Bernhard Sch\"olkopf (MPI-IS), and
+Rachel Ward (UT Austin)
+for valuable conversations and input.
+SV is partially funded by NSF DMS 2044349, EOARD FA9550-18-
+1-7007, and the NSF-Simons Research Collaboration on the Mathematical and Scientific
+Foundations of Deep Learning (MoDL) (NSF DMS 2031985)}}
 
@@
 It is even possible to take the limit of infinite parameters, at which, if the basis and regularization are chosen correctly, the least-squares fit becomes the mean of a Gaussian process (or, equivalently, a Wiener filter or kriging).
-Although there are often good fits with small numbers of parameters and also with very large numbers of parameters, the dangerous regime for linear fitting is when the number of parameters is comparable to the number of data points (the double-descent or peaking-phenomenon regime); we discuss this problem and how to ameliorate or avoid it.
+Although there are often good fits with small numbers of parameters and also with very large numbers of parameters, the dangerous regime for linear fitting is when the number of parameters is comparable to the number of data points (the double-descent or peaking-phenomenon regime); we discuss this problem and how to avoid it.
+We also comment on model selection, uncertainty estimation, and computational implementation.
 
@@
 
-HOGG: There are other contexts in which, recently, regressions have gone to very large numbers of parameters.
-For example, when there are many possible natural features...
-Pixels in an image or spectrum...
-etc...
-Deep learning and etc.
-This isn't our context!
-But it is relevant and related.
-Many good books exist, for example (HOGG CITE VARIOUS).
+In this \documentname, we treat applications that look like interpolation; there are many other contexts in which regressions have gone to very large numbers of parameters.
+For example, there are contexts in which there are enormous numbers of possible natural features, like for instance when the data are images or videos: Every pixel of every frame of the video---or any linear (or nonlinear) combination of pixels---can become a feature for the regression.
+Also, there are contexts in which features are generated randomly from, say, a space of functions that can act on the natural features (\citealt{rahimi2007random}).
+These settings are not what we are addressing here, but they are relevant and related
+(many good books exist, for example: \citealt{bishop, esl, agresti, gelman}).
+In some ways, the most flexible of models currently in use are deep networks, where it is both the case that the input data often have enormous numbers of natural features, \emph{and} the deep network is capable of generating (effectively) far more, internally.
 
@@
 Alternative common choices would be to make the embedding fumctions $g_j(t)$ polynomials or other kinds of ordered basis functions, such as wavelets or spherical harmonics (the latter if, say, the $t_i$ are positions on the sphere).
-Another choice that isn't common in the natural sciences, but highly studied in machine learning (for example, SOLEDAD CITE RANDOM FEATURES PAPER), is to choose the features randomly from a distribution (rather than on a regular grid in frequency, as we do here).
+Another choice that isn't common in the natural sciences, but highly studied in machine learning (for example, \cite{rahimi2007random}), is to choose the features randomly from a distribution (rather than on a regular grid in frequency, as we do here).
 That is beyond our scope, but we come back to it in \sectionname~\ref{sec:discussion}.
@@
 This isn't true!
-The only limits on inference are given by information theory, and information theory makes no reference to the \emph{number} of anything, parameters or data.
+Not only is it the case that we \emph{can} work at $p>n$, in many cases we \emph{should} work at $p>n$, and many real-world regressions do.
 But it is true that the $p>n$ regime is indeed strange!
@@
 The limit $p\rightarrow\infty$ of $X\,\Lambda^{-1}\,X^\top$ in \eqref{eq.limit} leads to a stationary kernel $k(\cdot,\cdot)$ because the feature embedding in $X$ is a set of sines and cosines.
-Sines and cosines form a basis for translation-invariant function spaces. SOLEDAD: IS THIS WORDING OKAY?
+Sines and cosines form a basis for translation-invariant function spaces.
 If we had made a different choice for our basis, such as polynomials or wavelets, we would have obtained a non-stationary kernel in the $p\rightarrow\infty$ limit.
@@
 In this case, you can assume that the linear model with $p$ parameters is a good model for your data, and write down a likelihood function and a prior.
-In this best-case scenario, you can turn the Bayesian crank and and deliver a posterior density or a marginalized likelihood for the predicted values $Y_\ast$ at the test locations $t_\ast$.
-The second derivative of the ln of the marginalized likelihood can then be processed into an uncertainty on the predictions $\hat{Y}_\ast$.
+In this best-case scenario, you can turn the Bayesian crank and deliver a posterior density for the predicted values $Y_\ast$ at the test locations $t_\ast$.
+The second derivative of the ln of the posterior density can then be processed into a standard error on the predictions $\hat{Y}_\ast$ (or you can deliver full posterior densities somehow).
 The details of this are way beyond the scope of this \documentname, but this (or a closely related) problem is discussed in some detail by us elsewhere (\citealt{products}).
@@
 In other words, the off-diagonal entries of $\hat{\Sigma}_\ast$ are being ignored here; there are important covariances that are hard to visualize (and beyond our scope).
-The one-sigma region is larger than the span of the jackknife trials; this is because the jackknife trials are strongly correlated.}
+The one-sigma region is larger than the span of the jackknife trials; this is because the jackknife trials are strongly correlated; the jackknife formula \eqref{eq:jackknife} commpensates for those correlations.}
     \label{fig:uncertainty}
@@
 HOGG: Instead of WEIGHTING features that are regularly spaced in frequency space with a weighting function $f(\omega)$, we could have generated RANDOM features from a distribution $f^2(\omega)$.
-That is the approach in some machine-learning contexts (SOLEDAD CITE HERE).
+That is the approach in some machine-learning contexts \cite{rahimi2007random}.
 The same GP limit would appear at $p\rightarrow\infty$ (provided we choose some random phases too).
 These random-feature approaches have rarely been used in the natural sciences, but they are potentially of interest in the future.
+
+HOGG: Discuss stationarity and Fourier basis, and kernel choice being equivalent to choosing a kernel.
+
+% end matter
 

### 2020-12-12 paper/main.tex
discussion; now at zeroth draft state

@@
 It is a pleasure to thank
+Jed Brown (CU Boulder),
 Dan Foreman-Mackey (Flatiron),
@@
 For example, the function call \code{solve(A, b)} should give you the best estimate it can for the product $A^{-1}\,b$, whereas the function call \code{dot(inv(A), b)}, which is the same on paper, will give you the dot product between \code{b} and the best estimate that \code{inv()} can find for the inverse of \code{A}.
-When the condition number of $A$ is large, these two values will diverge, and the \code{solve()} will be better (this claim contradicts what is stated in the abstract of \citealt{solve}, but this claim is based on real experiments on real matrices, so we stand by it).
-Use \code{solve(A, b)} and never \code{dot(inv(A), b)}.
+When the condition number of $A$ is large, these two values will diverge, and the \code{solve()} will be better (this claim contradicts what is stated in the abstract of \citealt{solve}, but this claim is based on our real experiences with real matrices, so we stand by it).
+Use \code{solve(A, b)} and never \code{dot(inv(A), b)} unless there are compelling code-structure reasons to use the latter, such as repeated calls (but even then, a Cholesky decomposition and Cholesky-solves are probably more stable).
 
@@
 
-HOGG: What main points did we make; what do we want you to take home? HOGG: Related: Why were we motivated to write this document?
+This \documentname\ was about linear fitting with very flexible models, for interpolation, prediction, and de-noising of data.
+We encouraged you to consider using very big models, but being intentional about regularization.
+These settings (over-parameterized, but carefully regularized) are adaptive and useful, and they connect, as we showed, to Gaussian processes in the limit, which are well-studied workhorses of data science.
 
-(HOGG: Say something about the case in which you have prior beliefs about the expected values of the parameters. THERE IS A PLACEHOLDER for this in the section about the over-parameterized case.)
+All the rage these days, is instead \emph{nonlinear fitting}, with things like deep learning and variational autoencoders and the like (HOGG CITE).
+We didn't discuss any of that.
+However, many of the high-level lessons in this \documentname\ carry over:
+All of these tools work well when the function space is flexible but also carefully regularized.
+In these nonlinear settings, regularization takes many additional new forms, like early stopping (HOGG CITE?), dropouts (HOGG CITE), and restricted network structure (such as convolutional; HOGG CITE).
 
-TODO:
-\begin{itemize}
-    \item Higher dimensions for the ambient space. Spherical harmonics.
-    \item The practice: design features for linear regression, how many do you choose, avoid pitfalls, when to go to Gaussian processes. Cross-validation. Everything an astronomer needs to know.
-    \item Discuss L1 and sparsity.
-In general in these flexible contexts, sparsity is usually not important.
-But if it is important, L1 is a good tool.
-AND you can get both the smoothness you want AND the sparsity if you do feature weighting and L1 (instead of feature weighting and L2, as we do here).
-Cite (https://arxiv.org/pdf/1308.0759.pdf).
-    \item cite stuff!
-\end{itemize}
+We only considered the setting in which you care about predicting new data $Y_\ast$ and never the setting in which you care about the internal parameters $\beta$ of the linear fit.
+However, if you are, say, measuring the power spectrum of a process (as we do, often, in cosmology), then you care about these amplitudes themselves.
+In this case, any regularization you apply takes the role of a prior or prior information.
+That prior must be chosen (in those cases) with great care, because the answers you get will be influenced by that choice; when it doesn't properly conform to your true beliefs, your answers will be distorted in bad ways.
+And, technically, when you take this view (that the parameters $\beta$ matter), you also have to get serious about the noise model on the data.
+That is, the beliefs encoded in the data noise variance tensor $C$ also must represent your true beliefs if you don't want your answers distorted in bad ways.
+All of that is out of scope here, but we say things about it all elsewhere (\citealt{fitting}).
 
-HOGG: In what sense are these flexible models the same as things like interpolators, running means, filters, and so on?
-All I got is that if they are linear---meaning that the prediction $\hat{Y}_\ast$ can be written as a linear operator acting on the training data $Y$---then they probably can be written in some form like feature-weighted OLS in the $p>>n$ regime.
+In many cases, when the goal is just to interpolate or de-noise data, in the natural sciences, investigators use running means (or medians), low-pass filters, or explicit interpolators (like cubic spline interpolation).
+These methods all have close relationships with what is written here.
+Indeed, a running mean, a low-pass filter, and a cubic-spline interpolator can all be written as a linear operator (the details of which depends on the locations $t_i$ of the data) acting on the input data vector $Y$, just like our linear fits produce linear operators.
+This means that in many cases, these methods can be translated into versions of the methods we present in this \documentname.
+A full translation is beyond our scope, though.
+And our view is that the value of being explicit about the basis and the regularization makes the linear fitting approach better in general.
 
-HOGG: Instead of WEIGHTING features that are regularly spaced in frequency space with a weighting function $f(\omega)$, we could have generated RANDOM features from a distribution $f^2(\omega)$.
-That is the approach in some machine-learning contexts \cite{rahimi2007random}.
-The same GP limit would appear at $p\rightarrow\infty$ (provided we choose some random phases too).
-These random-feature approaches have rarely been used in the natural sciences, but they are potentially of interest in the future.
+Regularization was perhaps the biggest theme of this \documentname.
+But we only really considered variants of L2 regularization (or ridge or Tikhonov).
+There are other regularizations, even other convex regularizations.
+A valuable and useful option is L1 or the lasso (HOGG CITE), which encourages sparsity---it encourages parameters $\beta_j$ to take the value $\beta_j=0$ exactly, where possible.
+This kind of regularization makes sense when we have prior beliefs that the functional forms we seek will in fact be sparse in our chosen basis.
+Usually this kind of consideration is less important in interpolation, prediction, and de-noising settings, but it is not unheard of.
+A nice recent result is that the feature weighting that we employ here can be used with L1 regularization to obtain simultaneously smoothness and sparsity (SOLEDAD CITE https://arxiv.org/pdf/1308.0759.pdf).
 
-HOGG: Discuss stationarity and Fourier basis, and kernel choice being equivalent to choosing a kernel.
+We discussed deterministic, ordered expansions like Fourier series and polynomials, but there is another class of \emph{random features} methods (see, for example, \citealt{rahimi2007random}) that we did not discuss.
+Briefly, the idea with random features is that instead of weighting features that are regularly spaced in frequency space with a weighting function $f(\omega)$, we could have generated features randomly from a probability distribution $\propto f^2(\omega)$.
+The same Gaussian process limit appears as $p\rightarrow\infty$ (provided we choose those features with appropriately random phases too).
+These random-feature approaches have rarely been used in the natural sciences, but they are potentially of interest in many applications.
+
+In the toy examples used throughout this \documentname, we considered data with locations $t_i$ in a one-dimensional location space or ambient space.
+This was a choice for simplicity of visualization; nothing is fundamental about the locations being one-dimensional.
+The only considerations about dimensionality is that the functions $g_j(t)$ have to act correctly on the locations $t_i$ whatever their size or shape.
+In astronomy and cosmology contexts, it is common for the locations $t_i$ to be positions on the sphere, and it is common for the natural basis functions to be spherical harmonics, for example.
+
+In our toy examples, we used a Fourier series.
+That is just one choice among many.
+However, \emph{it is often a great choice}.
+When you choose the Fourier basis (and---importantly---for every cosine term you include the corresponding sine term), the matrix $X\,\Lambda^{-1}\,X^\top$ (and the limiting kernel matrix $K$ at $p\rightarrow\infty$) has the property that every matrix element $[X\,\Lambda^{-1}\,X^\top]_{ii'}$ depends (or can be calculated from) just the absolute difference $|t_i-t_{i'}|$.
+That is, in this basis, all fitting methods become technically \emph{stationary}.
+This all relates to the translation-independence properties of the Fourier basis.
+So although the Fourier basis is just one choice among many, it is the \emph{right choice} when you think your problem has (or might have) certain kinds of translation invariances.
 

### 2020-12-13 paper/main.tex
kill a HOGG; tweaks

@@
 % -----
-% - Make sure that what we say about kriging and Wiener are correct.
+% - Make sure that what we say about Wiener filtering are correct.
 % - Are we clear that the feature weighting is a kind of regularization?
@@
   linewidth=0.5pt,
-  roundcorner=5pt,
+  roundcorner=1pt,
   shadow=false,
-  shadowcolor=black!05,
-  shadowsize=4pt
+  %shadowcolor=black!05,
+  %hadowsize=4pt
 }
@@
 1-7007, and the NSF-Simons Research Collaboration on the Mathematical and Scientific
-Foundations of Deep Learning (MoDL) (NSF DMS 2031985)}}
+Foundations of Deep Learning (MoDL) (NSF DMS-2031985).}}
 
@@
 
-HOGG: Now do the full generalization with $C$ and $\Lambda$ and explain how the matrix inversion formula (CITE SOMETHING) makes these two expressions equivalent:
+In the most general case, you have not just a set of feature weights $\Lambda^{-1}$, you also have a set of data-point weights $C^{-1}$ (which, in standard settings, would be the inverses of the variances of the noise affecting the data points $y_i$).
+When you put these all together, the feature-weighted, data-weighted least squares precitions are given by either of these two equivalent expressions:
 \begin{align}\label{eq:LambdaC1}
@@
 \end{align}
-Either leave the proof to the reader or make it an exercise HOGG: Check the units.
-And continue discussion of connections to Bayesian inference.
-Explain that these forms are good because they relieve the fits of the burden of going exactly through every data point.
-This is more responsive to the real situation of noisy data, and permits smoother solutions.
-HOGG: AND return to units again. And cite products again.
+We discuss the equivalence of these below in \appendixname~\ref{app:math}.
+These expressions appear in Bayesian-inference contexts (see, for example \citealt{products}) when $\Lambda$ is the variance of the prior on the parameter vector $\beta$ and $C$ is the variance of the noise on the data vector $Y$.
+In those contexts, the units of $C$ would be the units of $Y$ squared, and the units of $\Lambda$ would be the square of the ratio of the units of $Y$ to the units of $X$ (the square of the units of $\beta$.
+These weighted-feature, weighted-data least-square forms are good because (if the weightings are chosen appropriately) they lead to smooth solutions that are not required to pass precisely through every data point.
+This is appropriate in common, real situations in which data are noisy and the world is smooth.
+Which form you choose, between \eqref{eq:LambdaC1} and \eqref{eq:LambdaC2}, depends on a few things, but primarily $p/n$.
+If $p<n$ it's both faster and more stable to use \eqref{eq:LambdaC1}; if $p>n$ it's faster and more stable to use \eqref{eq:LambdaC2}.
 
@@
 Also ploted on each of the 23 lines is the prediction made for that fit's held-out data point.
-HOGG anything else to say here?}
+Some of the predictions don't appear within the plot window, because the predictions obtain large amplitudes at the edges.}
     \label{fig:loo}
@@
 In detail the first (lowest-$t$) and last (highest-$t$) data points were not used in computing the mean squared error; that choice is debatable, but we are imagining an assessment of the quality of the \emph{interpolations}, not extrapolations, of these models.
-Note that the OLS predictions are much, much worse at $p\approx n$ (check out all the orders of magnitude on the vertical axis) than they are at very low or very high $p$, but that ridge regression doesn't show this behavior.}
+Note that the OLS predictions are much, much worse at $p\approx n$ (check out all the orders of magnitude on the vertical axis) than they are at very low or very high $p$, but that ridge regression doesn't show this behavior.
+(HOGG MAKE SURE THIS POINT APPEARS IN THE MAIN TEXT).}
     \label{fig:cv}
@@
 Importantly for us, there is a strong connection between the feature-weighted OLS and the GP.
-In particular, when the features $x_j$ form some kind of (SOLEDAD: WHAT TO SAY HERE?) basis, and we take the limit of infinite features ($p\rightarrow\infty$) we get kernel matrices in place of the $X\,\Lambda^{-1}\,X^\top$ matrix products;
+In particular, when the features $x_j$ form some kind of (SOLEDAD: WHAT TO SAY HERE?
+reproducing?
+Hilbert?
+...?) basis, and we take the limit of infinite features ($p\rightarrow\infty$) we get kernel matrices $K$ in place of the $X\,\Lambda^{-1}\,X^\top$ matrix products:
 \begin{align}
@@
 As before, in contexts where you have independent uncertainties on each element $y_i$ of your training data $Y$, $C^{-1}$ would naturally be set to the diagonal matrix containing the inverses of the variances of those uncertainties (so $C$ would contain the variances).
-This form \eqref{eq:gpC} is used a lot in astronomy and physics (HOGG CITE SOME THINGS?) and it is also the standard form given for the Wiener filter, where the kernel function generating $K$ is the Fourier tranform of the ``signal power'' and the kernel function generating $C$ is the Fourier transform of the ``noise power''.
+This form \eqref{eq:gpC} is used a lot in astronomy and physics (HOGG CITE SOME THINGS?) and it is also the standard form given for the Wiener filter, where the kernel function generating $K$ is the Fourier transform of the ``signal power'' and the kernel function generating $C$ is the Fourier transform of the ``noise power''.
 
@@
 You might think that all of this is academic, but it really isn't when the number of features $p$ is within a factor of a few of the number of data points $n$.
-For example, in our toy-data OLS experiments in this paper with $n=23$, the matrix $X^\top\,X$ has a condition number (ratio of largest eigenvalue to smallest nonzero eigenvalue) that saturates machine precision for the entire range $12 < p < 50$!
+For example, in our toy-data OLS experiments in this paper with $n=23$, the matrix $X^\top\,X$ has a condition number (ratio of largest eigenvalue to smallest nonzero eigenvalue) that saturates machine precision for the entire range $12 < p < 50$.
 
@@
 We only considered the setting in which you care about predicting new data $Y_\ast$ and never the setting in which you care about the internal parameters $\beta$ of the linear fit.
-However, if you are, say, measuring the power spectrum of a process (as we do, often, in cosmology), then you care about these amplitudes themselves.
+However, if you are, say, measuring the power spectrum of a process (as we are, often, in cosmology), then you care about these amplitudes themselves.
 In this case, any regularization you apply takes the role of a prior or prior information.
@@
 However, \emph{it is often a great choice}.
-When you choose the Fourier basis (and---importantly---for every cosine term you include the corresponding sine term), the matrix $X\,\Lambda^{-1}\,X^\top$ (and the limiting kernel matrix $K$ at $p\rightarrow\infty$) has the property that every matrix element $[X\,\Lambda^{-1}\,X^\top]_{ii'}$ depends (or can be calculated from) just the absolute difference $|t_i-t_{i'}|$.
+When you choose the Fourier basis (and---importantly---for every cosine term you include the corresponding sine term), the matrix $X\,\Lambda^{-1}\,X^\top$ (and the limiting kernel matrix $K$ at $p\rightarrow\infty$) has the property that every matrix element $[X\,\Lambda^{-1}\,X^\top]_{ii'}$ depends on (or can be calculated from) just the absolute difference $|t_i-t_{i'}|$.
 That is, in this basis, all fitting methods become technically \emph{stationary}.
@@
 \appendix
-\section{Mathematical arguments and results}
+\section{Mathematical arguments and results}\label{app:math}
 

### 2020-12-16 paper/main.tex
Updates from Overleaf

@@
 % -----
+% - Note that we made the toy examples on a regular grid in t-space. That isn't required or assumed anywhere in the text; that's just a choice for the toy.
 % - Make sure that what we say about Wiener filtering are correct.
@@
 % - Audit for hyphens in under-parameterization and re-weighting and so on? Hyphenated words or single words? Make decisions and stick to them.
+% - HOGG: List clearly the assumptions underlying CVMSE and jackknife. They make assumptions about independence of the data points and also something maybe about per-point information content.
 
@@
 
+\usepackage{comment}
 % Price-Whelan's figure hacks
@@
 
-If you have encountered and solved problems like these, you have made these three kinds of choices (sometimes implcitly).
+If you have encountered and solved problems like these, you have made these three kinds of choices (sometimes implicitly).
 The second choice---about the number of coefficients to fit---is usually made heuristically, and often subject to the strongly believed opinion that you \emph{must have fewer parameters than data points}.
@@
 Example functions $g_j(t)$ from this basis are shown in \figurename~\ref{fig:basis}.
-Alternative common choices would be to make the embedding fumctions $g_j(t)$ polynomials or other kinds of ordered basis functions, such as wavelets or spherical harmonics (the latter if, say, the $t_i$ are positions on the sphere).
+Alternative common choices would be to make the embedding functions $g_j(t)$ polynomials or other kinds of ordered basis functions, such as wavelets or spherical harmonics (the latter if, say, the $t_i$ are positions on the sphere).
 Another choice that isn't common in the natural sciences, but highly studied in machine learning (for example, \cite{rahimi2007random}), is to choose the features randomly from a distribution (rather than on a regular grid in frequency, as we do here).
@@
     ~.
+    \label{OLS-under}
 \end{equation}
@@
 
-The prediction \eqref{eq:OLS} when $p<n$ (the under-paraemeterized or traditional regime) is \emph{affine invariant} in that $p$-dimensional rotations or rescalings of the rectangular $X$ design matrix do not affect predictions.
+The prediction \eqref{eq:OLS} when $p<n$ (the under-parameterized or traditional regime) is \emph{affine invariant} in that $p$-dimensional rotations or rescalings of the rectangular $X$ design matrix do not affect predictions.
 That is, if $R$ is an invertible $p\times p$ matrix, the prediction using $X'\leftarrow X\,R$ will be identical to the prediction using the original $X$.
@@
 The ridge-regularized prediction for new data looks like
-\begin{equation}
+\begin{equation} \label{eq:ridge}
     \hat{Y}_\ast = X_\ast\,(X^\top\,X + \lambda\,I)^{-1}\,X^\top\,Y
@@
 The three fits are very different, but they all go through all the data points exactly.
-As $p$ gets large, the fit function approaches $y=0$ almost everywhere; this is a consequence of Parseval's Theorem (see text).}
+As $p$ gets large, the fit function approaches $y=0$ almost everywhere; this is a consequence of Plancharel's Theorem (see text).}
     \label{fig:ols2}
@@
 It is slightly off-topic to notice that in \figurename~\ref{fig:ols2}, as $p$ gets very large, the OLS solution approaches $y=0$ everywhere that it can.
-This behavior is a direct consequence of Parseval's identity, which states that the Fourier transform is unitary.
-This means that the integral over frequency of the square of the Fourier transform is equal (up to a factor of $2\pi$) to the integral over location of the square of the original function.
+This behavior is a direct consequence of Plancharel's theorem, which states that the Fourier transform is unitary (see for instance \citealt{folland2016course}).
+This means that the integral over frequency of the square of the Fourier transform is equal to the integral over location of the square of the original function.
 Thus the min-norm solution delivered by OLS, which chooses the interpolating function that minimizes the squares of the component amplitudes in the Fourier basis used to make \figurename~\ref{fig:ols2} will also choose the interpolating function that minimizes the square of the value of the function.
@@
 That is, rotations and scalings in the feature space \emph{will} affect predictions.
-It behooves us to re-scale the features (the $p$ $n$-vectors of the design matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features (SOLEDAD CITE WARD; OTHERS?).
+It behooves us to re-scale the features (the $p$ $n$-vectors of the design matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features (\cite{xie2020weighted}, \cite{bah2016sample}, \cite{rauhut2016interpolation}).
 We can encode these feature weights in a $p\times p$ diagonal weight matrix $\Lambda^{-1}$ and the prediction becomes
@@
 In the most general case, you have not just a set of feature weights $\Lambda^{-1}$, you also have a set of data-point weights $C^{-1}$ (which, in standard settings, would be the inverses of the variances of the noise affecting the data points $y_i$).
-When you put these all together, the feature-weighted, data-weighted least squares precitions are given by either of these two equivalent expressions:
+When you put these all together, the feature-weighted, data-weighted least squares predictions are given by either of these two equivalent expressions:
 \begin{align}\label{eq:LambdaC1}
@@
 If $p<n$ it's both faster and more stable to use \eqref{eq:LambdaC1}; if $p>n$ it's faster and more stable to use \eqref{eq:LambdaC2}.
+We show a toy example of a fit with both feature weights $\Lambda^{-1}$ and data weights $C^{-1}$ in \figurename~\ref{fig:fwwls}.
+\begin{figure}[t]
+    \begin{mdframed}
+    \includegraphics[width=\figurewidth]{paper/weighted-WLS.pdf}
+    \caption{Comparison of the feature-weighted OLS shown in \figurename~\ref{fig:fwols} to the same but also including data weights $C^{-1}$, as in equations \eqref{eq:LambdaC1} and \eqref{eq:LambdaC2}.
+    Similarly to \figurename~\ref{fig:wls}, the data weights on the diagonal of $C^{-1}$ are the inverses of the squares of the uncertainties shown as vertical error bars.
+The feature weights encourage the prediction to be smooth; the data weights permit it to be even smoother because they permit the prediction to miss the training data.
+    Prediction results now depend on the specific amplitude or prefactor multiplying the feature weights; a particular value of $0.07\,f^2(\omega)$ was chosen for the feature weights for this demonstration.}
+    \label{fig:fwwls}
+    \end{mdframed}
+\end{figure}
 
@@
 The 23 lines are the 23 fits, for each of which one data point was held out.
-Also ploted on each of the 23 lines is the prediction made for that fit's held-out data point.
+Also plotted on each of the 23 lines is the prediction made for that fit's held-out data point.
 Some of the predictions don't appear within the plot window, because the predictions obtain large amplitudes at the edges.}
@@
 This leave-one-out cross-validation MSE (CVMSE) will be different for different choices for the basis, size ($p$), and regularization of the fits you do.
-It is a fairly reliable and well-studied method for assessing predictive accuracy (HOGG: WHAT TO CITE HERE?), although it does depend on some assumptions (for example, about the distribution of predictive information across individual data points, maybe).
+It is a fairly reliable and well-studied method for assessing predictive accuracy (see, for example, \citealt{cv}), although it does depend on some assumptions (for example, about the distribution of predictive information across individual data points, maybe).
 An example of CVMSE for two models (the feature-weighted OLS and the ridge regression) are shown for our toy data, as a function of the number of features $p$, in \figurename~\ref{fig:cv}.
-The predictive accuracy is a strong function of $p$!
+The predictive accuracy is indeed a function of $p$.
 \begin{figure}[t]
@@
 In detail the first (lowest-$t$) and last (highest-$t$) data points were not used in computing the mean squared error; that choice is debatable, but we are imagining an assessment of the quality of the \emph{interpolations}, not extrapolations, of these models.
-Note that the OLS predictions are much, much worse at $p\approx n$ (check out all the orders of magnitude on the vertical axis) than they are at very low or very high $p$, but that ridge regression doesn't show this behavior.
-(HOGG MAKE SURE THIS POINT APPEARS IN THE MAIN TEXT).}
+Note that the OLS predictions are much, much worse at $p\approx n$ (check out all the orders of magnitude on the vertical axis) than they are at very low or very high $p$, but that ridge regression doesn't show this behavior.}
     \label{fig:cv}
@@
 It is extremely general.
-There is an effect known in many kinds of regression called ``double descent'' or ``peaking phenomenon'' in which predictive accuracy becomes very poor when the number of free parameters $p$ comes close to the number of data points $n$ (SOLEDAD CITE THINGS).
-The fundamental reason for this phenomenon is ... SOLEDAD WORDS HERE.
+There is an effect known in many kinds of regression called ``double descent'' or ``peaking phenomenon'' in which predictive accuracy becomes very poor when the number of free parameters $p$ comes close to the number of data points $n$ \cite{jain198239, spigler2018jamming, geiger2019jamming}.
+In particular, for linear models, the ``risk''---the out-of-sample prediction error---blows up when the model capacity just reaches overfitting; at $p=n$ \cite{hastie2019surprises}.
+The fundamental reason for this phenomenon is that the ordinary least squares estimates \eqref{eq:OLS} and \eqref{eq:OLS2} require to compute the inverses $(X^\top X)^{-1}$ and $(XX^\top)^{-1}$ respectively, which are very badly conditioned around $p\approx n$.
+This translates on a large variance for the estimator $\hat \beta$ which implies a large risk.
+This behavior disappears with many forms of regularization, including Tikhonov regularization (also known as ridge regression, as described in \eqref{eq:ridge}), early stopping \citep{hastie2019surprises}, and dimensionality reduction \citep{huang2020dimensionality}.
 
@@
 \end{equation}
-where $k(\cdot,\cdot)$ is a non-negative definite definite kernel function.
+where $k(\cdot,\cdot)$ is a positive semi-definite kernel function.
 Stated this simply, the GP looks like magic; our goal here is to connect this to the feature-weighted OLS from \sectionname~\ref{sec:fwols}.
 
-First, what does it mean for a kernel function $k(\cdot,\cdot)$ to be non-negative definite?
-It means that no matter what set of $n$ locations $t_i$ you choose, the kernel matrix $K$ made from the function according to \eqref{eq:Kmatrix} has only non-negative, real eigenvalues.
-The kernel function must be non-negative definite because, among other things, it is describing the variance of a function, and variances are always non-negative.
-It turns out that you can guarantee that a kernel function is non-negative definite if you can show that it is, itself, the Fourier transform of a non-negative function.
-(It is \emph{not} required, however, that the function $k(\cdot,\cdot)$ itself be non-negative at all values of the inputs; non-negative definiteness is a different condition.)
+First, what does it mean for a kernel function $k(\cdot,\cdot)$ to be positive semi-definite?
+It means that no matter what set of $n$ locations $t_i$ you choose, the $n\times n$ kernel matrix $K$ made from the function according to \eqref{eq:Kmatrix} has only non-negative, real eigenvalues.
+The kernel function must be positive semi-definite because, among other things, it is describing the variance of a process, and variances are always non-negative.
+It turns out that you can guarantee that a kernel function is positive semi-definite if you can show that it is, itself, the Fourier transform of a non-negative function (this fact is known as Bochner's Theorem, see for instance \citealt{folland2016course}).
+(It is \emph{not} required, however, that the function $k(\cdot,\cdot)$ itself be non-negative at all values of the inputs; non-negative definiteness is a different condition entirely.)
 
-Although the kernel matrix $K$ is, by construction, always non-negative definite, it can have extremely bad or even infinite condition number.
+Although the kernel matrix $K$ is, by construction, always positive semi-definite, it can have extremely bad or even infinite condition number.
 That is, it can lead your code or implementation into very unstable linear-algebra operations.
@@
 When we consider only the mean prediction of the GP, as we do here, then the GP is a kind of linear filter that operates on data $Y$ and predicts or interpolates to new data $Y_\ast$.
-Classically, this linear filter is sometimes called a Wiener filter (more on this in a moment) or \emph{kriging} (HOGG CITE).
+Classically, this linear filter is sometimes called a Wiener filter (more on this in a moment) or \emph{kriging} (possibly because of \citealt{krige}).
 
 Importantly for us, there is a strong connection between the feature-weighted OLS and the GP.
-In particular, when the features $x_j$ form some kind of (SOLEDAD: WHAT TO SAY HERE?
-reproducing?
-Hilbert?
-...?) basis, and we take the limit of infinite features ($p\rightarrow\infty$) we get kernel matrices $K$ in place of the $X\,\Lambda^{-1}\,X^\top$ matrix products:
+In particular, when we take the limit of infinite features ($p\rightarrow\infty$; provided the limit exists) we get kernel matrices $K$ in place of the $X\,\Lambda^{-1}\,X^\top$ matrix products:
 \begin{align}
@@
 
-The connection between the infinite basis chosen (the form and weighting of the features) and the kernel function is governed by Mercer's theorem (CITE).
+The connection between the infinite basis chosen (the form and weighting of the features) and the kernel function is governed by Mercer's theorem (see \citealt{minh2006mercer}).
 However, if the basis is Fourier, as we chose above in \eqref{eq:basis}, and the spacing between modes ($\Delta\omega =\omega_{j+2}-\omega_j$) is small enough, the kernel becomes very close to the Fourier transform of the square of the weighting function $f(\omega)$ we use to weight the features.
 
-That is, in the case of the specific example of weight function $f(\omega)$ given in equation \eqref{eq:f}, we can connect our feature-weighted OLS to an equivalent GP if we know the fourier transform of the square of $f(\omega)$.
+That is, in the case of the specific example of weight function $f(\omega)$ given in equation \eqref{eq:f}, we can connect our feature-weighted OLS to an equivalent GP if we know the Fourier transform of the square of $f(\omega)$.
 We chose that specific form for $f(\omega)$ because it has a square that is a member of a Fourier-transform pair:
@@
 As before, in contexts where you have independent uncertainties on each element $y_i$ of your training data $Y$, $C^{-1}$ would naturally be set to the diagonal matrix containing the inverses of the variances of those uncertainties (so $C$ would contain the variances).
-This form \eqref{eq:gpC} is used a lot in astronomy and physics (HOGG CITE SOME THINGS?) and it is also the standard form given for the Wiener filter, where the kernel function generating $K$ is the Fourier transform of the ``signal power'' and the kernel function generating $C$ is the Fourier transform of the ``noise power''.
+This form \eqref{eq:gpC} is used a lot in astronomy and cosmology (for example, \citealt{zaroubi, aigrain, celerite}) and it is also the standard form given for the Wiener filter, where the kernel function generating $K$ is the Fourier transform of the ``signal power'' and the kernel function generating $C$ is the Fourier transform of the ``noise power''.
+In this form, the amplitude or prefactor or magnitude of the kernel function matters, because it is competing, in some sense, the variance $K$ of the GP against the variance $C$ of the noise.
+It is not sufficient to get the shape of the kernel function right to make a stable prediction of the mean, when using this form \eqref{eq:gpC}.
 
@@
 In this sense, it is more conservative to make use of more empirical methods for uncertainty estimation.
-The leading candidates are jackknife or bootstrap resamplings (HOGG CITE SOMETHING?).
+The leading candidates are jackknife or bootstrap resamplings (for example, \citealt{bootjack}).
 Here we will focus on jackknife.
@@
 In other words, the off-diagonal entries of $\hat{\Sigma}_\ast$ are being ignored here; there are important covariances that are hard to visualize (and beyond our scope).
-The one-sigma region is larger than the span of the jackknife trials; this is because the jackknife trials are strongly correlated; the jackknife formula \eqref{eq:jackknife} commpensates for those correlations.}
+The one-sigma region is larger than the span of the jackknife trials; this is because the jackknife trials are strongly correlated; the jackknife formula \eqref{eq:jackknife} compensates for those correlations.}
     \label{fig:uncertainty}
@@
 
-Finally, in order to take account of (4)~the uncertainty coming from your choices of basis, $p$, regularization, you might have to know (or learn) the distribution over \emph{these} things.
+Finally, in order to take account of (4)~the uncertainty coming from your choices of basis, number $p$, and regularization, you might have to know (or learn) the distribution over \emph{these} things.
 Since these choices are hyper-parameters, any inference that propagates uncertainties coming from these choices would have to be hierarchical in structure.
@@
 
-All of the code used to make the figures for this \documentname\ is available publicly at HOGG WHERE?
+All of the code used to make the figures for this \documentname\ is available publicly\footnote{\url{https://github.com/davidwhogg/FlexibleLinearModels}}.
 Although the examples are toys, the implementation of everything can be generalized for real-data situations.
@@
 For example, the function call \code{solve(A, b)} should give you the best estimate it can for the product $A^{-1}\,b$, whereas the function call \code{dot(inv(A), b)}, which is the same on paper, will give you the dot product between \code{b} and the best estimate that \code{inv()} can find for the inverse of \code{A}.
-When the condition number of $A$ is large, these two values will diverge, and the \code{solve()} will be better (this claim contradicts what is stated in the abstract of \citealt{solve}, but this claim is based on our real experiences with real matrices, so we stand by it).
+When the condition number of $A$ is large, these two values can be very different, and the \code{solve()} will be better (this claim contradicts what is stated in the abstract of \citealt{solve}, but this claim is based on our real experiences with real matrices, so we stand by it).
 Use \code{solve(A, b)} and never \code{dot(inv(A), b)} unless there are compelling code-structure reasons to use the latter, such as repeated calls (but even then, a Cholesky decomposition and Cholesky-solves are probably more stable).
@@
 
-You might think that all of this is academic, but it really isn't when the number of features $p$ is within a factor of a few of the number of data points $n$.
+You might think that all of this is academic, but it really isn't when the number of features $p$ is close to the number of data points $n$.
 For example, in our toy-data OLS experiments in this paper with $n=23$, the matrix $X^\top\,X$ has a condition number (ratio of largest eigenvalue to smallest nonzero eigenvalue) that saturates machine precision for the entire range $12 < p < 50$.
+And that's for $n=23$; things generally get worse as $n$ gets larger.
 
@@
 
-Once $p$ is large enough, if you are using a feature weighting with $\Lambda^{-1}$ with diagonal entries $[\Lambda^{-1}]_{jj}$ that decline with $j$, at some point, at machine precision, the additional columns you are adding to $X$ are effectively all zeros.
+Once $p$ is large enough, if you are using a feature weighting with $\Lambda^{-1}$ with diagonal entries $[\Lambda^{-1}]_{jj}$ that decrease to zero with $j$, at some point, at machine precision, the additional columns you are adding to $X$ are effectively all zeros.
 They will literally underflow the linear-algebra representation.
@@
 
-All the rage these days, is instead \emph{nonlinear fitting}, with things like deep learning and variational autoencoders and the like (HOGG CITE).
+All the rage these days, is instead \emph{nonlinear fitting}, with \emph{deep learning} and the like (\citealt{deep}, for example).
 We didn't discuss any of that.
@@
 All of these tools work well when the function space is flexible but also carefully regularized.
-In these nonlinear settings, regularization takes many additional new forms, like early stopping (HOGG CITE?), dropouts (HOGG CITE), and restricted network structure (such as convolutional; HOGG CITE).
+In these nonlinear settings, regularization takes many additional new forms, like early stopping (\citealt{earlystop}), dropout (\citealt{dropout}), and restricted network structure (such as convolutional; see for example \citealt{bishop}).
 
@@
 There are other regularizations, even other convex regularizations.
-A valuable and useful option is L1 or the lasso (HOGG CITE), which encourages sparsity---it encourages parameters $\beta_j$ to take the value $\beta_j=0$ exactly, where possible.
+A valuable and useful option is L1 or the lasso (\citealt{lasso}), which encourages sparsity---it encourages parameters $\beta_j$ to take the value $\beta_j=0$ exactly, where possible.
 This kind of regularization makes sense when we have prior beliefs that the functional forms we seek will in fact be sparse in our chosen basis.
 Usually this kind of consideration is less important in interpolation, prediction, and de-noising settings, but it is not unheard of.
-A nice recent result is that the feature weighting that we employ here can be used with L1 regularization to obtain simultaneously smoothness and sparsity (SOLEDAD CITE https://arxiv.org/pdf/1308.0759.pdf).
+A nice recent result is that the feature weighting that we employ here can be used with L1 regularization to obtain simultaneously smoothness and sparsity \citep{rauhut2016interpolation}.
 
 We discussed deterministic, ordered expansions like Fourier series and polynomials, but there is another class of \emph{random features} methods (see, for example, \citealt{rahimi2007random}) that we did not discuss.
-Briefly, the idea with random features is that instead of weighting features that are regularly spaced in frequency space with a weighting function $f(\omega)$, we could have generated features randomly from a probability distribution $\propto f^2(\omega)$.
+Briefly, the idea with random features is that instead of weighting features that are regularly spaced in frequency space with a weighting function $f(\omega)$, we could have generated unweighted features but randomly from a probability distribution $\propto f^2(\omega)$.
 The same Gaussian process limit appears as $p\rightarrow\infty$ (provided we choose those features with appropriately random phases too).
@@
 In astronomy and cosmology contexts, it is common for the locations $t_i$ to be positions on the sphere, and it is common for the natural basis functions to be spherical harmonics, for example.
+
+We also generated our toy data with locations $t_i$ regularly spaced in the location space.
+None of our results or recommendations depend on the locations being equally spaced.
+The simple form for the feature weighting we suggest does, however, depend on the features being equally spaced in \emph{frequency} space.
+
+The methods in this \documentname\ are all \emph{discriminative}, in the sense that we took the locations $t_i$ to be prior or primary;
+the goal was to find a function of locations $t_i$ that predicts data $y_i$.
+This asymmetry between the locations and the data led to concerning statements in \sectionname~\ref{sec:uncertainty} when we considered the possibility that the locations $t_i$ themselves might be noisy or uncertain.
+An alternative formulation to these discriminative models are \emph{generative} models, in which the model attempts not just to predict the $y_i$ from the $t_i$ but instead predicts both the $t_i$ and the $y_i$.
+A model that generates both can be used to make predictions $y_\ast$ at new locations $t_\ast$ by executing an inference or inverse problem on the generative model.
+Generative models are generally non-convex---and harder to execute---if you want the relationship between the $t_i$ and the $y_i$ to be nonlinear.
+You don't get closed-form solutions, and there aren't known guarantees (like the Gauss--Markov theorem) about performance.
+But they are more general, and often more appropriate, especially when both the locations $t_i$ and the data $y_i$ are comparably noisy measurements.
 
@@
 
+\textsl{t. b. d.}\begin{comment}
 SOLEDAD: Maybe how you get from the optimization statements to the closed-form solutions, for the under- and over-parameterized cases?
@@
 SOLEDAD: Other math details?
-
-HOGG: Maybe show that lstsq beats solve, which beats inv?
+\end{comment}
 

### 2020-12-16 paper/main.tex
Updates from Overleaf

@@
 where $I$ is the $p\times p$ identity.
-In the language of Bayesian inference, $\lambda$ can be seen as a prior variance for the parameters $\beta_j$.
+In the language of Bayesian inference, $\lambda$ can be seen as the inverse of a prior variance for the parameters $\beta_j$.
 The salutary effect of the ridge regularization is shown in \figurename~\ref{fig:ridge}.
@@
 We'll discuss this form \eqref{eq:foo} more below in \sectionname~\ref{sec:fwols},
-but briefly we can say here that it appears in Bayesian inference contexts where the data points $y_i$ are treated as having Gaussian noise associated with them (with known variance tensor $C$) and there is a Gaussian prior on the parameter vector $\beta$ (with known variance $\Lambda$).
+but briefly we can say here that it appears in Bayesian inference contexts where the data points $y_i$ are treated as having Gaussian noise associated with them (with known variance tensor $C$) and there is a Gaussian prior on the parameter vector $\beta$ (with known variance $\Lambda^{-1}$).
 We have discussed that model elsewhere (\citealt{products}).
-It is also useful sometimes to think of the ``units'' or dimensions of the quantities in \eqref{eq:foo}: In the Bayesian setting, the units of $C$ would be the square of the units of $Y$ and the units of $\Lambda$ would be the square of the units of the ratio $Y/X$ (the square of the units of $\beta$).
+It is also useful sometimes to think of the ``units'' or dimensions of the quantities in \eqref{eq:foo}: In the Bayesian setting, the units of $C$ would be the square of the units of $Y$ and the units of $\Lambda^{-1}$ would be the square of the units of the ratio $Y/X$ (the square of the units of $\beta$).
 
@@
 We discuss the equivalence of these below in \appendixname~\ref{app:math}.
-These expressions appear in Bayesian-inference contexts (see, for example \citealt{products}) when $\Lambda$ is the variance of the prior on the parameter vector $\beta$ and $C$ is the variance of the noise on the data vector $Y$.
-In those contexts, the units of $C$ would be the units of $Y$ squared, and the units of $\Lambda$ would be the square of the ratio of the units of $Y$ to the units of $X$ (the square of the units of $\beta$.
+These expressions appear in Bayesian-inference contexts (see, for example \citealt{products}) when $\Lambda^{-1}$ is the variance of the prior on the parameter vector $\beta$ and $C$ is the variance of the noise on the data vector $Y$.
+In those contexts, the units of $C$ would be the units of $Y$ squared, and the units of $\Lambda^{-1}$ would be the square of the ratio of the units of $Y$ to the units of $X$ (the square of the units of $\beta$.
 These weighted-feature, weighted-data least-square forms are good because (if the weightings are chosen appropriately) they lead to smooth solutions that are not required to pass precisely through every data point.
@@
 The feature weights encourage the prediction to be smooth; the data weights permit it to be even smoother because they permit the prediction to miss the training data.
-    Prediction results now depend on the specific amplitude or prefactor multiplying the feature weights; a particular value of $0.07\,f^2(\omega)$ was chosen for the feature weights for this demonstration.}
+    Prediction results now depend on the specific amplitude or prefactor multiplying the feature weights; a particular value of $0.07\,f^2(\omega)$ was chosen for the diagonal of the feature weight matrix $\Lambda^{-1}$ for this demonstration.}
     \label{fig:fwwls}
@@
 
-In the best-case scenario, you might have accurate estimates of the variances $[C]_{ii} = \sigma_i^2$ of the noise contributions affecting your training data values $y_i$, the noise might be Gaussian with zero mean, you might have locations $t_i$ that are extremely accurately known, and you might have justifiable prior variances $[\Lambda]_{jj}$ on your parameters $\beta_j$.
+In the best-case scenario, you might have accurate estimates of the variances $[C]_{ii} = \sigma_i^2$ of the noise contributions affecting your training data values $y_i$, the noise might be Gaussian with zero mean, you might have locations $t_i$ that are extremely accurately known, and you might have justifiable prior variances $[\Lambda^{-1}]_{jj}$ on your parameters $\beta_j$.
 In this case, you can assume that the linear model with $p$ parameters is a good model for your data, and write down a likelihood function and a prior.

### 2021-01-05 paper/main.tex
KSF comments, math fax

@@
 % -----
+% - Address the META over-fitting point that if you do lots of CVs and $n$ is small, you are probably still over-fitting.
+For example, the $p=73$ result is probably an over-fit.
+SV has an example in the literature to be cited.
+Goes in the discussion.
+But maybe also gets hinted in the introduction.
+% - Incorporate Zhao comments and thank Zhao
+% - Incorporate Gentillini comments and thank Gentillini
 % - Note that we made the toy examples on a regular grid in t-space. That isn't required or assumed anywhere in the text; that's just a choice for the toy.
-% - Make sure that what we say about Wiener filtering are correct.
 % - Are we clear that the feature weighting is a kind of regularization?
@@
 % Math operators and definitions
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathtools}
+\usepackage{amsmath, amssymb, mathtools, mathrsfs}
 \newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
-\DeclareMathOperator{\FT}{FT}
+\DeclareMathOperator{\FT}{\mathscr{F}}
 
@@
 Adrian Price-Whelan (Flatiron),
-Bernhard Sch\"olkopf (MPI-IS), and
-Rachel Ward (UT Austin)
+Bernhard Sch\"olkopf (MPI-IS),
+Kate Storey-Fisher (NYU),
+Rachel Ward (UT Austin), and
+Lily Zhao (Yale)
 for valuable conversations and input.
@@
 
-In contexts in which we want to fit a flexible function to data, for interpolation or denoising, we often perform linear fitting in a generic basis, such as polynomials, fourier modes, wavelets, or spherical harmonics.
+In contexts in which we want to fit a flexible function to data, for interpolation or denoising, we often perform linear fitting in a generic basis, such as polynomials, Fourier modes, wavelets, or spherical harmonics.
 This kind of linear fitting arises in astronomy when, for example, we want to calibrate the relationship between wavelength and position on the detector in a spectrograph:
@@
 
-In this \documentname, we treat applications that look like interpolation; there are many other contexts in which regressions have gone to very large numbers of parameters.
+An important assumption or setting for the problems we are addressing in this \documentname\ will be that you care about predicting new data or interpolating the data, but you explicitly \emph{don't care} about the parameters of the fit or the weights of the basis functions \foreign{per se}.
+In this setting there are no important meanings to the components of the model.
+That is---for us---only the data exist.
+The details of the model are just choices that permit high-quality interpolations and predictions.
+
+In what follows, we will look at applications that look like interpolation; there are many other contexts in which regressions have gone to very large numbers of parameters.
 For example, there are contexts in which there are enormous numbers of possible natural features, like for instance when the data are images or videos: Every pixel of every frame of the video---or any linear (or nonlinear) combination of pixels---can become a feature for the regression.
@@
 
-An important assumption or setting in what follows will be that you care about predicting new data or interpolating the data, but you explicitly don't care about the parameters of the fit or the weights of the basis functions \foreign{per se}.
-In this setting there are no important meanings to the components of the model.
-That is---for us---only the data exist.
-The details of the model are just choices that permit high-quality interpolations and predictions.
-
 In some contexts you have strong beliefs about the noise affecting your measurements. In other cases you don't.
@@
 The differences in these beliefs and the differences in your objectives will change what methods you choose and how you use and analyze them.
-We'll try to come back to these important \emph{subjective} aspects of regression as we go.
+We'll try to be useful to you no matter where you're at.
 
-\section{Standard linear fitting: Ordinary least squares with a feature embedding}
+Ordinary least squares is reviewed in \sectionname~\ref{sec:ols}.
+The extensions of weighted least squares and ridge regression are shown in \sectionname~\ref{sec:extensions}.
+The over-para\-meterized case (more parameters than data) is discussed in \sectionname~\ref{sec:overpar}.
+The concept of feature weighting for over-parameterized fits is introduced in \sectionname~\ref{sec:fwols}.
+Cross-validation is explained and used to choose the number of parameters in \sectionname~\ref{sec:dd}, and the double descent phenomenon is shown.
+The Gaussian Process appears as the limit of infinite parameters in \sectionname~\ref{sec:gp}.
+Jackknife resampling is explained and used to estimate uncertainties in \sectionname~\ref{sec:uncertainty}.
+Numerical implementation considerations are discussed in \sectionname~\ref{sec:implementation} and some final remarks are made in \sectionname~\ref{sec:discussion}.
+
+\section{Standard linear fitting: Ordinary least squares with a feature embedding}\label{sec:ols}
 
@@
 Each of these data points has an associated coordinate or location $t_i$.
+In the machine-learning lexicon, these will be our ``training data''.
 This location $t_i$ could be thought of as a time at which the data point was taken, or a position, or it can be a higher dimensional vector or blob of housekeeping data associated with the data point.
@@
 Alternative common choices would be to make the embedding functions $g_j(t)$ polynomials or other kinds of ordered basis functions, such as wavelets or spherical harmonics (the latter if, say, the $t_i$ are positions on the sphere).
-Another choice that isn't common in the natural sciences, but highly studied in machine learning (for example, \cite{rahimi2007random}), is to choose the features randomly from a distribution (rather than on a regular grid in frequency, as we do here).
+Another choice that isn't common in the natural sciences, but highly studied in machine learning (for example, \citealt{rahimi2007random}), is to choose the features randomly from a distribution (rather than on a regular grid in frequency, as we do here).
 That is beyond our scope, but we come back to it in \sectionname~\ref{sec:discussion}.
@@
 \end{equation}
-This optimization objective \eqref{eq:opt1} is convex and the optimization problem has a solution in closed form as long as the number of parameters (and features) $p$ is less than the number of training points $n$ (and the matrix $X^\top X$ is invertible):
+This optimization objective \eqref{eq:opt1} is convex and the optimization problem has a solution in closed form\footnote{
+Note that $\nabla_{\beta} \|Y-X\beta\|^2 = 2X^\top(Y-X\beta)$ so critical points are such that $X^\top Y= X^\top X\beta$.
+Since the objective is convex and unbounded all these critical points are global minima.
+} as long as the number of parameters (and features) $p$ is less than the number of training points $n$ (and the matrix $X^\top X$ is invertible):
 \begin{equation}
@@
 In these contexts, we don't care about the parameter vector $\hat{\beta}$ itself.
-We care only about the predictions at a set of new ``test'' locations $t_\ast$, which will usually be different from the training locations $t_j$
+We care only about the predictions at a set of new ``test'' locations $t_\ast$, which will usually be different from the training locations $t_j$.
 From the new test times $t_\ast$ we create the test feature matrix $X_\ast$ (by the same feature embedding functions $g_j(t)$).
@@
 This form \eqref{eq:OLS} of the prediction of new test data is called ordinary least squares (OLS). It has many good properties, some of which are encoded in the Gauss--Markov theorem.
-In particular, if the noise contributions in the model given in equation \eqref{eq.model} are uncorrelated, has zero mean, and equal variances for $i=1,\ldots, n$ then the Gauss--Markov theorem states that the OLS estimator has the lowest variance within the class of unbiased estimators that are linear in $Y$ (see, for example, \citealt{esl}, Ch 3).
+In particular, if the noise contributions in the model given in equation \eqref{eq.model} are uncorrelated, have zero mean, and equal variances for $i=1,\ldots, n$ then the Gauss--Markov theorem states that the OLS estimator has the lowest variance within the class of unbiased estimators that are linear in $Y$ (see, for example, \citealt{esl}, Ch 3).
 
@@
 Fits are shown for different values of the number of basis functions $p$; there are $n=23$ data points.
+Here (and in all the \figurename s to follow) we are using the Fourier basis functions in \eqref{eq:basis} and shown in \figurename~\ref{fig:basis}.
 The data points $y_i$ were generated using a function that does not reside in the function space spanned by the basis.
@@
 
-\section{Discussion and extensions of OLS}
+\section{Discussion and extensions of OLS}\label{sec:extensions}
 
-The prediction \eqref{eq:OLS} when $p<n$ (the under-parameterized or traditional regime) is \emph{affine invariant} in that $p$-dimensional rotations or rescalings of the rectangular $X$ design matrix do not affect predictions.
+The prediction \eqref{eq:OLS} when $p<n$ (the under-parameterized or traditional regime) is \emph{affine invariant} in that $p$-dimensional rotations or rescalings of the rectangular design matrix $X$ do not affect predictions.
 That is, if $R$ is an invertible $p\times p$ matrix, the prediction using $X'\leftarrow X\,R$ will be identical to the prediction using the original $X$.
@@
 Indeed, if you know weights or inverse variances for your data points, conceptually you can put them into a weight matrix $C^{-1}$ (written this way to emphasize that reweighting is usually inverse-variance weighting) and write
-\begin{equation}
+\begin{equation}\label{eq:wls}
     \hat{Y}_\ast = X_\ast\,(X^\top\,C^{-1}\,X)^{-1}\,X^\top\,C^{-1}\,Y
@@
 where the weight matrix $C^{-1}$ is $n\times n$ (and often diagonal in standard applications).
-This form of least squares is called \emph{weighted least squares} (WLS) because of the data weighting (not to be confused with \emph{feature} weighting, to appear below).
+The weight matrix $C^{-1}$ is sometimes called the information tensor (or information matrix) and its inverse $C$ is often called the covariance matrix or the noise variance tensor.
+
+This form \eqref{eq:wls} of least squares is called \emph{weighted least squares} (WLS) because of the data weighting (not to be confused with \emph{feature} weighting, to appear below).
 It is also called chi-squared fitting because it optimizes the scalar objective commonly called chi-squared:
@@
 It is common to include a regularization that discourages the fit from making use of large amplitudes $\beta_j$.
-There are many options, but the simplest is ridge regression (or Tikhonov regularization or L2 regularization), which looks like
+There are many options, but the simplest is ridge regression (or Tikhonov regularization or L2 regularization), which (in the form that doesn't have data weights) looks like
 \begin{equation}
@@
 This will become important later when we consider feature weights below.
-It is also case that the regularization need not be proportional to the identity matrix; in principle any positive definite matrix $\Lambda$ could be used in place of $\lambda\,I$; this makes sense to consider when you have detailed prior beliefs about all the parameters $\beta_j$ or if those parameters are measured with different units (say).
+It is also the case that the regularization need not be proportional to the identity matrix: In principle any positive definite matrix $\Lambda$ could be used in place of $\lambda\,I$; this makes sense to consider when you have detailed prior beliefs about all the parameters $\beta_j$ or if those parameters are measured with different units (say).
 
@@
 We'll discuss this form \eqref{eq:foo} more below in \sectionname~\ref{sec:fwols},
-but briefly we can say here that it appears in Bayesian inference contexts where the data points $y_i$ are treated as having Gaussian noise associated with them (with known variance tensor $C$) and there is a Gaussian prior on the parameter vector $\beta$ (with known variance $\Lambda^{-1}$).
+but briefly we can say here that it appears in Bayesian inference contexts where the data points $y_i$ are treated as having Gaussian noise associated with them (with known variance tensor or covariance matrix $C$) and there is a Gaussian prior on the parameter vector $\beta$ (with known variance $\Lambda^{-1}$).
 We have discussed that model elsewhere (\citealt{products}).
@@
 
-\section{Over-parameterization}
+\section{Over-parameterization}\label{sec:overpar}
 
@@
 The OLS solution, in this case, is defined (somewhat arbitrarily) to be the minimum-norm parameter vector $\beta$ that interpolates the data:
-\begin{equation}
+\begin{equation}\label{eq:opt2}
     \hat{\beta} = \arg\min_\beta \|\beta\|_2^2 ~~\mbox{subject to}~~ Y = X\,\beta
@@
 When the investigator knows uncertainties on the training data points $y_i$, this expression will change a bit; we return to that in the next \sectionname.
-The under-parameterized and over-parameterized optimizations can be unified into one form by considering the limit of light L2 regularization:
-\begin{equation}
+The under-parameterized and over-parameterized optimization statements \eqref{eq:opt1} and \eqref{eq:opt2} can be unified into one form by considering the limit of light L2 regularization:
+\begin{equation}\label{eq:opt3}
     \hat{\beta} = \lim_{\lambda\rightarrow 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\beta\|_2^2\right]
@@
 \end{equation}
-in the limit, this delivers the min-norm OLS solution.
+in the limit, this delivers the OLS solution in either case.
 
@@
 provided that $X\,X^\top$ is invertible (which will usually be the case).
-Like \eqref{eq:OLS}, this prediction is \emph{also} called ordinary least squares (OLS), or sometimes ``min-norm least-squares'' to emphasize the degeneracy-breaking choice.
+Like \eqref{eq:OLS}, this prediction is \emph{also} called ordinary least squares (OLS), or sometimes ``min-norm least-squares'' to emphasize the point that it is making the minimum-norm choice of $\beta$ among many degenerate solutions.
 Examples of OLS fits in the over-parameterized regime are shown in \figurename~\ref{fig:ols2}.
@@
 That is, rotations and scalings in the feature space \emph{will} affect predictions.
-It behooves us to re-scale the features (the $p$ $n$-vectors of the design matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features (\cite{xie2020weighted}, \cite{bah2016sample}, \cite{rauhut2016interpolation}).
+It behooves us to re-scale the features (the $p$ $n$-vectors of the design matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features (\citealt{xie2020weighted, bah2016sample, rauhut2016interpolation}).
 We can encode these feature weights in a $p\times p$ diagonal weight matrix $\Lambda^{-1}$ and the prediction becomes
@@
 \end{equation}
-which can also be written as
+which---in analogy to the optimizations \eqref{eq:opt2} and \eqref{eq:opt3}---can also be written as
 \begin{equation}
@@
 \end{equation}
-This optimization penalizes more strongly the parameters $\beta_j$ corresponding to features $g_j(t)$ with larger values of $[\Lambda^{1/2}]_{jj}$.
-If you are a physicist and you don't like the mathematical $\|\cdot\|_2^2$ notation---if you prefer to look at quantities that are obvious scalar forms---then recall that $\|\Lambda^{-1/2}\,\beta\|_2^2 = \beta^\top\,\Lambda^{-1}\,\beta$.
-That latter object is a gauge-invariant object so long as $\beta$ and $\Lambda$ are also gauge-invariant objects themselves.
-Yes, data analysis can have this kind of geometric structure!
+This optimization\footnote{If you are a physicist and you don't like the mathematical $\|\cdot\|_2^2$ notation---if you prefer to look at quantities that are obvious scalar forms---then recall that $\|\Lambda^{1/2}\,\beta\|_2^2 = \beta^\top\Lambda\,\beta$.
+That right-hand-side object is a gauge-invariant object so long as $\beta$ and $\Lambda$ are also gauge-invariant objects themselves.
+Yes, data analysis can have this kind of geometric structure!}
+penalizes more strongly the parameters $\beta_j$ corresponding to features $g_j(t)$ with larger values of $[\Lambda^{1/2}]_{jj}$.
 
@@
 These expressions appear in Bayesian-inference contexts (see, for example \citealt{products}) when $\Lambda^{-1}$ is the variance of the prior on the parameter vector $\beta$ and $C$ is the variance of the noise on the data vector $Y$.
-In those contexts, the units of $C$ would be the units of $Y$ squared, and the units of $\Lambda^{-1}$ would be the square of the ratio of the units of $Y$ to the units of $X$ (the square of the units of $\beta$.
+In those contexts, the units of $C$ would be the units of $Y$ squared, and the units of $\Lambda^{-1}$ would be the square of the ratio of the units of $Y$ to the units of $X$ (the square of the units of $\beta$).
 These weighted-feature, weighted-data least-square forms are good because (if the weightings are chosen appropriately) they lead to smooth solutions that are not required to pass precisely through every data point.
@@
 It is extremely general.
-There is an effect known in many kinds of regression called ``double descent'' or ``peaking phenomenon'' in which predictive accuracy becomes very poor when the number of free parameters $p$ comes close to the number of data points $n$ \cite{jain198239, spigler2018jamming, geiger2019jamming}.
-In particular, for linear models, the ``risk''---the out-of-sample prediction error---blows up when the model capacity just reaches overfitting; at $p=n$ \cite{hastie2019surprises}.
+There is an effect known in many kinds of regression called ``double descent'' or ``peaking phenomenon'' in which predictive accuracy becomes very poor when the number of free parameters $p$ comes close to the number of data points $n$ (\citealt{jain198239, spigler2018jamming, geiger2019jamming}).
+For linear models, the ``risk''---the out-of-sample prediction error---blows up when the model capacity just reaches overfitting; at $p=n$ (\citealt{hastie2019surprises}).
 The fundamental reason for this phenomenon is that the ordinary least squares estimates \eqref{eq:OLS} and \eqref{eq:OLS2} require to compute the inverses $(X^\top X)^{-1}$ and $(XX^\top)^{-1}$ respectively, which are very badly conditioned around $p\approx n$.
-This translates on a large variance for the estimator $\hat \beta$ which implies a large risk.
+This translates to a large variance for the estimator $\hat \beta$ which implies a large risk.
 This behavior disappears with many forms of regularization, including Tikhonov regularization (also known as ridge regression, as described in \eqref{eq:ridge}), early stopping \citep{hastie2019surprises}, and dimensionality reduction \citep{huang2020dimensionality}.
@@
 
-By the way, you might have felt uncomfortable with dropping individual points in this problem, since the points are regularly spaced in the location space (the $t$ space) to begin with, and become irregularly spaced when you leave one out.
+By the way, you might have felt uncomfortable with dropping individual points in this problem, since the points are sort-of regularly spaced in the location space (the $t$ space) to begin with, and become more irregularly spaced when you leave one out.
 How much does this matter?
@@
 \end{align}
-Provided that the spacing of the Fourier modes in frequency space is $\Delta\omega\ll 1 / \Delta t_{\max}$ and the maximum frequency $\floor{p / 2}\,\Delta\omega \gg 1 / \min(s, \Delta t_{\min})$, where
+Provided that the spacing of the Fourier modes in frequency space is $\Delta\omega\ll 1 / \Delta t_{\max}$ and the maximum frequency is $\floor{p / 2}\,\Delta\omega \gg 1 / \min(s, \Delta t_{\min})$, where
 \begin{align}
@@
 \end{align}
-it will be true that the OLS with feature weights $f(\omega)$ will be very similar to the mean of a GP with kernel $k(\Delta t) = \FT[f^2]$.
+it will be true that the OLS with feature weights $f(\omega)$ will be essentially identical to the mean of a GP with kernel $k(\Delta t) = \FT[f^2]$.
 The comparison of the OLS and GP is shown in \figurename~\ref{fig:gp}.
@@
 Not all $p\rightarrow\infty$ kernels will be stationary.
-The limit $p\rightarrow\infty$ of $X\,\Lambda^{-1}\,X^\top$ in \eqref{eq.limit} leads to a stationary kernel $k(\cdot,\cdot)$ because the feature embedding in $X$ is a set of sines and cosines.
+The limit $p\rightarrow\infty$ of $X\,\Lambda^{-1}\,X^\top$ in \eqref{eq.limit} leads to a stationary kernel $k(\cdot,\cdot)$ in this case because the feature embedding in $X$ is a set of sines and cosines.
 Sines and cosines form a basis for translation-invariant function spaces.
@@
 This form \eqref{eq:gpC} is used a lot in astronomy and cosmology (for example, \citealt{zaroubi, aigrain, celerite}) and it is also the standard form given for the Wiener filter, where the kernel function generating $K$ is the Fourier transform of the ``signal power'' and the kernel function generating $C$ is the Fourier transform of the ``noise power''.
-In this form, the amplitude or prefactor or magnitude of the kernel function matters, because it is competing, in some sense, the variance $K$ of the GP against the variance $C$ of the noise.
+In this form, the amplitude of the kernel function matters, because it is competing, in some sense, the variance $K$ of the GP against the variance $C$ of the noise.
 It is not sufficient to get the shape of the kernel function right to make a stable prediction of the mean, when using this form \eqref{eq:gpC}.
@@
 In this case, you can assume that the linear model with $p$ parameters is a good model for your data, and write down a likelihood function and a prior.
-In this best-case scenario, you can turn the Bayesian crank and deliver a posterior density for the predicted values $Y_\ast$ at the test locations $t_\ast$.
-The second derivative of the ln of the posterior density can then be processed into a standard error on the predictions $\hat{Y}_\ast$ (or you can deliver full posterior densities somehow).
+In this case, you can turn the Bayesian crank and deliver a posterior density for the predicted values $Y_\ast$ at the test locations $t_\ast$.
+The second derivative of the natural logarithm of the posterior density can then be processed into a standard error on the predictions $\hat{Y}_\ast$ (or you can deliver full posterior densities somehow).
 The details of this are way beyond the scope of this \documentname, but this (or a closely related) problem is discussed in some detail by us elsewhere (\citealt{products}).
@@
 The square-root of the trace of this uncertainty variance $\hat{\Sigma}$ (that is, what you might call the jackknife estimate of the standard error) is shown in \figurename~\ref{fig:uncertainty}.
-Note the similarity between jackknife and cross-validation; that's relevant and important; these empirical estimates of uncertainty and prediction error are closely related.
+Note the similarity between jackknife and cross-validation; it is relevant and important: These empirical estimates of uncertainty and prediction error are closely related.
 \begin{figure}[t]
@@
 \end{figure}
+
+One comment about the jackknife variance expression \eqref{eq:jackknife}: The prefactor before the sum is $(n-1)/n$, not the usually expected $1/(n-1)$.
+This difference comes from the fact that the $n$ jackknife trials are not uncorrelated: They share data.
+The variance of the uncertainty is therefore larger than the variance across jackknife trials by a factor of order $n$ (the factor is $(n-1)^2/n$ to be precise).
 
@@
 A full translation is beyond our scope, though.
-And our view is that the value of being explicit about the basis and the regularization makes the linear fitting approach better in general.
+And our view is that the value of making explicit investigator choices about basis and the regularization makes the linear fitting approach better in general.
 
@@
 This was a choice for simplicity of visualization; nothing is fundamental about the locations being one-dimensional.
-The only considerations about dimensionality is that the functions $g_j(t)$ have to act correctly on the locations $t_i$ whatever their size or shape.
+The only considerations about dimensionality (SOLEDAD: KSF ASKS: WHAT ABOUT WHEN THE DIMENSIONALITY of $t$ exceeds $n$ or $p$?) is that the functions $g_j(t)$ have to act correctly on the locations $t_i$ whatever their size or shape.
 In astronomy and cosmology contexts, it is common for the locations $t_i$ to be positions on the sphere, and it is common for the natural basis functions to be spherical harmonics, for example.
@@
 A model that generates both can be used to make predictions $y_\ast$ at new locations $t_\ast$ by executing an inference or inverse problem on the generative model.
-Generative models are generally non-convex---and harder to execute---if you want the relationship between the $t_i$ and the $y_i$ to be nonlinear.
-You don't get closed-form solutions, and there aren't known guarantees (like the Gauss--Markov theorem) about performance.
+Generative models are generally non-convex---and harder to execute---if you want the relationship between the $t_i$ and the $y_i$ to be nonlinear (for an example of this in astronomy, see, for example, \citealt{thecannon}).
+In these cases you don't get closed-form solutions, and there aren't known guarantees (like the Gauss--Markov theorem) about performance.
 But they are more general, and often more appropriate, especially when both the locations $t_i$ and the data $y_i$ are comparably noisy measurements.
@@
 
+To prove that \eqref{} and \eqref{} are equivalent we use a classical result in quadratic optimization (see for instance Chapter 16 of \cite{nocedal2006numerical}).
+
+Consider the quadratic optimization problem 
+\begin{equation} \label{qp}
+    \min_x \frac{1}{2} x^TG x + x^\top c \quad \text{ subject to } Ax=b.
+\end{equation}
+Assume that $A$ has full row rank and let $Z$ be such that its columns form a basis for the null space of $A$ (i.e.
+$AZ=0$).
+If $Z^\top G Z$ is positive definite then the solution of \eqref{qp} is given by the Karush-Kuhn-Tucker conditions, namely
+\begin{equation}
+    \left[
+    \begin{matrix}
+
+    \end{matrix}\right]
+\end{equation}
+
 \textsl{t. b. d.}\begin{comment}

### 2021-01-11 paper/main.tex

@@
 But maybe also gets hinted in the introduction.
-% - Incorporate Zhao comments and thank Zhao
-% - Incorporate Gentillini comments and thank Gentillini
-% - Note that we made the toy examples on a regular grid in t-space. That isn't required or assumed anywhere in the text; that's just a choice for the toy.
+% - Incorporate remaining Zhao comments
 % - Are we clear that the feature weighting is a kind of regularization?
@@
 % - In uncertainties, we talk about Bayesian. Should we also talk about frequentist and/or information theory?
-% - Audit for the use of "points" and "locations" and "data" to make sure all is consistent. The ts are locations, the ys are data.
-% - Audit for use of the words "fit" and "prediction" and "model". All okay?
 % - Audit for use of \, as the multiply operator? Fix the kerning around the ^\top items?
-% - Audit for design matrix, feature matrix, and so on. We should mention design matrix but stick with feature matrix as our terminology.
-% - Audit for hyphens in under-parameterization and re-weighting and so on? Hyphenated words or single words? Make decisions and stick to them.
 % - HOGG: List clearly the assumptions underlying CVMSE and jackknife. They make assumptions about independence of the data points and also something maybe about per-point information content.
+% - SOLEDAD: address constraints may not be satisfiable
 
@@
 Dan Foreman-Mackey (Flatiron),
+Alessandro Gentilini,
 Teresa Huang (JHU),
@@
 \textsl{\footnotesize Flatiron Institute, a division of the Simons Foundation \\
-Center for Cosmology and Particle Physics, Deptartment of Physics, New York University \\
+Center for Cosmology and Particle Physics, Department of Physics, New York University \\
 Center for Data Science, New York University \\
@@
 
-\paragraph{Abstract:} There are many uses for linear fitting; the context we consider here is interpolation and denoising of data, as (for example) when you have calibration data and you want to fit a smooth, flexible function to those data.
+\paragraph{Abstract:} There are many uses for linear fitting; the context here is interpolation and denoising of data, as when you have calibration data and you want to fit a smooth, flexible function to those data.
 Or you want to fit a flexible function to de-trend a time series or normalize a spectrum.
@@
 Here we discuss how this basis-function fitting is done, with ordinary least squares and extensions thereof.
-We emphasize that it is often valuable to choose \emph{far more parameters than data points}, despite folk rules to the contrary.
-It is even possible to take the limit of infinite parameters, at which, if the basis and regularization are chosen correctly, the least-squares fit becomes the mean of a Gaussian process (or, equivalently, a Wiener filter or kriging).
-Although there are often good fits with small numbers of parameters and also with very large numbers of parameters, the dangerous regime for linear fitting is when the number of parameters is comparable to the number of data points (the double-descent or peaking-phenomenon regime); we discuss this problem and how to avoid it.
-We also comment on model selection, uncertainty estimation, and computational implementation.
+We emphasize that it is often valuable to choose \emph{far more parameters than data points}, despite folk rules to the contrary:
+Suitably regularized models with enormous numbers of parameters generalize well and make good predictions for held-out data; over-fitting is not (mainly) a problem of having too many parameters.
+It is even possible to take the limit of infinite parameters, at which, if the basis and regularization are chosen correctly, the least-squares fit becomes the mean of a Gaussian process.
+We recommend cross-validation as a good empirical method for model selection (for example, setting the number of parameters and the detailed form of the regularization),
+and jackknife resampling as a good empirical method for estimating the uncertainties of the predictions made by the model.
+We also give advice for building stable computational implementations.
 
@@
 This kind of linear fitting arises in astronomy when, for example, we want to calibrate the relationship between wavelength and position on the detector in a spectrograph:
-We have noisy measurements of calibration data and we want to fit a smooth function of position that de-noises and interpolates the calibration data.
-It also arises when we want to make a data-driven interpolation, extrapolation, or local averaging of data, as with light-curve detrending, continuum estimation, and interpolation or extrapolation of instrument housekeeping (or other) data.
+We have noisy measurements of calibration data and we want to fit a smooth function of position that denoises and interpolates the calibration data.
+It also arises when we want to make a data-driven interpolation, extrapolation, or local averaging of data, as with light-curve de-trending, continuum estimation, and interpolation or extrapolation of instrument housekeeping (or other) data.
 
@@
 This optimization objective \eqref{eq:opt1} is convex and the optimization problem has a solution in closed form\footnote{
-Note that $\nabla_{\beta} \|Y-X\beta\|^2 = 2X^\top(Y-X\beta)$ so critical points are such that $X^\top Y= X^\top X\beta$.
-Since the objective is convex and unbounded all these critical points are global minima.
+Note that $\nabla_{\beta} \|Y-X\beta\|^2 = 2X^\top(Y-X\beta)$ so critical points are such that $X^\top Y= X^\top X\beta$. Since the objective is convex all these critical points are global minima. 
 } as long as the number of parameters (and features) $p$ is less than the number of training points $n$ (and the matrix $X^\top X$ is invertible):
@@
 We will treat the case in which the matrix is not invertible below.
-When the investigator knows uncertainties on the training data points $y_i$, this expression will change a bit; we begin to discuss that in the next \sectionname.
+When the investigator knows uncertainties on the training data $y_i$, this expression will change a bit; we begin to discuss that in the next \sectionname.
 
@@
 Here (and in all the \figurename s to follow) we are using the Fourier basis functions in \eqref{eq:basis} and shown in \figurename~\ref{fig:basis}.
-The data points $y_i$ were generated using a function that does not reside in the function space spanned by the basis.
-Here the $X_\ast$ matrices used in the predictions $\hat{Y}_\ast$ were generated from a fine grid of points in the location coordinate $t$; the plots of the fine grid of predictions are the continuous lines.
+The data $y_i$ were generated using a function that does not reside in the function space spanned by the basis.
+Here the $X_\ast$ matrices used in the predictions $\hat{Y}_\ast$ were generated from a fine grid of locations in the location coordinate $t$; the plots of the fine grid of predictions are the continuous lines.
 The fits with larger $p$ have more flexibility to fit the data than the fit with $p=3$, but the fit at the highest $p$ shows evidence of over-fitting.}
@@
 
-The prediction \eqref{eq:OLS} when $p<n$ (the under-parameterized or traditional regime) is \emph{affine invariant} in that $p$-dimensional rotations or rescalings of the rectangular design matrix $X$ do not affect predictions.
+The prediction \eqref{eq:OLS} when $p<n$ (the under-parameterized or traditional regime) is \emph{affine invariant} in that $p$-dimensional rotations or rescalings of the rectangular feature matrix $X$ do not affect predictions.
 That is, if $R$ is an invertible $p\times p$ matrix, the prediction using $X'\leftarrow X\,R$ will be identical to the prediction using the original $X$.
@@
 Although the OLS prediction \eqref{eq:OLS} is affine invariant with respect to $p$-dimensional transformations, it is \emph{not} affine invariant with respect to $n$-dimensional transformations, such as a re-weighting of the input data.
-Indeed, if you know weights or inverse variances for your data points, conceptually you can put them into a weight matrix $C^{-1}$ (written this way to emphasize that reweighting is usually inverse-variance weighting) and write
+Indeed, if you know weights or inverse variances for your data points $y_i$, conceptually you can put them into a weight matrix $C^{-1}$ (written this way to emphasize that reweighting is usually inverse-variance weighting) and write
 \begin{equation}\label{eq:wls}
@@
 We will say more about noisy data and the propagation of uncertainties below in \sectionname~\ref{sec:uncertainty}.
-It might be crossing your mind that there are uncertainties not just in the data points $y_i$, but also often in the \emph{locations} $t_i$ of the data points as well.
+It might be crossing your mind that there are uncertainties not just in the data points $y_i$, but also often in the \emph{locations} $t_i$ of the data as well.
 It turns out that taking the latter into account is a much harder problem; we return to this also in \sectionname~\ref{sec:uncertainty}.
@@
 There are many options, but the simplest is ridge regression (or Tikhonov regularization or L2 regularization), which (in the form that doesn't have data weights) looks like
-\begin{equation}
+\begin{equation} \label{eq:ridge}
     \hat{\beta} = \arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\beta\|_2^2
@@
 The ridge-regularized prediction for new data looks like
-\begin{equation} \label{eq:ridge}
+\begin{equation} \label{eq:ridge_sol}
     \hat{Y}_\ast = X_\ast\,(X^\top\,X + \lambda\,I)^{-1}\,X^\top\,Y
@@
 Examples of OLS fits in the over-parameterized regime are shown in \figurename~\ref{fig:ols2}.
-Note that the fits with different numbers of parameters $p$ lead to very different predictions, but they all go through the data points exactly.
+Note that the fits with different numbers of parameters $p$ lead to very different predictions, but they all go through the data exactly.
 \begin{figure}[t]
@@
 That is, rotations and scalings in the feature space \emph{will} affect predictions.
-It behooves us to re-scale the features (the $p$ $n$-vectors of the design matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features (\citealt{xie2020weighted, bah2016sample, rauhut2016interpolation}).
+It behooves us to re-scale the features (the $p$ $n$-vectors of the feature matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features (\citealt{xie2020weighted, bah2016sample, rauhut2016interpolation}).
 We can encode these feature weights in a $p\times p$ diagonal weight matrix $\Lambda^{-1}$ and the prediction becomes
-\begin{equation}
+\begin{equation} \label{eq:weighted_sol}
     \hat{Y}_\ast = X_\ast\,\Lambda^{-1}\,X^\top\,(X\,\Lambda^{-1}\,X^\top)^{-1}\,Y
@@
 This can be seen as the prediction for new data resulting from the following optimization:
-\begin{equation}
+\begin{equation} \label{eq:weighted}
     \hat{\beta} = \arg\min_\beta \|\Lambda^{1/2}\,\beta\|_2^2 ~~\mbox{subject to}~~ Y = X\,\beta
@@
     \caption{Comparison of ordinary least squares (OLS) to OLS with a specific feature weighting.
-The feature-weighting function is given in the text in equations~\eqref{eq:f} and \eqref{eq:lambdainv}.
+The feature-weighting function is given in the text in equations~\eqref{eq:f} and \eqref{eq:lambdainv}; in this and the following \figurename s, we (somewhat arbitrarily) set the width parameter to be $s=0.05$.
 When the high-frequency features are weighted down, the min-norm solution gives them small amplitudes, making the fit smoother.}
@@
 Then this process is iterated over all choices of what part (or point) to leave out.
-This process is illustrated in \figurename~\ref{fig:loo}, where we show $23$ fits, each of which is trained to the 22 points left when we leave one of the $n=23$ points out.
+This process is illustrated in \figurename~\ref{fig:loo}, where we show $23$ fits, each of which is trained to the 22 points remaining when we leave one of the $n=23$ points out.
 Also shown is the prediction, in each leave-one-out fit, for the left-out point.
@@
     \caption{Leave-one-out cross-validation estimates of mean squared prediction error for the feature-weighted OLS fits, as a function of the number of features $p$.
-Also shown are the same for ridge regression with $\lambda=0.1$ and also the Gaussian process introduced in \sectionname~\ref{sec:gp} and shown in \figurename~\ref{fig:gp}.
-The GP result is shown as a flat line because it doesn't have an associated number $p$.
+Also shown are the same for ridge regression with $\lambda=0.1$ and also the Gaussian process that we will introduce in \sectionname~\ref{sec:gp} and show in \figurename~\ref{fig:gp}; the GP result is shown as a flat line because it doesn't have an associated number $p$.
 In detail the first (lowest-$t$) and last (highest-$t$) data points were not used in computing the mean squared error; that choice is debatable, but we are imagining an assessment of the quality of the \emph{interpolations}, not extrapolations, of these models.
@@
 It is extremely general.
-There is an effect known in many kinds of regression called ``double descent'' or ``peaking phenomenon'' in which predictive accuracy becomes very poor when the number of free parameters $p$ comes close to the number of data points $n$ (\citealt{jain198239, spigler2018jamming, geiger2019jamming}).
-For linear models, the ``risk''---the out-of-sample prediction error---blows up when the model capacity just reaches overfitting; at $p=n$ (\citealt{hastie2019surprises}).
-The fundamental reason for this phenomenon is that the ordinary least squares estimates \eqref{eq:OLS} and \eqref{eq:OLS2} require to compute the inverses $(X^\top X)^{-1}$ and $(XX^\top)^{-1}$ respectively, which are very badly conditioned around $p\approx n$.
+There is an effect known in many kinds of regression called ``double descent'' or ``peaking phenomenon'' or ``jamming'' in which predictive accuracy becomes very poor when the number of free parameters $p$ comes close to the number of data points $n$ (\citealt{jain198239, spigler2018jamming, geiger2019jamming}).
+For linear models, the ``risk''---the out-of-sample prediction error---blows up when the model capacity just becomes excessive; at $p=n$ (\citealt{hastie2019surprises}).
+The fundamental reason for this phenomenon is that the ordinary least squares estimates \eqref{eq:OLS} and \eqref{eq:OLS2} require to compute the inveses $(X^\top X)^{-1}$ and $(X\,X^\top)^{-1}$ respectively, which are very badly conditioned around $p\approx n$.
 This translates to a large variance for the estimator $\hat \beta$ which implies a large risk.
-This behavior disappears with many forms of regularization, including Tikhonov regularization (also known as ridge regression, as described in \eqref{eq:ridge}), early stopping \citep{hastie2019surprises}, and dimensionality reduction \citep{huang2020dimensionality}.
+One way to think about this is that when the condition number of the matrix $X^\top X$ or $X\,X^\top$ is large, some directions in the data space---some linear combinations of the elements of the data vector $Y$---are very strongly amplified.\footnote{The condition number comes back up below in \sectionname~\ref{sec:implementation}.
+It turns out that when the condition number is large, not only do the output predictions become very sensitive to the input training data, but also the numerical (computational) stability of the linear algebra can also be badly affected.
+But we emphasize here that the risk goes bad when the condition number is large \emph{even if} it is possible to perform the linear algebra correctly at high precision.}
+This makes the regression unreasonably sensitive to noise in the data.
+The high-risk behavior at $p\approx n$ disappears with certain kinds of regularization.
+These include the ridge regularization shown in \figurename~\ref{fig:cv} (also known as Tikhonov regression), but also early stopping \citep{hastie2019surprises}, and dimensionality reduction \citep{huang2020dimensionality}.
 
-The CVMSE gets better and worse at different values of $p$;
-and it even gets really \emph{good} at particular values of $p$.
-That's not surprising; there are places where the fit basis is just appropriate for your specific problem.
+Since it is an overloaded concept, we pause here to make a few comments about ``over-fitting''.... HOGG
+
+The CVMSE gets better and worse at different values of $p$.
+That's not surprising; there are places where the fit basis and size and feature weighting are all more appropriate for your specific problem.
 These good-CVMSE places are the best places to work, if you can afford to search for them and find them.
@@
 The minimum-CVMSE choices for $p$ and the hyper-parameters will generally be very close to the choices that lead to the best predictions for new data.
+
+HOGG: INSERT POINT ABOUT OVER-CHOOSING YOUR HYPER-PARAMETERS: Over-fitting to the validation operator.
 
@@
 There are four-ish sources of uncertainty in the predictions you are making in problems like these:
-(1)~The data points you have $y_i$ are individually noisy.
+(1)~The data points $y_i$ you have are individually noisy.
 (2)~There are finitely many of those data points (there are $n$ of them) and there are gaps between them in the location space $t$.
@@
 In the toy examples used throughout this \documentname, we considered data with locations $t_i$ in a one-dimensional location space or ambient space.
-This was a choice for simplicity of visualization; nothing is fundamental about the locations being one-dimensional.
-The only considerations about dimensionality (SOLEDAD: KSF ASKS: WHAT ABOUT WHEN THE DIMENSIONALITY of $t$ exceeds $n$ or $p$?) is that the functions $g_j(t)$ have to act correctly on the locations $t_i$ whatever their size or shape.
+This was a choice for simplicity of visualization; in principle the locations $t_i$ could be higher dimensional, or live in a different kind of space.
+The most important consideration about the dimensionality and range of the locations is that the functions $g_j(t)$ have to sensibly take the locations $t_i$ as input.
 In astronomy and cosmology contexts, it is common for the locations $t_i$ to be positions on the sphere, and it is common for the natural basis functions to be spherical harmonics, for example.
@@
 {\raggedright
+\setlength{\bibsep}{0pt plus 0.3ex} % trust in Hogg
 \bibliographystyle{authordate1}
@@
 
-To prove that \eqref{} and \eqref{} are equivalent we use a classical result in quadratic optimization (see for instance Chapter 16 of \cite{nocedal2006numerical}).
+As mentioned in the main text, the optimal solutions of the unconstrained objectives \eqref{eq:opt1} and \eqref{eq:ridge} can be obtained by computing the first-order critical points.
+The first-order critical points are global minima because all the objectives considered are convex in the regression coefficients $\beta$.
+
+To derive the optimal solutions of the constrained optimization we use a classical result in quadratic optimization (see for instance Chapter 16 of \cite{nocedal2006numerical}).
 
@@
 \begin{equation} \label{qp}
-    \min_x \frac{1}{2} x^TG x + x^\top c \quad \text{ subject to } Ax=b.
+    \arg\min_x \frac{1}{2} x^T G x + x^\top c \quad \text{ subject to } Ax=b.
 \end{equation}
-Assume that $A$ has full row rank and let $Z$ be such that its columns form a basis for the null space of $A$ (i.e.
+
+The first-order necessary conditions for $x^*$ to be a solution of \eqref{qp} is that there is a vector $\lambda^*$ (known as Lagrange multipliers) such that the following system of equations is satisfied:
+
+%Assume that $A$ has full row rank and let $Z$ be such that its columns form a basis for the null space of $A$ (i.e.
 $AZ=0$).
@@
     \begin{matrix}
+    G & A^\top \\ 
+    A & 0
+    \end{matrix}\right]
+    \left[
+    \begin{matrix}
+    x^* \\ 
+    \lambda^*
+    \end{matrix}\right] = 
+    \left[
+    \begin{matrix}
+    -c \\ 
+    b
+    \end{matrix}\right].
+    \label{kkt}
+\end{equation}
+Equation \eqref{kkt} is typically known as the Karush-Kuhn-Tucker conditions (KKT).
+If the objective function in \eqref{qp} is convex, the KKT conditions are also sufficient for optimality\footnote{The KKT conditions can also characterize optimality in more general cases.
+For instance, if $A$ has full row rank and $Z$ is the nullspace of $A$, if $Z^\top G Z$ is positive semidefinite the KKT conditions are sufficient for optimality.
+If $Z^\top G Z$ is positive definite we also have that the solution of \eqref{qp} is unique (which is typically the case in the underparameterized linear regression but not in the overparameterized).}.
 
-    \end{matrix}\right]
-\end{equation}
+Using this formulation it is easy to check that the solution of \eqref{eq:opt2} leads to predictions in \eqref{eq:ridge_sol}, and the solution of \eqref{eq:weighted} produce \eqref{eq:weighted_sol}.
 
-\textsl{t. b. d.}\begin{comment}
+\begin{comment}
 SOLEDAD: Maybe how you get from the optimization statements to the closed-form solutions, for the under- and over-parameterized cases?

### 2021-01-12 paper/main.tex
Zhao comments, math, typesetting

@@
 % -----
-% - Address the META over-fitting point that if you do lots of CVs and $n$ is small, you are probably still over-fitting.
-For example, the $p=73$ result is probably an over-fit.
-SV has an example in the literature to be cited.
-Goes in the discussion.
-But maybe also gets hinted in the introduction.
-% - Incorporate remaining Zhao comments
-% - Are we clear that the feature weighting is a kind of regularization?
-I (DWH) think it IS because it affects how the L2 on beta affects different parameters.
-SV says that maybe we should get explicit about the regularization points, and when the regularization is implicit or hidden.
-% - In uncertainties, we talk about Bayesian. Should we also talk about frequentist and/or information theory?
-% - Audit for use of \, as the multiply operator? Fix the kerning around the ^\top items?
+% - To be submitted to EPJ Data Science https://epjdatascience.springeropen.com/about
+% - Audit for use of \, as the multiply operator?
 % - HOGG: List clearly the assumptions underlying CVMSE and jackknife. They make assumptions about independence of the data points and also something maybe about per-point information content.
-% - SOLEDAD: address constraints may not be satisfiable
+% - SOLEDAD: address the point that some constraints may not be satisfiable
+% - Soledad: Once appendix is done, point down to it from the text at relevant places.
 
@@
 We'll try to be useful to you no matter where you're at.
+This document does not deliver new research results on the mathematics or statistics of regression.
+It is novel only in that it makes very specific the connection between regularized linear regression and Gaussian processes.
 
@@
 \begin{equation}
-    \|q\|_2^2 \equiv q^\top\,q
+    \|q\|_2^2 \equiv q^\top q
     ~.
@@
 \begin{equation}
-    \hat{\beta} = (X^\top\,X)^{-1}\,X^\top\,Y
+    \hat{\beta} = (X^\top X)^{-1}\,X^\top Y
     ~.
@@
 \begin{equation}\label{eq:OLS}
-    \hat{Y}_\ast = X_\ast\,(X^\top\,X)^{-1}\,X^\top\,Y
+    \hat{Y}_\ast = X_\ast\,(X^\top X)^{-1}\,X^\top Y
     ~.
 \end{equation}
-Examples of OLS applied to some toy data are shown in \figurename~\ref{fig:ols1}.
+Examples of OLS applied to some toy data\footnote{The algorithm by which the toy data were made---and indeed all of the code executed to make the figures for this \documentname---is available online at \url{https://github.com/davidwhogg/FlexibleLinearModels}.} are shown in \figurename~\ref{fig:ols1}.
 This form \eqref{eq:OLS} of the prediction of new test data is called ordinary least squares (OLS). It has many good properties, some of which are encoded in the Gauss--Markov theorem.
 In particular, if the noise contributions in the model given in equation \eqref{eq.model} are uncorrelated, have zero mean, and equal variances for $i=1,\ldots, n$ then the Gauss--Markov theorem states that the OLS estimator has the lowest variance within the class of unbiased estimators that are linear in $Y$ (see, for example, \citealt{esl}, Ch 3).
-
 \begin{figure}[t]
@@
 Although the OLS prediction \eqref{eq:OLS} is affine invariant with respect to $p$-dimensional transformations, it is \emph{not} affine invariant with respect to $n$-dimensional transformations, such as a re-weighting of the input data.
-Indeed, if you know weights or inverse variances for your data points $y_i$, conceptually you can put them into a weight matrix $C^{-1}$ (written this way to emphasize that reweighting is usually inverse-variance weighting) and write
+Indeed, if you know weights or inverse variances for your data points, conceptually you can put them into a weight matrix $C^{-1}$ (written this way to emphasize that reweighting is usually inverse-variance weighting) and write
 \begin{equation}\label{eq:wls}
-    \hat{Y}_\ast = X_\ast\,(X^\top\,C^{-1}\,X)^{-1}\,X^\top\,C^{-1}\,Y
+    \hat{Y}_\ast = X_\ast\,(X^\top C^{-1}\,X)^{-1}\,X^\top C^{-1}\,Y
     ~,
@@
 \begin{equation}
-    \chi^2 = (Y - X\,\beta)^\top\,C^{-1}\,(Y - X\,\beta)
+    \chi^2 = (Y - X\,\beta)^\top C^{-1}\,(Y - X\,\beta)
     ~.
@@
 \begin{equation} \label{eq:ridge_sol}
-    \hat{Y}_\ast = X_\ast\,(X^\top\,X + \lambda\,I)^{-1}\,X^\top\,Y
+    \hat{Y}_\ast = X_\ast\,(X^\top X + \lambda\,I)^{-1}\,X^\top Y
     ~,
@@
 \begin{equation}\label{eq:foo}
-    \hat{Y}_\ast = X_\ast\,(X^\top\,C^{-1}\,X + \Lambda)^{-1}\,X^\top\,C^{-1}\,Y
+    \hat{Y}_\ast = X_\ast\,(X^\top C^{-1}\,X + \Lambda)^{-1}\,X^\top C^{-1}\,Y
     ~.
@@
 but briefly we can say here that it appears in Bayesian inference contexts where the data points $y_i$ are treated as having Gaussian noise associated with them (with known variance tensor or covariance matrix $C$) and there is a Gaussian prior on the parameter vector $\beta$ (with known variance $\Lambda^{-1}$).
-We have discussed that model elsewhere (\citealt{products}).
+We have discussed that model elsewhere (\citealt{products}).\footnote{In our previous discussion of this product of Gaussians, the notation differs.
+What's called $\Lambda^{-1}$ here is called $\Lambda$ in \citet{products}.}
 It is also useful sometimes to think of the ``units'' or dimensions of the quantities in \eqref{eq:foo}: In the Bayesian setting, the units of $C$ would be the square of the units of $Y$ and the units of $\Lambda^{-1}$ would be the square of the units of the ratio $Y/X$ (the square of the units of $\beta$).
@@
 \begin{equation}\label{eq:OLS2}
-    \hat{Y}_\ast = X_\ast\,X^\top\,(X\,X^\top)^{-1}\,Y
+    \hat{Y}_\ast = X_\ast\,X^\top (X\,X^\top)^{-1}\,Y
     ~,
@@
 The pseudo-inverse of a diagonal matrix is defined as the diagonal matrix made by inverting the non-zero diagonal entries.
-And for any non-diagonal (or any non-square) matrix $X$ the pseudo-inverse is defined by taking the singular-value decomposition (SVD) of $X$, $X=U\,S\,V$, with $S$ diagonal and $U,V$ orthogonal, then $X^\dagger \equiv V^\top\,S^\dagger\,U^\top$.
+And for any non-diagonal (or any non-square) matrix $X$ the pseudo-inverse is defined by taking the singular-value decomposition (SVD) of $X$, $X=U\,S\,V$, with $S$ diagonal and $U,V$ orthogonal, then $X^\dagger \equiv V^\top S^\dagger\,U^\top$.
 
-This pseudo-inverse form \eqref{eq:OLS3} of OLS is extremely general: It works for both the $p\le n$ and $p>n$ cases, and it works when the $X\,X^\top$ or $X^\top\,X$ matrices are not invertible.
+This pseudo-inverse form \eqref{eq:OLS3} of OLS is extremely general: It works for both the $p\le n$ and $p>n$ cases, and it works when the $X\,X^\top$ or $X^\top X$ matrices are not invertible.
 There can be significant numerical issues with implementing the pseudo-inverse; we comment on those in \sectionname~\ref{sec:implementation}.
@@
 \begin{equation} \label{eq:weighted_sol}
-    \hat{Y}_\ast = X_\ast\,\Lambda^{-1}\,X^\top\,(X\,\Lambda^{-1}\,X^\top)^{-1}\,Y
+    \hat{Y}_\ast = X_\ast\,\Lambda^{-1}\,X^\top (X\,\Lambda^{-1}\,X^\top)^{-1}\,Y
 \end{equation}
-This can be seen as the prediction for new data resulting from the following optimization:
+This can be seen as the prediction for new data resulting from the following optimization (again, assuming the data can be interpolated):
 \begin{equation} \label{eq:weighted}
@@
 \begin{equation}
-    \hat{\beta} = \lim_{\lambda\rightarrow 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\Lambda^{1/2}\beta\|_2^2\right]
+    \hat{\beta} = \lim_{\lambda\rightarrow 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\Lambda^{1/2}\,\beta\|_2^2\right]
     ~.
@@
 \begin{align}\label{eq:LambdaC1}
-    \hat{Y} &= X_\ast\,(X^\top\,C^{-1}\,X + \Lambda)^{-1}\,X^\top\,C^{-1}\,Y
+    \hat{Y} &= X_\ast\,(X^\top C^{-1}\,X + \Lambda)^{-1}\,X^\top C^{-1}\,Y
     \\ \label{eq:LambdaC2}
-    \hat{Y} &= X_\ast\,\Lambda^{-1}\,X^\top\,(X\,\Lambda^{-1}\,X^\top + C)^{-1}\,Y
+    \hat{Y} &= X_\ast\,\Lambda^{-1}\,X^\top (X\,\Lambda^{-1}\,X^\top + C)^{-1}\,Y
     ~.
@@
 We discuss the equivalence of these below in \appendixname~\ref{app:math}.
-These expressions appear in Bayesian-inference contexts (see, for example \citealt{products}) when $\Lambda^{-1}$ is the variance of the prior on the parameter vector $\beta$ and $C$ is the variance of the noise on the data vector $Y$.
-In those contexts, the units of $C$ would be the units of $Y$ squared, and the units of $\Lambda^{-1}$ would be the square of the ratio of the units of $Y$ to the units of $X$ (the square of the units of $\beta$).
-These weighted-feature, weighted-data least-square forms are good because (if the weightings are chosen appropriately) they lead to smooth solutions that are not required to pass precisely through every data point.
+These expressions appear in Bayesian-inference contexts (see, for example, \citealt{products}) when $\Lambda^{-1}$ is the variance of the prior on the parameter vector $\beta$ and $C$ is the variance of the noise on the data vector $Y$.
+They are solutions to the optimization
+\begin{equation}
+    \hat{\beta} = \arg\min_\beta \|C^{-1/2}\,(Y - X\,\beta)\|_2^2 + \|\Lambda^{1/2}\,\beta\|_2^2
+    ~.
+\end{equation}
+The units of $C$ must be the units of $Y$ squared, and the units of $\Lambda^{-1}$ must be the square of the ratio of the units of $Y$ to the units of $X$ (the square of the units of $\beta$).
+These weighted-feature, weighted-data least-square forms \eqref{eq:LambdaC1} and \eqref{eq:LambdaC2} are good because (if the weightings are chosen appropriately) they lead to smooth solutions that are not required to pass precisely through every data point.
 This is appropriate in common, real situations in which data are noisy and the world is smooth.
@@
 
-Since it is an overloaded concept, we pause here to make a few comments about ``over-fitting''.... HOGG
+Sometimes the word ``over-fitting'' is used to describe models that are too flexible.
+In our view, a model is properly called ``over-fit'' when the prediction of the regression on held-out data---what the statisticians call ``risk''---is bad.
+So over-fitting happens not universally when the number of parameters is large, but instead when the number of parameters is comparable to the number of data points, and (also) the regularization is inappropriate.
+\figurename~\ref{fig:cv} shows that models with both small and large numbers $p$ of parameters can make good predictions for held-out data, and that regularization can also protect a model from over-fitting, even when $p\approx n$.
+We don't mean to imply that over-fitting is not a problem in regression; it can be!
+Our recommendation is just that the problem of over-fitting be analyzed empirically through cross-validation, not through intuitive ideas about the number of parameters.
 
@@
 
-HOGG: INSERT POINT ABOUT OVER-CHOOSING YOUR HYPER-PARAMETERS: Over-fitting to the validation operator.
+There is one more point to make about over-fitting which is that, when your data set is small, it is possible to over-fit even your cross-validation.
+This problem is beyond the scope of this \documentname; all we will say here is that it is not possible to make precise settings of many hyper-parameters through cross validation.
+Because in cross validation you are making use of your data to set the properties of your regression, there are dangers of over-adapting your method to your data.
+It is safer to have a fully independent validation data set, but this is rarely practical (and it doesn't completely protect you either \citealt{SOLEDAD}).
 
@@
 You might think that all of this is academic, but it really isn't when the number of features $p$ is close to the number of data points $n$.
-For example, in our toy-data OLS experiments in this paper with $n=23$, the matrix $X^\top\,X$ has a condition number (ratio of largest eigenvalue to smallest nonzero eigenvalue) that saturates machine precision for the entire range $12 < p < 50$.
+For example, in our toy-data OLS experiments in this paper with $n=23$, the matrix $X^\top X$ has a condition number (ratio of largest eigenvalue to smallest nonzero eigenvalue) that saturates machine precision for the entire range $12 < p < 50$.
 And that's for $n=23$; things generally get worse as $n$ gets larger.
 
-Related to this, if you have a choice between formulations that involve an inverse of a square, like $(X^\top\,X)^{-1}\,X^\top\,Y$, and formulations that involve a pseudo-inverse, like $X^\dagger\,Y$, you should do the latter, because $X^\top\,X$ has the \emph{square} of the condition number of $X$.
+Related to this, if you have a choice between formulations that involve an inverse of a square, like $(X^\top X)^{-1}\,X^\top Y$, and formulations that involve a pseudo-inverse, like $X^\dagger\,Y$, you should do the latter, because $X^\top X$ has the \emph{square} of the condition number of $X$.
 When you want to execute $X^\dagger\,Y$, as we do in \eqref{eq:OLS3}, you should again use \code{lstsq()}, which was literally designed for these applications; use \code{lstsq(X, Y, rcond=tiny)}.
@@
 \appendix
-\section{Mathematical arguments and results}\label{app:math}
+\section{Mathematical arguments}\label{app:math}
 
@@
 \begin{equation} \label{qp}
-    \arg\min_x \frac{1}{2} x^T G x + x^\top c \quad \text{ subject to } Ax=b.
+    \arg\min_x \frac{1}{2} x^T G\, x + x^\top c \quad \text{ subject to } A\,x=b.
 \end{equation}
@@
 If the objective function in \eqref{qp} is convex, the KKT conditions are also sufficient for optimality\footnote{The KKT conditions can also characterize optimality in more general cases.
-For instance, if $A$ has full row rank and $Z$ is the nullspace of $A$, if $Z^\top G Z$ is positive semidefinite the KKT conditions are sufficient for optimality.
-If $Z^\top G Z$ is positive definite we also have that the solution of \eqref{qp} is unique (which is typically the case in the underparameterized linear regression but not in the overparameterized).}.
+For instance, if $A$ has full row rank and $Z$ is the nullspace of $A$, if $Z^\top G\, Z$ is positive semidefinite the KKT conditions are sufficient for optimality.
+If $Z^\top G\, Z$ is positive definite we also have that the solution of \eqref{qp} is unique (which is typically the case in the underparameterized linear regression but not in the overparameterized).}.
 
 Using this formulation it is easy to check that the solution of \eqref{eq:opt2} leads to predictions in \eqref{eq:ridge_sol}, and the solution of \eqref{eq:weighted} produce \eqref{eq:weighted_sol}.
+For instance, in order to show the latter we consider
+\begin{equation} \label{eq:weighted_app}
+    \hat{\beta} = \arg\min_\beta \|\Lambda^{1/2}\,\beta\|_2^2 ~~\mbox{subject to}~~ Y = X\,\beta
+    ~,
+\end{equation}
+or equivalently 
+\begin{equation}
+    \hat{\beta} = \arg\min_\beta \frac{1}{2}\beta^\top \Lambda\,\beta ~~\mbox{subject to}~~  X\,\beta = Y
+    ~,
+\end{equation}
+obtaining the formulation in \eqref{qp} for $G=\Lambda$, $c=0$, $A=X$, $b=Y$ and $x=\beta$. Using the KKT conditions we obtain
+\begin{equation}
+    \left[
+    \begin{matrix}
+    \hat \beta \\ 
+    \lambda^*
+    \end{matrix}\right] =
+    \left[
+    \begin{matrix}
+    \Lambda & X^\top \\ 
+    X & 0
+    \end{matrix}\right]^{-1}
+    \left[
+    \begin{matrix}
+    0 \\ 
+    Y
+    \end{matrix}\right],
+    \label{kkt2}
+\end{equation}
+(assuming the KKT matrix is invertible).
+Luckily there exists a complete characterization for the inverse of $2\times 2$ block matrices (see \cite{lu2002inverses}).
+In particular if $A$ and $D - CA^{-1}B$ are invertible matrices we have
+\begin{multline} 
+ {\begin{bmatrix}  {A} &   {B} \\  {C} &  {D} \end{bmatrix}}^{-1}= \\ {\begin{bmatrix}  {A} ^{-1}+  {A} ^{-1}  {B} \left(  {D} -  {CA} ^{-1}  {B} \right)^{-1}  {CA} ^{-1}& -  {A} ^{-1}  {B} \left(  {D} -  {CA} ^{-1}  {B} \right)^{-1}\\-\left(  {D} -  {CA} ^{-1}  {B} \right)^{-1}  {CA} ^{-1}& \left(  {D} -  {CA} ^{-1}  {B} \right)^{-1}\end{bmatrix}}.
+\end{multline}
+
+In the particular case of \eqref{kkt2} it suffices to compute the top right block the inverse. Obtaining that if both $\Lambda$ and $X\Lambda^{-1}X^\top$ are invertible we have 
+\begin{equation}
+    \hat \beta = \Lambda^{-1}X^\top(X\Lambda^{-1}X^\top)^{-1}Y. 
+\end{equation}
 

### 2021-01-12 paper/main.tex
soledad final edits

@@
+% This document is part of the FlexibleLinearModels project. Copyright 2021 the authors.
+
 % to-do
@@
 % - To be submitted to EPJ Data Science https://epjdatascience.springeropen.com/about
-% - Audit for use of \, as the multiply operator?
-% - HOGG: List clearly the assumptions underlying CVMSE and jackknife. They make assumptions about independence of the data points and also something maybe about per-point information content.
-% - SOLEDAD: address the point that some constraints may not be satisfiable
-% - Soledad: Once appendix is done, point down to it from the text at relevant places.
 
@@
 for valuable conversations and input.
-SV is partially funded by NSF DMS 2044349, EOARD FA9550-18-
-1-7007, and the NSF-Simons Research Collaboration on the Mathematical and Scientific
-Foundations of Deep Learning (MoDL) (NSF DMS-2031985).}}
+SV is partially funded by NSF DMS 2044349, EOARD FA9550-18-1-7007, and the NSF--Simons Research Collaboration on the Mathematical and Scientific Foundations of Deep Learning (MoDL) (NSF DMS-2031985).}}
 
@@
 This optimization objective \eqref{eq:opt1} is convex and the optimization problem has a solution in closed form\footnote{
-Note that $\nabla_{\beta} \|Y-X\beta\|^2 = 2X^\top(Y-X\beta)$ so critical points are such that $X^\top Y= X^\top X\beta$. Since the objective is convex all these critical points are global minima. 
+Note that $\nabla_{\beta} \|Y-X\beta\|^2 = 2X^\top(Y-X\beta)$ so critical points are such that $X^\top Y= X^\top X\beta$.
+Since the objective is convex all these critical points are global minima.
+Further analysis is given in Appendix \ref{app:math}.
 } as long as the number of parameters (and features) $p$ is less than the number of training points $n$ (and the matrix $X^\top X$ is invertible):
@@
 \end{equation}
-Examples of OLS applied to some toy data\footnote{The algorithm by which the toy data were made---and indeed all of the code executed to make the figures for this \documentname---is available online at \url{https://github.com/davidwhogg/FlexibleLinearModels}.} are shown in \figurename~\ref{fig:ols1}.
+Examples of OLS applied to some toy data\footnote{The algorithm by which the toy data were made---and indeed all of the code used to make the figures for this \documentname---is available online at \url{https://github.com/davidwhogg/FlexibleLinearModels}.} are shown in \figurename~\ref{fig:ols1}.
 This form \eqref{eq:OLS} of the prediction of new test data is called ordinary least squares (OLS). It has many good properties, some of which are encoded in the Gauss--Markov theorem.
@@
 \end{equation}
-where $I$ is the $p\times p$ identity.
+where $I$ is the $p\times p$ identity (see Appendix \ref{app:math}).
 In the language of Bayesian inference, $\lambda$ can be seen as the inverse of a prior variance for the parameters $\beta_j$.
@@
 \end{equation}
-in the limit, this delivers the OLS solution in either case.
+in the limit, this delivers the OLS solution in either case and doesn't require the constraint in \eqref{eq:opt2} to be satisfied.
 
@@
     \hat{\beta} = \lim_{\lambda\rightarrow 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\Lambda^{1/2}\,\beta\|_2^2\right]
-    ~.
+    ~,
 \end{equation}
+which doesn't require the constraints in \eqref{eq:weighted} to be satisfied. 
 This optimization\footnote{If you are a physicist and you don't like the mathematical $\|\cdot\|_2^2$ notation---if you prefer to look at quantities that are obvious scalar forms---then recall that $\|\Lambda^{1/2}\,\beta\|_2^2 = \beta^\top\Lambda\,\beta$.
@@
 \end{align}
-We discuss the equivalence of these below in \appendixname~\ref{app:math}.
+The equivalence of these is due to the Woodbury matrix identity \citep{henderson1981deriving}.
 These expressions appear in Bayesian-inference contexts (see, for example, \citealt{products}) when $\Lambda^{-1}$ is the variance of the prior on the parameter vector $\beta$ and $C$ is the variance of the noise on the data vector $Y$.
@@
 
-Given a data set (location--data pairs $t_i, y_i$), what is the best way to empirically estimate, from those data, the out-of-sample prediction error---that is, how do you estimate how well you are likely to predict new data?
-The only good answer to this is cross-validation:
+Given a data set (location--data pairs $t_i, y_i$), what is the best way to empirically estimate, from those data, the out-of-sample prediction error?
+That is, how do you estimate how well you are likely to predict new data?
+A reasonable answer to this is cross-validation:
 In cross-validation, we leave out a part of the data (in the most extreme form, leave out one single data point at a time), train the model using all but the left-out part, and predict the left-out part.
@@
 This leave-one-out cross-validation MSE (CVMSE) will be different for different choices for the basis, size ($p$), and regularization of the fits you do.
-It is a fairly reliable and well-studied method for assessing predictive accuracy (see, for example, \citealt{cv}), although it does depend on some assumptions (for example, about the distribution of predictive information across individual data points, maybe).
+It is a fairly reliable and well-studied method for assessing predictive accuracy (see, for example, \citealt{cv}), although it does depend on some assumptions (for example, that data points are not duplicated or strongly corrrelated, and that the predictive information in the data is distributed among multiple individual data points).
 An example of CVMSE for two models (the feature-weighted OLS and the ridge regression) are shown for our toy data, as a function of the number of features $p$, in \figurename~\ref{fig:cv}.
@@
 Because in cross validation you are making use of your data to set the properties of your regression, there are dangers of over-adapting your method to your data.
-It is safer to have a fully independent validation data set, but this is rarely practical (and it doesn't completely protect you either \citealt{SOLEDAD}).
+It is safer to have a fully independent validation data set, but this is rarely practical (and it doesn't completely protect you either \citealt{cifar10}).
 
@@
 
-In the particular case of \eqref{kkt2} it suffices to compute the top right block the inverse. Obtaining that if both $\Lambda$ and $X\Lambda^{-1}X^\top$ are invertible we have 
+In the particular case of \eqref{kkt2} it suffices to compute the top right block the inverse. Obtaining that if both $\Lambda$ and $X\,\Lambda^{-1}X^\top$ are invertible we have 
 \begin{equation}
-    \hat \beta = \Lambda^{-1}X^\top(X\Lambda^{-1}X^\top)^{-1}Y. 
+    \hat \beta = \Lambda^{-1}\,X^\top(X\,\Lambda^{-1}X^\top)^{-1}\,Y. 
 \end{equation}

### 2021-01-13 paper/main.tex
small tweaks and adjustments

@@
 % -----
+% - SOLEDAD: MAKE SECTION 7 NOT WRONG.
 % - To be submitted to EPJ Data Science https://epjdatascience.springeropen.com/about
@@
 They also choose an order, or number of basis functions to fit, and (often) some kind of regularization.
-Here we discuss how this basis-function fitting is done, with ordinary least squares and extensions thereof.
+We discuss how this basis-function fitting is done, with ordinary least squares and extensions thereof.
 We emphasize that it is often valuable to choose \emph{far more parameters than data points}, despite folk rules to the contrary:
@@
 It is even possible to take the limit of infinite parameters, at which, if the basis and regularization are chosen correctly, the least-squares fit becomes the mean of a Gaussian process.
-We recommend cross-validation as a good empirical method for model selection (for example, setting the number of parameters and the detailed form of the regularization),
+We recommend cross-validation as a good empirical method for model selection (for example, setting the number of parameters and the form of the regularization),
 and jackknife resampling as a good empirical method for estimating the uncertainties of the predictions made by the model.
@@
 And they have to decide how (or whether) to regularize the fit, or discourage fit coefficients from getting out of line when the data are noisy or the basis functions are close to (or strictly) degenerate.
-In what follows, we will discuss all three of these kinds of choices.
 
@@
 Instead of fitting a basis expansion, you can use a strict interpolator (like a cubic spline), or you can fit a Gaussian process to your data.
-Here we will show that the choice of any Gaussian process kernel function is equivalent to choosing a basis and a regularization and letting the number of fit components go to infinity (in a certain way).
+Here we will show that the choice of any Gaussian process kernel function is equivalent to choosing a basis and a regularization and letting the number of fit components go to infinity.
 That is, going non-parametric doesn't really get you out of making these choices.
@@
 That is---for us---only the data exist.
-The details of the model are just choices that permit high-quality interpolations and predictions.
+The details of the model are just choices that permit high-quality interpolations and predictions in the space of the data.
 
@@
 These settings are not what we are addressing here, but they are relevant and related
-(many good books exist, for example: \citealt{bishop, esl, agresti, gelman}).
+(many good books exist, for example, \citealt{bishop}, \citealt{esl}, \citealt{agresti}, \citealt{gelman}).
 In some ways, the most flexible of models currently in use are deep networks, where it is both the case that the input data often have enormous numbers of natural features, \emph{and} the deep network is capable of generating (effectively) far more, internally.
@@
 The over-para\-meterized case (more parameters than data) is discussed in \sectionname~\ref{sec:overpar}.
-The concept of feature weighting for over-parameterized fits is introduced in \sectionname~\ref{sec:fwols}.
+The concept of feature weighting for controlling regularization in over-parameterized fits is introduced in \sectionname~\ref{sec:fwols}.
 Cross-validation is explained and used to choose the number of parameters in \sectionname~\ref{sec:dd}, and the double descent phenomenon is shown.
@@
 In the machine-learning lexicon, these will be our ``training data''.
-This location $t_i$ could be thought of as a time at which the data point was taken, or a position, or it can be a higher dimensional vector or blob of housekeeping data associated with the data point.
+The location $t_i$ could be thought of as a time at which the data point was taken, or a position, or it can be a higher dimensional vector or blob of housekeeping data associated with the data point.
 Critically, we are going to imagine that the $t_i$ are known very well (not very uncertain or noisy), while the $y_i$ are possibly very uncertain or noisy measurements.
@@
 Alternative common choices would be to make the embedding functions $g_j(t)$ polynomials or other kinds of ordered basis functions, such as wavelets or spherical harmonics (the latter if, say, the $t_i$ are positions on the sphere).
-Another choice that isn't common in the natural sciences, but highly studied in machine learning (for example, \citealt{rahimi2007random}), is to choose the features randomly from a distribution (rather than on a regular grid in frequency, as we do here).
+Another choice that isn't common in the natural sciences, but studied in machine learning (for example, \citealt{rahimi2007random}), is to choose the features randomly from a distribution (rather than on a regular grid in frequency, as we do here).
 That is beyond our scope, but we come back to it in \sectionname~\ref{sec:discussion}.
@@
 \end{equation}
-where $\hat{\beta}$ is the $p$-vector (column vector) of the $p$ best-fit values $\hat{\beta}_j$ of the parameters $\beta_j$, and $\|q\|_2^2$ denotes the squared L2-norm, or the \emph{sum of squares} of the components of $q$
+where $\hat{\beta}$ is the $p$-vector (column vector) of the $p$ best-fit values $\hat{\beta}_j$ of the parameters $\beta_j$, and $\|q\|_2^2$ denotes the squared L2-norm, or the \emph{sum of squares} of the components of a vector $q$
 \begin{equation}
@@
 This form \eqref{eq:OLS} of the prediction of new test data is called ordinary least squares (OLS). It has many good properties, some of which are encoded in the Gauss--Markov theorem.
-In particular, if the noise contributions in the model given in equation \eqref{eq.model} are uncorrelated, have zero mean, and equal variances for $i=1,\ldots, n$ then the Gauss--Markov theorem states that the OLS estimator has the lowest variance within the class of unbiased estimators that are linear in $Y$ (see, for example, \citealt{esl}, Ch 3).
+In particular, if the noise contributions in the model given in equation \eqref{eq.model} are uncorrelated, have zero mean, and equal variances for $i=1,\ldots, n$ then the Gauss--Markov theorem states that the OLS estimator has the lowest variance within the class of unbiased estimators that are linear in $Y$ (see, for example, \citealt{esl}, Ch.~3).
 \begin{figure}[t]
@@
 That is, if $R$ is an invertible $p\times p$ matrix, the prediction using $X'\leftarrow X\,R$ will be identical to the prediction using the original $X$.
-This affine invariance will return in a different form in the over-parameterized regime, below.
+This affine invariance will be modified in the over-parameterized regime, below.
 
@@
 This form \eqref{eq:wls} of least squares is called \emph{weighted least squares} (WLS) because of the data weighting (not to be confused with \emph{feature} weighting, to appear below).
-It is also called chi-squared fitting because it optimizes the scalar objective commonly called chi-squared:
+It is also called \emph{chi-squared fitting} because it optimizes the scalar objective commonly called chi-squared:
 \begin{equation}
@@
 It might be crossing your mind that there are uncertainties not just in the data points $y_i$, but also often in the \emph{locations} $t_i$ of the data as well.
-It turns out that taking the latter into account is a much harder problem; we return to this also in \sectionname~\ref{sec:uncertainty}.
+It turns out that taking the latter into account is a much harder problem; we will discuss this briefly in \sectionname~\ref{sec:uncertainty}.
 
@@
 The regularized fit looks more sensible, though it fits the individual data points less precisely.
-The choice of regularization parameter $\lambda$ matters; here we used $\lambda=0.1$ (chosen arbitrarily).}
+The choice of regularization parameter $\lambda$ matters; here we used $\lambda=0.1$ (chosen heuristically by hand).}
     \label{fig:ridge}
@@
 But it is true that the $p>n$ regime is indeed strange!
-In the over-parameterized case, there are many settings of the parameters $\beta_j$ that will literally zero out the differences between the data $Y$ and the linear prediction $X\,\beta$.
+In the over-parameterized case, there are typically many settings of the parameters $\beta_j$ that will literally zero out the differences between the data $Y$ and the linear prediction $X\,\beta$.
 The OLS solution, in this case, is defined (somewhat arbitrarily) to be the minimum-norm parameter vector $\beta$ that interpolates the data:
@@
 This means that the integral over frequency of the square of the Fourier transform is equal to the integral over location of the square of the original function.
-Thus the min-norm solution delivered by OLS, which chooses the interpolating function that minimizes the squares of the component amplitudes in the Fourier basis used to make \figurename~\ref{fig:ols2} will also choose the interpolating function that minimizes the square of the value of the function.
+Thus the min-norm solution delivered by OLS, which chooses the interpolating function that minimizes the squares of the component amplitudes $\beta$ in the Fourier basis used to make \figurename~\ref{fig:ols2}, will choose the interpolating function $y(t)$ that minimizes the mean square of the value of the function in the location space.
 It will try to stay as close to $y=0$ as possible.
@@
 That is, rotations and scalings in the feature space \emph{will} affect predictions.
-It behooves us to re-scale the features (the $p$ $n$-vectors of the feature matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features (\citealt{xie2020weighted, bah2016sample, rauhut2016interpolation}).
+It behooves us to re-scale the features (the $p$ $n$-vectors of the feature matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features (\citealt{xie2020weighted}, \citealt{bah2016sample}, \citealt{rauhut2016interpolation}).
 We can encode these feature weights in a $p\times p$ diagonal weight matrix $\Lambda^{-1}$ and the prediction becomes
@@
     \hat{Y}_\ast = X_\ast\,\Lambda^{-1}\,X^\top (X\,\Lambda^{-1}\,X^\top)^{-1}\,Y
+    ~.
 \end{equation}
@@
     \hat{\beta} = \lim_{\lambda\rightarrow 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\Lambda^{1/2}\,\beta\|_2^2\right]
-    ~,
+    ~.
 \end{equation}
-which doesn't require the constraints in \eqref{eq:weighted} to be satisfied. 
+This doesn't require the constraints in \eqref{eq:weighted} to be satisfied. 
 This optimization\footnote{If you are a physicist and you don't like the mathematical $\|\cdot\|_2^2$ notation---if you prefer to look at quantities that are obvious scalar forms---then recall that $\|\Lambda^{1/2}\,\beta\|_2^2 = \beta^\top\Lambda\,\beta$.
@@
 The feature-weighting function is given in the text in equations~\eqref{eq:f} and \eqref{eq:lambdainv}; in this and the following \figurename s, we (somewhat arbitrarily) set the width parameter to be $s=0.05$.
-When the high-frequency features are weighted down, the min-norm solution gives them small amplitudes, making the fit smoother.}
+Because this weighting function penalizes more strongly the higher-frequency features, the min-norm solution gives them smaller amplitudes, making the fit smoother.}
     \label{fig:fwols}
@@
 
+If we think of the OLS choice $\hat{\beta}$---the min-norm vector among all vectors $\beta$ that thread the data (satisfy $X\,\beta = Y$)---as the result of a kind of light regularization, then the feature weighting is an adjustment of the form of that regularization:
+It asks the optimization to pull some components of $\beta$ towards zero harder than others.
+In our view, feature weighting should be considered part of the investigator's choice of regularization.
+The feature weighting can be thought of as altering the details of that choice, or it can be thought of as making the standard min-norm choice but in a carefully chosen, rescaled basis.
+
 In the most general case, you have not just a set of feature weights $\Lambda^{-1}$, you also have a set of data-point weights $C^{-1}$ (which, in standard settings, would be the inverses of the variances of the noise affecting the data points $y_i$).
@@
 \end{align}
-The equivalence of these is due to the Woodbury matrix identity \citep{henderson1981deriving}.
+The equivalence of these is due to the Woodbury matrix identity (\citealt{henderson1981deriving}).
 These expressions appear in Bayesian-inference contexts (see, for example, \citealt{products}) when $\Lambda^{-1}$ is the variance of the prior on the parameter vector $\beta$ and $C$ is the variance of the noise on the data vector $Y$.
@@
 
-There is a lot of literature analyzing the performance of linear regressions as a function of the sizes $n$ and $p$, regularization strengths and forms, and so on (for example, \citealt{bartlett2020benign}, \citealt{hastie2019surprises} ).
+There is a lot of literature analyzing the performance of linear regressions as a function of the sizes $n$ and $p$, regularization strengths and forms, and so on (for example, \citealt{bartlett2020benign}, \citealt{hastie2019surprises}).
 They often refer to the ``risk'', which is a statistics term for the expected squared error (mistake) made when predicting new data not in your training set.
@@
 The prediction for the mean-squared error (MSE) for new data is the mean of the square of the differences between the leave-one-out predictions and the left-out data.
-This leave-one-out cross-validation MSE (CVMSE) will be different for different choices for the basis, size ($p$), and regularization of the fits you do.
+This leave-one-out cross-validation MSE (CVMSE) will be different for different choices for the basis, size ($p$), and regularization (including feature-weight functions) of the fits you do.
 It is a fairly reliable and well-studied method for assessing predictive accuracy (see, for example, \citealt{cv}), although it does depend on some assumptions (for example, that data points are not duplicated or strongly corrrelated, and that the predictive information in the data is distributed among multiple individual data points).
 An example of CVMSE for two models (the feature-weighted OLS and the ridge regression) are shown for our toy data, as a function of the number of features $p$, in \figurename~\ref{fig:cv}.
-The predictive accuracy is indeed a function of $p$.
+The predictive accuracy is indeed a very strong function of $p$.
 \begin{figure}[t]
@@
 It is extremely general.
-There is an effect known in many kinds of regression called ``double descent'' or ``peaking phenomenon'' or ``jamming'' in which predictive accuracy becomes very poor when the number of free parameters $p$ comes close to the number of data points $n$ (\citealt{jain198239, spigler2018jamming, geiger2019jamming}).
-For linear models, the ``risk''---the out-of-sample prediction error---blows up when the model capacity just becomes excessive; at $p=n$ (\citealt{hastie2019surprises}).
-The fundamental reason for this phenomenon is that the ordinary least squares estimates \eqref{eq:OLS} and \eqref{eq:OLS2} require to compute the inveses $(X^\top X)^{-1}$ and $(X\,X^\top)^{-1}$ respectively, which are very badly conditioned around $p\approx n$.
+There is an effect known in many kinds of regression called ``double descent'' or ``peaking phenomenon'' or ``jamming'' in which predictive accuracy becomes very poor when the number of free parameters $p$ comes close to the number of data points $n$ (\citealt{jain198239}, \citealt{spigler2018jamming}, \citealt{geiger2019jamming}).
+For linear models, the ``risk''---the out-of-sample prediction error---blows up when the model capacity just becomes excessive at $p=n$ (\citealt{hastie2019surprises}).
+The fundamental reason for this phenomenon is that the ordinary least-squares estimates \eqref{eq:OLS} and \eqref{eq:OLS2} require computation of the inverses $(X^\top X)^{-1}$ and $(X\,X^\top)^{-1}$ respectively, which are very badly conditioned around $p\approx n$.
 This translates to a large variance for the estimator $\hat \beta$ which implies a large risk.
@@
 The high-risk behavior at $p\approx n$ disappears with certain kinds of regularization.
-These include the ridge regularization shown in \figurename~\ref{fig:cv} (also known as Tikhonov regression), but also early stopping \citep{hastie2019surprises}, and dimensionality reduction \citep{huang2020dimensionality}.
+These include the ridge regularization shown in \figurename~\ref{fig:cv} (also known as Tikhonov regression), but also early stopping (\citealt{hastie2019surprises}), and dimensionality reduction (\citealt{huang2020dimensionality}).
 
@@
 
-There is one more point to make about over-fitting which is that, when your data set is small, it is possible to over-fit even your cross-validation.
+That said, there is one more point to make about over-fitting, which is that, when your data set is small, it is possible to over-fit even your cross-validation.
 This problem is beyond the scope of this \documentname; all we will say here is that it is not possible to make precise settings of many hyper-parameters through cross validation.
 Because in cross validation you are making use of your data to set the properties of your regression, there are dangers of over-adapting your method to your data.
-It is safer to have a fully independent validation data set, but this is rarely practical (and it doesn't completely protect you either \citealt{cifar10}).
+It is safer to have a fully independent validation data set, but this is rarely practical (and it doesn't completely protect you either; see \citealt{cifar10}).
 
@@
 As before, in contexts where you have independent uncertainties on each element $y_i$ of your training data $Y$, $C^{-1}$ would naturally be set to the diagonal matrix containing the inverses of the variances of those uncertainties (so $C$ would contain the variances).
-This form \eqref{eq:gpC} is used a lot in astronomy and cosmology (for example, \citealt{zaroubi, aigrain, celerite}) and it is also the standard form given for the Wiener filter, where the kernel function generating $K$ is the Fourier transform of the ``signal power'' and the kernel function generating $C$ is the Fourier transform of the ``noise power''.
+This form \eqref{eq:gpC} is used a lot in astronomy and cosmology (for example, \citealt{zaroubi}, \citealt{aigrain}, \citealt{celerite}) and it is also the standard form given for the Wiener filter, where the kernel function generating $K$ is the Fourier transform of the ``signal power'' and the kernel function generating $C$ is the Fourier transform of the ``noise power''.
 In this form, the amplitude of the kernel function matters, because it is competing, in some sense, the variance $K$ of the GP against the variance $C$ of the noise.
@@
 That scenario is best-case, but it does involve a lot of assumptions.
-That is, if you don't trust your estimates of the noise variances, or if you think the noise might be non-Gaussian, or if you don't have plausible prior information, then the likelihood approaches will give poor uncertainty estimates.
+That is, if you don't trust your estimates of the noise variances, or if you think the noise might be non-Gaussian, then the likelihood approaches will give poor uncertainty estimates.
 In this sense, it is more conservative to make use of more empirical methods for uncertainty estimation.
@@
 
-One comment about the jackknife variance expression \eqref{eq:jackknife}: The prefactor before the sum is $(n-1)/n$, not the usually expected $1/(n-1)$.
-This difference comes from the fact that the $n$ jackknife trials are not uncorrelated: They share data.
-The variance of the uncertainty is therefore larger than the variance across jackknife trials by a factor of order $n$ (the factor is $(n-1)^2/n$ to be precise).
-
 These methods---full likelihood analysis and jackknife---take into account (1)~the noise in the data $y_i$ and (2)~the number and spacing of the training data points.
@@
 
-All of the code used to make the figures for this \documentname\ is available publicly\footnote{\url{https://github.com/davidwhogg/FlexibleLinearModels}}.
+All of the code used to make the figures for this \documentname\ is available publicly.\footnote{\url{https://github.com/davidwhogg/FlexibleLinearModels}}
 Although the examples are toys, the implementation of everything can be generalized for real-data situations.
-In that code, there are some aspects of the linear-algebra implementation that might seem odd.
+In our code, there are some aspects of the linear-algebra implementation that might seem odd.
 Here are some comments.
@@
 And you can invert by just inverting the diagonal entries.
-Avoid constructing and operating on operators that are almost entirely zeros.
+Avoid constructing and operating on operators that are almost entirely zeros, unless you have a very efficient sparse linear algebra implementation and you are a power user.
 
@@
 We encouraged you to consider using very big models, but being intentional about regularization.
-These settings (over-parameterized, but carefully regularized) are adaptive and useful, and they connect, as we showed, to Gaussian processes in the limit, which are well-studied workhorses of data science.
+These settings (over-parameterized, but carefully regularized) are adaptive and useful, and they connect, as we showed, to Gaussian processes in the limit, which are well-studied workhorses of machine learning and data science.
 
@@
 Usually this kind of consideration is less important in interpolation, prediction, and de-noising settings, but it is not unheard of.
-A nice recent result is that the feature weighting that we employ here can be used with L1 regularization to obtain simultaneously smoothness and sparsity \citep{rauhut2016interpolation}.
+A nice recent result is that the feature weighting that we employ here can be used with L1 regularization to obtain simultaneously smoothness \emph{and} sparsity (\citealt{rauhut2016interpolation}).
 
@@
 
-To derive the optimal solutions of the constrained optimization we use a classical result in quadratic optimization (see for instance Chapter 16 of \cite{nocedal2006numerical}).
-
+To derive the optimal solutions of the constrained optimization \eqref{eq:opt2} and similar, we use a classical result in quadratic optimization (see for instance \citealt{nocedal2006numerical}, Ch.~16):
 Consider the quadratic optimization problem 
 \begin{equation} \label{qp}
-    \arg\min_x \frac{1}{2} x^T G\, x + x^\top c \quad \text{ subject to } A\,x=b.
+    \arg\min_x \frac{1}{2} x^T G\, x + x^\top c \quad \text{ subject to } A\,x=b
+    ~.
 \end{equation}
-
 The first-order necessary conditions for $x^*$ to be a solution of \eqref{qp} is that there is a vector $\lambda^*$ (known as Lagrange multipliers) such that the following system of equations is satisfied:
-
 %Assume that $A$ has full row rank and let $Z$ be such that its columns form a basis for the null space of $A$ (i.e.
@@
     b
-    \end{matrix}\right].
+    \end{matrix}\right]
+    ~.
     \label{kkt}
@@
 Equation \eqref{kkt} is typically known as the Karush-Kuhn-Tucker conditions (KKT).
-If the objective function in \eqref{qp} is convex, the KKT conditions are also sufficient for optimality\footnote{The KKT conditions can also characterize optimality in more general cases.
+If the objective function in \eqref{qp} is convex, the KKT conditions are also sufficient for optimality.\footnote{The KKT conditions can also characterize optimality in more general cases.
 For instance, if $A$ has full row rank and $Z$ is the nullspace of $A$, if $Z^\top G\, Z$ is positive semidefinite the KKT conditions are sufficient for optimality.
-If $Z^\top G\, Z$ is positive definite we also have that the solution of \eqref{qp} is unique (which is typically the case in the underparameterized linear regression but not in the overparameterized).}.
+If $Z^\top G\, Z$ is positive definite we also have that the solution of \eqref{qp} is unique (which is typically the case in the underparameterized linear regression but not in the overparameterized).}
 
@@
     Y
-    \end{matrix}\right],
+    \end{matrix}\right]
+    ~,
     \label{kkt2}
@@
 (assuming the KKT matrix is invertible).
-Luckily there exists a complete characterization for the inverse of $2\times 2$ block matrices (see \cite{lu2002inverses}).
+Luckily there exists a complete characterization for the inverse of $2\times 2$ block matrices (see, for example, \citealt{lu2002inverses}).
 In particular if $A$ and $D - CA^{-1}B$ are invertible matrices we have
 \begin{multline} 
- {\begin{bmatrix}  {A} &   {B} \\  {C} &  {D} \end{bmatrix}}^{-1}= \\ {\begin{bmatrix}  {A} ^{-1}+  {A} ^{-1}  {B} \left(  {D} -  {CA} ^{-1}  {B} \right)^{-1}  {CA} ^{-1}& -  {A} ^{-1}  {B} \left(  {D} -  {CA} ^{-1}  {B} \right)^{-1}\\-\left(  {D} -  {CA} ^{-1}  {B} \right)^{-1}  {CA} ^{-1}& \left(  {D} -  {CA} ^{-1}  {B} \right)^{-1}\end{bmatrix}}.
+ {\begin{bmatrix}  {A} &   {B} \\  {C} &  {D} \end{bmatrix}}^{-1}= \\ {\begin{bmatrix}  {A} ^{-1}+  {A} ^{-1}  {B} \left(  {D} -  {CA} ^{-1}  {B} \right)^{-1}  {CA} ^{-1}& -  {A} ^{-1}  {B} \left(  {D} -  {CA} ^{-1}  {B} \right)^{-1}\\-\left(  {D} -  {CA} ^{-1}  {B} \right)^{-1}  {CA} ^{-1}& \left(  {D} -  {CA} ^{-1}  {B} \right)^{-1}\end{bmatrix}}
+ ~.
 \end{multline}
 
-In the particular case of \eqref{kkt2} it suffices to compute the top right block the inverse. Obtaining that if both $\Lambda$ and $X\,\Lambda^{-1}X^\top$ are invertible we have 
+In the particular case of \eqref{kkt2} it suffices to compute the top right block the inverse. If both $\Lambda$ and $X\,\Lambda^{-1}X^\top$ are invertible we obtain 
 \begin{equation}
-    \hat \beta = \Lambda^{-1}\,X^\top(X\,\Lambda^{-1}X^\top)^{-1}\,Y. 
+    \hat \beta = \Lambda^{-1}\,X^\top(X\,\Lambda^{-1}X^\top)^{-1}\,Y
+    ~. 
 \end{equation}
 
-\begin{comment}
-SOLEDAD: Maybe how you get from the optimization statements to the closed-form solutions, for the under- and over-parameterized cases?
-
-SOLEDAD: Maybe prove the equivalence of the expressions with $C$ and $\Lambda$.
-
-SOLEDAD: Maybe sketch some arguments about double descent?
-
-SOLEDAD: Maybe words or thoughts about Mercer's theorem and when the Fourier-transform correspondence we use here is applicable (and when it is not)?
-
-SOLEDAD: Other math details?
-\end{comment}
-
 \end{document}

### 2021-01-14 paper/main.tex
tweaks to GP section

@@
 But like most folk rules, it has a strong basis in reality: There are extremely bad choices possible for the number of coefficients, and especially when the number of parameters is close or comparable to the number of data points.
-As we will discuss below, these choices ought to be avoided, or made with care.
+As we will discuss below, these choices ought to be made with care.
 
@@
 
-The Gaussian process (GP) is a non-parametric regression that takes training data $y_i$ at coordinates $t_i$, plus a kernel function, and makes predictions $\hat{y}_\ast$ for new data at new positions $t_\ast$.
+The Gaussian process (GP; see \citealt{gpml} for a complete introduction) is a non-parametric regression that takes training data $y_i$ at coordinates $t_i$, plus a kernel function, and makes predictions $\hat{y}_\ast$ for new data at new positions $t_\ast$.
 The Gaussian process mean prediction looks like%
@@
 \end{equation}
-where $K_\ast$ is the rectangular kernel matrix between test locations $t_\ast$ and training locations $t_i$, while $K$ is the square kernel matrix between training locations and themselves
+where $K$ is a square $n\times n$ kernel matrix between training locations and themselves
 \begin{equation}\label{eq:Kmatrix}
@@
 \end{equation}
-where $k(\cdot,\cdot)$ is a positive semi-definite kernel function.
+and $K_\ast$ is the same except it is the rectangular kernel matrix between test locations $t_\ast$ and training locations $t_i$;
+the function $k(\cdot,\cdot)$ is a positive semi-definite kernel function.
 Stated this simply, the GP looks like magic; our goal here is to connect this to the feature-weighted OLS from \sectionname~\ref{sec:fwols}.
@@
 The kernel function must be positive semi-definite because, among other things, it is describing the variance of a process, and variances are always non-negative.
-It turns out that you can guarantee that a kernel function is positive semi-definite if you can show that it is, itself, the Fourier transform of a non-negative function (this fact is known as Bochner's Theorem, see for instance \citealt{folland2016course}).
-(It is \emph{not} required, however, that the function $k(\cdot,\cdot)$ itself be non-negative at all values of the inputs; non-negative definiteness is a different condition entirely.)
+It turns out that you can guarantee that a kernel function is positive semi-definite if you can show that it is, itself, the Fourier transform of a non-negative function (Bochner's Theorem, see for example \citealt{folland2016course}).\footnote{It is \emph{not} required that the function $k(\cdot,\cdot)$ itself be non-negative; non-negative definiteness is a different condition entirely from non-negativity.}
 
@@
 That is, it can lead your code or implementation into very unstable linear-algebra operations.
-We discuss these issues below in \sectionname~\ref{sec:implementation}.
+We discuss how to handle these issues below in \sectionname~\ref{sec:implementation}.
 
@@
 For example, the function call \code{solve(A, b)} should give you the best estimate it can for the product $A^{-1}\,b$, whereas the function call \code{dot(inv(A), b)}, which is the same on paper, will give you the dot product between \code{b} and the best estimate that \code{inv()} can find for the inverse of \code{A}.
-When the condition number of $A$ is large, these two values can be very different, and the \code{solve()} will be better (this claim contradicts what is stated in the abstract of \citealt{solve}, but this claim is based on our real experiences with real matrices, so we stand by it).
-Use \code{solve(A, b)} and never \code{dot(inv(A), b)} unless there are compelling code-structure reasons to use the latter, such as repeated calls (but even then, a Cholesky decomposition and Cholesky-solves are probably more stable).
+When the condition number of $A$ is large, these two values can be very different, and the \code{solve()} will be better.\footnote{This claim contradicts what is stated in the abstract of \citet{solve}, but this claim is based on our real numerical experiments on real matrices, so we stand by it.
+What is uncontroversial is that \code{solve(A, b)} will always perform non-worse than \code{dot(inv(A), b)}; sometimes it will perform far better.}
+Use \code{solve(A, b)} and never \code{dot(inv(A), b)} unless there are compelling code-structure reasons to use the latter, such as repeated calls (but even then, a Cholesky decomposition followed by repeated Cholesky solves is probably a more stable solution).
 
@@
 
-In many cases, when the goal is just to interpolate or de-noise data, in the natural sciences, investigators use running means (or medians), low-pass filters, or explicit interpolators (like cubic spline interpolation).
+In many cases, when the goal is just to interpolate or de-noise data, investigators use running means (or medians), low-pass filters, or explicit interpolators (like cubic spline interpolation).
 These methods all have close relationships with what is written here.
@@
 In astronomy and cosmology contexts, it is common for the locations $t_i$ to be positions on the sphere, and it is common for the natural basis functions to be spherical harmonics, for example.
-
-We also generated our toy data with locations $t_i$ regularly spaced in the location space.
-None of our results or recommendations depend on the locations being equally spaced.
-The simple form for the feature weighting we suggest does, however, depend on the features being equally spaced in \emph{frequency} space.
 
@@
 \begin{equation}
-    \hat{\beta} = \arg\min_\beta \frac{1}{2}\beta^\top \Lambda\,\beta ~~\mbox{subject to}~~  X\,\beta = Y
+    \hat{\beta} = \arg\min_\beta \frac{1}{2}\,\beta^\top \Lambda\,\beta ~~\mbox{subject to}~~  X\,\beta = Y
     ~,

### 2021-01-15 paper/main.tex
version to submit to arXiv

@@
 % Hogg's issues
-\setlength{\topmargin}{-0.40in}
+\setlength{\topmargin}{-0.50in}
 \setlength{\headsep}{4ex}
-\setlength{\textheight}{9.20in}
+\setlength{\textheight}{9.30in}
 \setlength{\oddsidemargin}{0.5in}
@@
 \renewcommand\section{\@startsection {section}{1}{\z@}%
-  {-3.5ex \@plus -1ex \@minus -.2ex}%
-  {2.3ex \@plus.2ex}%
-  {\raggedright\normalfont\Large\bfseries}}
+  {-3.25ex \@plus -1ex \@minus -.2ex}%
+  {1.5ex \@plus .2ex}%
+  {\raggedright\normalfont\large\bfseries}}
 \makeatother
@@
 \begin{equation}\label{eq:opt3}
-    \hat{\beta} = \lim_{\lambda\rightarrow 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\beta\|_2^2\right]
+    \hat{\beta} = \lim_{\lambda\to 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\beta\|_2^2\right]
     ~;
@@
 \begin{equation}
-    \hat{\beta} = \lim_{\lambda\rightarrow 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\Lambda^{1/2}\,\beta\|_2^2\right]
+    \hat{\beta} = \lim_{\lambda\to 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\Lambda^{1/2}\,\beta\|_2^2\right]
     ~.
@@
 Above, we called the GP prediction the ``mean''. This is because the Gaussian process is a model for a mean \emph{and variance} in function space.
-In addition to the mean $\hat{Y}_\ast$ predicted in \eqref{eq:gpmean}, the GP also predicts a \emph{variance} in the $Y_\ast$ space around that mean.
+In addition to the mean $\hat{Y}_\ast$ predicted\footnote{There is an additional point worthy of mention here, which is that the expression \eqref{eq:gpmean} is implicitly for a GP with a zero prior mean.
+There is a more general expression that subtracts a prior mean function from the $Y$ values and adds the prior mean back in to the $\hat{Y}_\ast$ values.
+See \citet{gpml} for all the math.} in \eqref{eq:gpmean}, the GP also predicts a \emph{variance} in the $Y_\ast$ space around that mean.
 In this \documentname, we are going to treat the GP as producing only a mean prediction, where the shape of the kernel function matters, but the amplitude of the kernel function does not (the prediction is a ratio of kernel matrices, so the kernel amplitudes cancel).
 However, in Bayesian-inference contexts the amplitude of the GP kernel is important, and the predicted variances are important.
-(There is an additional point worthy of mention here, which is that the expression \eqref{eq:gpmean} is implicitly for a GP with a zero prior mean; there is a more general expression that subtracts a prior mean function from the $Y$ values and adds the prior mean back in to the $\hat{Y}_\ast$ values.)
 When we consider only the mean prediction of the GP, as we do here, then the GP is a kind of linear filter that operates on data $Y$ and predicts or interpolates to new data $Y_\ast$.
@@
 Importantly for us, there is a strong connection between the feature-weighted OLS and the GP.
-In particular, when we take the limit of infinite features ($p\rightarrow\infty$; provided the limit exists) we get kernel matrices $K$ in place of the $X\,\Lambda^{-1}\,X^\top$ matrix products:
+In particular, when we take the limit of infinite features ($p\to\infty$; provided the limit exists) we get kernel matrices $K$ in place of the $X\,\Lambda^{-1}\,X^\top$ matrix products:
 \begin{align}
-    \lim_{p\rightarrow\infty} X\,\Lambda^{-1}\,X^\top &= K
+    \lim_{p\to\infty} X\,\Lambda^{-1}\,X^\top &= K
     \\
-    \lim_{p\rightarrow\infty} X_\ast\,\Lambda^{-1}\,X^\top &= K_\ast
+    \lim_{p\to\infty} X_\ast\,\Lambda^{-1}\,X^\top &= K_\ast
     ~,
@@
 \begin{equation}
-    \lim_{p\rightarrow\infty} \sum_{j=1}^p [\Lambda^{-1}]_{jj}\,g_j(t)\,g_{j}(t') = k(t, t')
+    \lim_{p\to\infty} \sum_{j=1}^p [\Lambda^{-1}]_{jj}\,g_j(t)\,g_{j}(t') = k(t, t')
     ~,
@@
 The connection between the infinite basis chosen (the form and weighting of the features) and the kernel function is governed by Mercer's theorem (see \citealt{minh2006mercer}).
-However, if the basis is Fourier, as we chose above in \eqref{eq:basis}, and the spacing between modes ($\Delta\omega =\omega_{j+2}-\omega_j$) is small enough, the kernel becomes very close to the Fourier transform of the square of the weighting function $f(\omega)$ we use to weight the features.
+However, if the basis is Fourier, as we chose above in \eqref{eq:basis}, and the spacing between modes ($\Delta\omega =\omega_{j+2}-\omega_j$) is small enough, the kernel approximates the Fourier transform of the square of the weighting function $f(\omega)$ we use to weight the features.
 
@@
 This latter function is also known as the Mat\'ern $3/2$ kernel function; it will become the kernel function for the Gaussian process when we take the limit.
-In the limit $p\rightarrow\infty$, then, the specific example of a feature-weighted OLS given here becomes, in the limit, a GP with a kernel function very close to
+In the limit $\Delta\omega\to 0$ the specific example of the $p\to\infty$ feature-weighted OLS given here becomes a GP with kernel function $F(\cdot)$ (under the mild assumptions that guarantee that the discrete Fourier transform converges to the continuous Fourier transform, see \citealt{ft}):
 \begin{align}
-    k(t_i,t_{i'}) &= F(t_i-t_{i'})
+    k(t_i,t_{i'}) &\to F(t_i-t_{i'})
     \\ \label{eq:k}
@@
 \end{align}
-Provided that the spacing of the Fourier modes in frequency space is $\Delta\omega\ll 1 / \Delta t_{\max}$ and the maximum frequency is $\floor{p / 2}\,\Delta\omega \gg 1 / \min(s, \Delta t_{\min})$, where
+Technically, the kernel function $k(\cdot,\cdot)$ converges to the Fourier transform of the square of the weighting function $f^2(\cdot)$ in the limit $\Delta\omega\to 0$ (the definition of $k(\cdot,\cdot)$ already assumes $p\to \infty$).
+However, provided that the spacing of the Fourier modes in frequency space is $\Delta\omega\ll 1 / \Delta t_{\max}$ and the maximum frequency is $\floor{p / 2}\,\Delta\omega \gg 1 / \min(s, \Delta t_{\min})$, where
 \begin{align}
-    \Delta t_{\min} \equiv \min_{i\ne j}|t_i - t_j|
+    \Delta t_{\min} &\equiv \min_{i\ne j}|t_i - t_j|
     \\
-    \Delta t_{\max} \equiv \max_{i,j}|t_i - t_j|
+    \Delta t_{\max} &\equiv \max_{i,j}|t_i - t_j|
     ~,
 \end{align}
-it will be true that the OLS with feature weights $f(\omega)$ will be essentially identical to the mean of a GP with kernel $k(\Delta t) = \FT[f^2]$.
+it will be true that the OLS with feature weights $f(\omega)$ will closely approximate the mean of a GP with kernel $k(\Delta t) = \FT[f^2]$ (\citealt{ft}).
 The comparison of the OLS and GP is shown in \figurename~\ref{fig:gp}.
@@
 The particular kernel we obtain in equation \eqref{eq:k} is a stationary kernel, meaning it depends only on absolute values of time differences $|t - t'|$.
-Not all $p\rightarrow\infty$ kernels will be stationary.
-The limit $p\rightarrow\infty$ of $X\,\Lambda^{-1}\,X^\top$ in \eqref{eq.limit} leads to a stationary kernel $k(\cdot,\cdot)$ in this case because the feature embedding in $X$ is a set of sines and cosines.
+Not all $p\to\infty$ kernels will be stationary.
+The limit $p\to\infty$ of $X\,\Lambda^{-1}\,X^\top$ in \eqref{eq.limit} leads to a stationary kernel $k(\cdot,\cdot)$ in this case because the feature embedding in $X$ is a set of sines and cosines.
 Sines and cosines form a basis for translation-invariant function spaces.
-If we had made a different choice for our basis, such as polynomials or wavelets, we would have obtained a non-stationary kernel in the $p\rightarrow\infty$ limit.
+If we had made a different choice for our basis, such as polynomials or wavelets, we would have obtained a non-stationary kernel in the $p\to\infty$ limit.
 
@@
 In this form, the amplitude of the kernel function matters, because it is competing, in some sense, the variance $K$ of the GP against the variance $C$ of the noise.
-It is not sufficient to get the shape of the kernel function right to make a stable prediction of the mean, when using this form \eqref{eq:gpC}.
+It is not sufficient to get the shape of the kernel function right to make a stable prediction of the mean, when using form \eqref{eq:gpC}.
 
@@
 That is, the beliefs encoded in the data noise variance tensor $C$ also must represent your true beliefs if you don't want your answers distorted in bad ways.
-All of that is out of scope here, but we say things about it all elsewhere (\citealt{fitting}).
+All of that is out of scope here, but we say things about it all elsewhere (for example, \citealt{fitting}).
 
@@
 Indeed, a running mean, a low-pass filter, and a cubic-spline interpolator can all be written as a linear operator (the details of which depends on the locations $t_i$ of the data) acting on the input data vector $Y$, just like our linear fits produce linear operators.
-This means that in many cases, these methods can be translated into versions of the methods we present in this \documentname.
+This means that in many cases, these methods can be translated into versions of the methods we have presented in this \documentname.
 A full translation is beyond our scope, though.
@@
 Briefly, the idea with random features is that instead of weighting features that are regularly spaced in frequency space with a weighting function $f(\omega)$, we could have generated unweighted features but randomly from a probability distribution $\propto f^2(\omega)$.
-The same Gaussian process limit appears as $p\rightarrow\infty$ (provided we choose those features with appropriately random phases too).
+The same Gaussian process limit appears as $p\to\infty$ (provided we choose those features with appropriately random phases too).
 These random-feature approaches have rarely been used in the natural sciences, but they are potentially of interest in many applications.
@@
 However, \emph{it is often a great choice}.
-When you choose the Fourier basis (and---importantly---for every cosine term you include the corresponding sine term), the matrix $X\,\Lambda^{-1}\,X^\top$ (and the limiting kernel matrix $K$ at $p\rightarrow\infty$) has the property that every matrix element $[X\,\Lambda^{-1}\,X^\top]_{ii'}$ depends on (or can be calculated from) just the absolute difference $|t_i-t_{i'}|$.
+When you choose the Fourier basis (and---importantly---for every cosine term you include the corresponding sine term), the matrix $X\,\Lambda^{-1}\,X^\top$ (and the limiting kernel matrix $K$ at $p\to\infty$) has the property that every matrix element $[X\,\Lambda^{-1}\,X^\top]_{ii'}$ depends on (or can be calculated from) just the absolute difference $|t_i-t_{i'}|$.
 That is, in this basis, all fitting methods become technically \emph{stationary}.
@@
 \appendix
-\section{Mathematical arguments}\label{app:math}
+\section{Optimization arguments}\label{app:math}
 

### 2021-01-26 paper/main.tex
Updates from Overleaf

@@
 % -----
-% - SOLEDAD: MAKE SECTION 7 NOT WRONG.
+% - Is the GP relationship fully encoded in Bishop?
+If so, cite; if not, get more precise about what's new here.
+Also, maybe add a footnote in which we give the translation between our notation and Bishop's notation.
+Oh and thank Espinoza.
+% - Should we mention the "dual" representation? HOGG thinks we are going to the dual when we go from XTX to XXT.
+% - Should we do a CVMSE vs the s parameter to show that you can choose kernel parameters by CV as well? Let's start by performing an experiment in the notebook. Not for now.
 % - To be submitted to EPJ Data Science https://epjdatascience.springeropen.com/about
@@
 % text definitions
-\newcommand{\documentname}{\textsl{Note}}
+\newcommand{\documentname}{\textsl{Review}}
 \newcommand{\sectionname}{Section}
@@
 
-\section*{\raggedright Fitting very flexible models: Linear regression with large numbers of parameters%
-\footnote{%
-It is a pleasure to thank
-Jed Brown (CU Boulder),
-Dan Foreman-Mackey (Flatiron),
-Alessandro Gentilini,
-Teresa Huang (JHU),
-Sam Roweis (deceased),
-Adrian Price-Whelan (Flatiron),
-Bernhard Sch\"olkopf (MPI-IS),
-Kate Storey-Fisher (NYU),
-Rachel Ward (UT Austin), and
-Lily Zhao (Yale)
-for valuable conversations and input.
-SV is partially funded by NSF DMS 2044349, EOARD FA9550-18-1-7007, and the NSF--Simons Research Collaboration on the Mathematical and Scientific Foundations of Deep Learning (MoDL) (NSF DMS-2031985).}}
+\section*{Fitting very flexible models: Linear regression with large numbers of parameters}
 
 \noindent
-\textbf{David W. Hogg} \\
+\textbf{David W. Hogg}\footnote{Corresponding author: David W. Hogg \href{mailto:david.hogg@nyu.edu}{david.hogg@nyu.edu}.} \\
 \textsl{\footnotesize Flatiron Institute, a division of the Simons Foundation \\
@@
 
+\paragraph{Keywords:}
+regression
+---
+interpolation
+---
+Gaussian~processes
+\\ ---
+double~descent
+---
+cross-validation
+
+\clearpage
 \section{Introduction}
@@
 We'll try to be useful to you no matter where you're at.
-This document does not deliver new research results on the mathematics or statistics of regression.
-It is novel only in that it makes very specific the connection between regularized linear regression and Gaussian processes.
+This \documentname\ delivers a theoretical and practical discussion of linear regression and function interpolation; it does not deliver new research results.
+Our only novel contribution is to make a specific connection between regularized linear regression and Gaussian processes.
 
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{paper/fourier.pdf}
+    \includegraphics[width=\figurewidth]{./fourier.pdf}
     \caption{Examples of basis functions $g_j(t)$ from the basis given in equation~\eqref{eq:basis}.
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{paper/OLS-under.pdf}
+    \includegraphics[width=\figurewidth]{./OLS-under.pdf}
     \caption{Ordinary least-squares (OLS) fits (continuous lines) to a set of example data points (black dots).
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{paper/WLS.pdf}
+    \includegraphics[width=\figurewidth]{./WLS.pdf}
     \caption{Comparison of ordinary least-squares (OLS) and weighted least-squares (WLS) fits (continuous lines) to the example data (black dots).
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{paper/ridge.pdf}
+    \includegraphics[width=\figurewidth]{./ridge.pdf}
     \caption{Comparison of ordinary least-squares (OLS) and ridge-regression fits (continuous lines) to the example data (black dots).
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{paper/OLS-over.pdf}
+    \includegraphics[width=\figurewidth]{./OLS-over.pdf}
     \caption{Ordinary least-squares (OLS) or min-norm least-squares fits (continuous lines) to a set of example data points (black dots), but now for a few over-parameterized cases.
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{paper/weighted-OLS.pdf}
+    \includegraphics[width=\figurewidth]{./weighted-OLS.pdf}
     \caption{Comparison of ordinary least squares (OLS) to OLS with a specific feature weighting.
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{paper/weighted-WLS.pdf}
+    \includegraphics[width=\figurewidth]{./weighted-WLS.pdf}
     \caption{Comparison of the feature-weighted OLS shown in \figurename~\ref{fig:fwols} to the same but also including data weights $C^{-1}$, as in equations \eqref{eq:LambdaC1} and \eqref{eq:LambdaC2}.
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{paper/LOO.pdf}
+    \includegraphics[width=\figurewidth]{./LOO.pdf}
     \caption{A demonstration of leave-one-out cross-validation for one particular model.
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{paper/cross-validation.pdf}
+    \includegraphics[width=\figurewidth]{./cross-validation.pdf}
     \caption{Leave-one-out cross-validation estimates of mean squared prediction error for the feature-weighted OLS fits, as a function of the number of features $p$.
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{paper/GP.pdf}
+    \includegraphics[width=\figurewidth]{./GP.pdf}
     \caption{Comparison of feature-weighted ordinary least squares with a Gaussian process.
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{paper/uncertainty.pdf}
+    \includegraphics[width=\figurewidth]{./uncertainty.pdf}
     \caption{The jackknife-estimated uncertainty on an ordinary least squares fit.
@@
 
-This \documentname\ was about linear fitting with very flexible models, for interpolation, prediction, and de-noising of data.
-We encouraged you to consider using very big models, but being intentional about regularization.
+This \documentname\ is about linear fitting with very flexible models, for interpolation, prediction, and de-noising of data.
+We have encouraged you to consider using very big models, but being intentional about regularization.
 These settings (over-parameterized, but carefully regularized) are adaptive and useful, and they connect, as we showed, to Gaussian processes in the limit, which are well-studied workhorses of machine learning and data science.
@@
 
+\section*{Declarations}
+This section completes requirements for submission to \textit{EPJ Data Science}.
+
+\paragraph{Availability of data and materials:}
+All code and data used in this project are available at
+\url{https://github.com/davidwhogg/FlexibleLinearModels}
+
+\paragraph{Competing interests:}
+Does not apply.
+
+\paragraph{Funding:}
+DWH's work on this project was supported by the Flatiron Institute, a division of the Simons Foundation.
+SV's work on this project was supported by NSF DMS 2044349, EOARD FA9550-18-1-7007, and the NSF--Simons Research Collaboration on the Mathematical and Scientific Foundations of Deep Learning (MoDL) (NSF DMS-2031985).
+
+\paragraph{Authors' contributions:}
+The two authors contributed equally to the analysis and writing represented in this work.
+
+\paragraph{Acknowledgements:}
+It is a pleasure to thank
+Jed Brown (CU Boulder),
+Nestor Espinoza (STScI),
+Dan Foreman-Mackey (Flatiron),
+Alessandro Gentilini,
+Teresa Huang (JHU),
+Sam Roweis (deceased),
+Adrian Price-Whelan (Flatiron),
+Bernhard Sch\"olkopf (MPI-IS),
+Kate Storey-Fisher (NYU),
+Rachel Ward (UT Austin), and
+Lily Zhao (Yale)
+for valuable conversations and input.
+
 \end{document}

### 2021-03-02 paper/letter.tex

\documentclass{letter}
\usepackage{hyperref}
\signature{Soledad Villar}
\address{Department of Mathematics and Statistics \\ Mathematical Institute for Data Science \\ Johns Hopkins University}
\begin{document}

\begin{letter}{Foundations of Data Science Journal}
\opening{Dear Editors:}

Please consider our manuscript entitled ``Fitting very flexible models: Linear regression with large numbers of parameters" for publication in your journal.

Our note is intended to be an expository review article directed to scientists and data scientists. We address fundamental questions about over-parameterized linear regression and their connections to kernel regression, which are workhorses of contemporary data science. In particular, we emphasize the importance of regularization through a compelling example, we discuss cross-validation, and implementation considerations. We address active research in machine learning, such as the double descent phenomenon.

\closing{Yours Faithfully,}

%\encl{Copyright permission form}

\end{letter}
\end{document}

### 2021-03-02 paper/main.tex

@@
 % This document is part of the FlexibleLinearModels project. Copyright 2021 the authors.
+
+%Changes since submission on  2021-03-02
+%--
+%Do it!
 
@@
 % -----
-% - Is the GP relationship fully encoded in Bishop?
-If so, cite; if not, get more precise about what's new here.
-Also, maybe add a footnote in which we give the translation between our notation and Bishop's notation.
-Oh and thank Espinoza.
-% - Should we mention the "dual" representation? HOGG thinks we are going to the dual when we go from XTX to XXT.
+% - HOGG: Finish going through Acquaviva comments and incorporate / assess.
+% - BOTH: Take one more look through the abstract (and title) and see what needs to be adjusted.
+% - HOGG. It is a kernel even when p \ne \infty! Re-word stuff in section 7.
 % - Should we do a CVMSE vs the s parameter to show that you can choose kernel parameters by CV as well? Let's start by performing an experiment in the notebook. Not for now.
-% - To be submitted to EPJ Data Science https://epjdatascience.springeropen.com/about
 
@@
 \pagestyle{myheadings}
-\markright{\textcolor{gray}{\textsf{\upshape Fitting very flexible models / Hogg \& Villar}}}
+\markright{\textcolor{gray}{\textsf{\upshape Fitting very flexible models}}}
 \newlength{\figurewidth}
@@
 % text definitions
-\newcommand{\documentname}{\textsl{Review}}
+\newcommand{\documentname}{\textsl{expository note}}
 \newcommand{\sectionname}{Section}
@@
 \noindent
-\textbf{David W. Hogg}\footnote{Corresponding author: David W. Hogg \href{mailto:david.hogg@nyu.edu}{david.hogg@nyu.edu}.} \\
+\textbf{David W. Hogg} \\%\footnote{Corresponding author: David W. Hogg \href{mailto:david.hogg@nyu.edu}{david.hogg@nyu.edu}.} \\
 \textsl{\footnotesize Flatiron Institute, a division of the Simons Foundation \\
@@
 
-\paragraph{Abstract:} There are many uses for linear fitting; the context here is interpolation and denoising of data, as when you have calibration data and you want to fit a smooth, flexible function to those data.
-Or you want to fit a flexible function to de-trend a time series or normalize a spectrum.
-In these contexts, investigators often choose a polynomial basis, or a Fourier basis, or wavelets, or something equally general.
+\paragraph{Abstract:} There are many uses for linear fitting; we consider here the interpolation and denoising of data, as when the goal is to fit a smooth, flexible function to a set of noisy data points.
+Investigators often choose a polynomial basis, or a Fourier basis, or wavelets, or something equally general.
 They also choose an order, or number of basis functions to fit, and (often) some kind of regularization.
 We discuss how this basis-function fitting is done, with ordinary least squares and extensions thereof.
-We emphasize that it is often valuable to choose \emph{far more parameters than data points}, despite folk rules to the contrary:
+We emphasize that it can be valuable to choose \emph{far more parameters than data points}, despite folk rules to the contrary:
 Suitably regularized models with enormous numbers of parameters generalize well and make good predictions for held-out data; over-fitting is not (mainly) a problem of having too many parameters.
-It is even possible to take the limit of infinite parameters, at which, if the basis and regularization are chosen correctly, the least-squares fit becomes the mean of a Gaussian process.
+It is even possible to take the limit of infinite parameters, at which, if the basis and regularization are chosen correctly, the least-squares fit becomes the mean of a Gaussian process, or a kernel regression.
 We recommend cross-validation as a good empirical method for model selection (for example, setting the number of parameters and the form of the regularization),
@@
 If you have encountered and solved problems like these, you have made these three kinds of choices (sometimes implicitly).
-The second choice---about the number of coefficients to fit---is usually made heuristically, and often subject to the strongly believed opinion that you \emph{must have fewer parameters than data points}.
-Here we are going to show that this folk rule is not valid; you can go to extremely large numbers of coefficients without trouble.
+The second choice---about the number of coefficients to fit---is usually made heuristically, and often subject to the strongly believed opinion that we \emph{must have fewer parameters than data points}.
+Here we show that this folk rule is not valid; we can go to extremely large numbers of coefficients without trouble.
 But like most folk rules, it has a strong basis in reality: There are extremely bad choices possible for the number of coefficients, and especially when the number of parameters is close or comparable to the number of data points.
@@
 In many cases the third kind of choice---about regularization---is made implicitly, not explicitly.
-Here we are going to emphasize this choice and its importance, and its value in improving your results.
+Here we are going to emphasize this choice and its importance, and its value in improving results.
 
@@
 
-An important assumption or setting for the problems we are addressing in this \documentname\ will be that you care about predicting new data or interpolating the data, but you explicitly \emph{don't care} about the parameters of the fit or the weights of the basis functions \foreign{per se}.
+An important assumption or setting for the problems we are addressing in this \documentname\ will be that we care about predicting new data or interpolating the data, but we explicitly \emph{don't care} about the parameters of the fit or the weights of the basis functions \foreign{per se}.
 In this setting there are no important meanings to the components of the model.
@@
 
-In some contexts you have strong beliefs about the noise affecting your measurements. In other cases you don't.
-In some cases you have strong reasons to use a particular basis.
-In other cases you don't.
-The differences in these beliefs and the differences in your objectives will change what methods you choose and how you use and analyze them.
-We'll try to be useful to you no matter where you're at.
+In some contexts we have strong beliefs about the noise affecting our measurements. In other cases we don't.
+In some cases we have strong reasons to use a particular basis.
+In other cases we don't.
+The differences in these beliefs and the differences in our objectives will change what methods we choose and how we use and analyze them.
+
 This \documentname\ delivers a theoretical and practical discussion of linear regression and function interpolation; it does not deliver new research results.
-Our only novel contribution is to make a specific connection between regularized linear regression and Gaussian processes.
+Our only novel contribution is to make an explicit connection between regularized linear regression and Gaussian processes.
 
@@
 It is called variously a \emph{feature map} or a \emph{feature embedding}.
-We like ``embedding'' because it (almost always) raises the dimensionality of the locations $t$ into the $p$-dimensional space of the rows of $X$.
+The embedding raises the dimensionality of the locations $t$ into the $p$-dimensional space of the rows of $X$.
 
@@
 We are using the linear fit to interpolate the data, or de-noise the data, or predict new data.
-In these contexts, we don't care about the parameter vector $\hat{\beta}$ itself.
+In these contexts, we typically don't care about the parameter vector $\hat{\beta}$ itself.
 We care only about the predictions at a set of new ``test'' locations $t_\ast$, which will usually be different from the training locations $t_j$.
@@
 Although the OLS prediction \eqref{eq:OLS} is affine invariant with respect to $p$-dimensional transformations, it is \emph{not} affine invariant with respect to $n$-dimensional transformations, such as a re-weighting of the input data.
-Indeed, if you know weights or inverse variances for your data points, conceptually you can put them into a weight matrix $C^{-1}$ (written this way to emphasize that reweighting is usually inverse-variance weighting) and write
+Indeed, if we know weights or inverse variances for our data points, conceptually we can put them into a weight matrix $C^{-1}$ (written this way to emphasize that reweighting is usually inverse-variance weighting) and write
 \begin{equation}\label{eq:wls}
@@
 \end{equation}
-(If that isn't obviously chi-squared to you, recall that $C^{-1}$ is often diagonal and has the inverses of the squares of the data uncertainties on that diagonal.)
+%(If that isn't obviously chi-squared to you, recall that $C^{-1}$ is often diagonal and has the inverses of the squares of the data uncertainties on that diagonal.)
 In \figurename~\ref{fig:wls} a comparison of OLS and WLS is shown, for a case of non-trivial data weights, where the data weights are set to be the inverse squares of individual data-point uncertainties.
@@
 We will say more about noisy data and the propagation of uncertainties below in \sectionname~\ref{sec:uncertainty}.
-It might be crossing your mind that there are uncertainties not just in the data points $y_i$, but also often in the \emph{locations} $t_i$ of the data as well.
+It is true that in realistic scenarios there are uncertainties not just in the data points $y_i$, but also often in the \emph{locations} $t_i$ of the data as well.
 It turns out that taking the latter into account is a much harder problem; we will discuss this briefly in \sectionname~\ref{sec:uncertainty}.
@@
 The ridge brings with it a choice: How to set the hyper-parameter $\lambda$?
-We generally recommend cross-validation, to be discussed below in \sectionname~\ref{sec:dd}.
+We generally recommend cross-validation, to be discussed below in \sectionname~\ref{sec:dd}; cross-validation gives good results but it produces a slightly biased estimate \citep{cv-bias}.
 Ridge regression is not affine invariant in the sense that the standard OLS prediction \eqref{eq:OLS} is; that is, the effect of the regularization depends on the amplitudes and linear combinations of features placed in the feature matrix.
 This will become important later when we consider feature weights below.
-It is also the case that the regularization need not be proportional to the identity matrix: In principle any positive definite matrix $\Lambda$ could be used in place of $\lambda\,I$; this makes sense to consider when you have detailed prior beliefs about all the parameters $\beta_j$ or if those parameters are measured with different units (say).
+It is also the case that the regularization need not be proportional to the identity matrix: In principle any positive definite matrix $\Lambda$ could be used in place of $\lambda\,I$; this makes sense to consider when we have detailed prior beliefs about all the parameters $\beta_j$ or if those parameters are measured with different units (say).
 
-You can combine both the point weighting from WLS and the generalized ridge regression into a weighted ridge that looks like
+Combining both the point weighting from WLS and the generalized ridge regression into a weighted ridge yields to estimates
 \begin{equation}\label{eq:foo}
@@
 
-We are taught folklore, at a young age, that we can never fit for more parameters than we have data. That is, we can never work at $p>n$.
+We are taught folklore, that we can never fit for more parameters than we have data. That is, we can never work at $p>n$.
 This isn't true!
 Not only is it the case that we \emph{can} work at $p>n$, in many cases we \emph{should} work at $p>n$, and many real-world regressions do.
-But it is true that the $p>n$ regime is indeed strange!
-In the over-parameterized case, there are typically many settings of the parameters $\beta_j$ that will literally zero out the differences between the data $Y$ and the linear prediction $X\,\beta$.
+But it is true that the $p>n$ regime is indeed strange.
+In the over-parameterized case, there are typically many choices for the parameters $\beta_j$ that will literally zero out the differences between the data $Y$ and the linear prediction $X\,\beta$.
 The OLS solution, in this case, is defined (somewhat arbitrarily) to be the minimum-norm parameter vector $\beta$ that interpolates the data:
@@
 This optimization is again convex and has a unique solution, although that solution will depend on feature weights that we discuss in a moment.
-When the investigator knows uncertainties on the training data points $y_i$, this expression will change a bit; we return to that in the next \sectionname.
+%When the investigator knows uncertainties on the training data points $y_i$, this expression will change a bit; we return to that in the next \sectionname.
 The under-parameterized and over-parameterized optimization statements \eqref{eq:opt1} and \eqref{eq:opt2} can be unified into one form by considering the limit of light L2 regularization:
@@
 The three fits are very different, but they all go through all the data points exactly.
-As $p$ gets large, the fit function approaches $y=0$ almost everywhere; this is a consequence of Plancharel's Theorem (see text).}
+As $p$ gets large, the fit function approaches $y=0$ almost everywhere; this is a consequence of Plancharel's Theorem and the use of the Fourier basis (see text).}
     \label{fig:ols2}
@@
 It is slightly off-topic to notice that in \figurename~\ref{fig:ols2}, as $p$ gets very large, the OLS solution approaches $y=0$ everywhere that it can.
-This behavior is a direct consequence of Plancharel's theorem, which states that the Fourier transform is unitary (see for instance \citealt{folland2016course}).
+This behavior is a direct consequence of using the Fourier basis and Plancharel's theorem, which states that the Fourier transform is unitary (see for instance \citealt{folland2016course}).
 This means that the integral over frequency of the square of the Fourier transform is equal to the integral over location of the square of the original function.
@@
 This doesn't require the constraints in \eqref{eq:weighted} to be satisfied. 
-This optimization\footnote{If you are a physicist and you don't like the mathematical $\|\cdot\|_2^2$ notation---if you prefer to look at quantities that are obvious scalar forms---then recall that $\|\Lambda^{1/2}\,\beta\|_2^2 = \beta^\top\Lambda\,\beta$.
-That right-hand-side object is a gauge-invariant object so long as $\beta$ and $\Lambda$ are also gauge-invariant objects themselves.
-Yes, data analysis can have this kind of geometric structure!}
+This optimization
+%\footnote{If you are a physicist and you don't like the mathematical $\|\cdot\|_2^2$ notation---if you prefer to look at quantities that are obvious scalar forms---then recall that $\|\Lambda^{1/2}\,\beta\|_2^2 = \beta^\top\Lambda\,\beta$.
+%That right-hand-side object is a gauge-invariant object so long as $\beta$ and $\Lambda$ are also gauge-invariant objects themselves.
+%Yes, data analysis can have this kind of geometric structure!
+%}
 penalizes more strongly the parameters $\beta_j$ corresponding to features $g_j(t)$ with larger values of $[\Lambda^{1/2}]_{jj}$.
@@
 \begin{align}\label{eq:LambdaC1}
-    \hat{Y} &= X_\ast\,(X^\top C^{-1}\,X + \Lambda)^{-1}\,X^\top C^{-1}\,Y
+    \hat{Y}_\ast &= X_\ast\,(X^\top C^{-1}\,X + \Lambda)^{-1}\,X^\top C^{-1}\,Y
     \\ \label{eq:LambdaC2}
-    \hat{Y} &= X_\ast\,\Lambda^{-1}\,X^\top (X\,\Lambda^{-1}\,X^\top + C)^{-1}\,Y
+    \hat{Y}_\ast &= X_\ast\,\Lambda^{-1}\,X^\top (X\,\Lambda^{-1}\,X^\top + C)^{-1}\,Y
     ~.
@@
 This is appropriate in common, real situations in which data are noisy and the world is smooth.
-Which form you choose, between \eqref{eq:LambdaC1} and \eqref{eq:LambdaC2}, depends on a few things, but primarily $p/n$.
+Which form to choose, between \eqref{eq:LambdaC1} and \eqref{eq:LambdaC2}, depends on a few things, but primarily $p/n$.
 If $p<n$ it's both faster and more stable to use \eqref{eq:LambdaC1}; if $p>n$ it's faster and more stable to use \eqref{eq:LambdaC2}.
@@
 
-\section{How to set the number of parameters (and other hyper-parameters)}\label{sec:dd}
+\section{How to set the number of parameters and the double descent phenomenon}
+%(and other hyper-parameters)}
+\label{sec:dd}
 
-There is a lot of literature analyzing the performance of linear regressions as a function of the sizes $n$ and $p$, regularization strengths and forms, and so on (for example, \citealt{bartlett2020benign}, \citealt{hastie2019surprises}).
-They often refer to the ``risk'', which is a statistics term for the expected squared error (mistake) made when predicting new data not in your training set.
+There is a lot of literature analyzing the performance of linear regressions as a function of the sizes $n$ and $p$, regularization strengths and forms, and so on (for example, \citealt{dobriban2018high}, \citealt{bartlett2020benign}, \citealt{hastie2019surprises}).
+They often refer to the ``risk'', which is a statistics term for the expected squared error (mistake) made when predicting new data not in the training set.
 In order to deliver values or bounds on the risk, this literature depends on knowing how the data were generated, or the family of distributions from which the data ($X$ and $Y$ in our nomenclature) were drawn.
-In the Real World~(tm), you don't get this luxury.
-The data are given to you without documentation!
+%In the Real World~(tm), you don't get this luxury.
+When working with real data, we don't get this luxury (real data comes without documentation).
 Indeed, understanding the generating process of the world is the goal of investigations in the natural sciences (such as astronomy); the investigator does not know the generating process at the outset.
@@
 Given a data set (location--data pairs $t_i, y_i$), what is the best way to empirically estimate, from those data, the out-of-sample prediction error?
-That is, how do you estimate how well you are likely to predict new data?
+That is, how do we estimate how well we are likely to predict new data?
 A reasonable answer to this is cross-validation:
@@
 It is extremely general.
-There is an effect known in many kinds of regression called ``double descent'' or ``peaking phenomenon'' or ``jamming'' in which predictive accuracy becomes very poor when the number of free parameters $p$ comes close to the number of data points $n$ (\citealt{jain198239}, \citealt{spigler2018jamming}, \citealt{geiger2019jamming}).
+There is an effect known in many kinds of regression called ``double descent'' or ``peaking phenomenon'' or ``jamming'' in which predictive accuracy becomes very poor when the number of free parameters $p$ comes close to the number of data points $n$ (\citealt{jain198239}, \citealt{belkin2019reconciling}, \citealt{spigler2018jamming}, \citealt{geiger2019jamming}).
 For linear models, the ``risk''---the out-of-sample prediction error---blows up when the model capacity just becomes excessive at $p=n$ (\citealt{hastie2019surprises}).
@@
 That's not surprising; there are places where the fit basis and size and feature weighting are all more appropriate for your specific problem.
-These good-CVMSE places are the best places to work, if you can afford to search for them and find them.
-In general, if you care about predictive accuracy, it is worth doing a search for the values of $p$ (and other hyper-parameters, like regularization strengths and feature-weighting function parameters) that minimize the CVMSE.
+These good-CVMSE places are the best places to work, if we can afford to search for them and find them.
+In general, if we care about predictive accuracy, it is worth doing a search for the values of $p$ (and other hyper-parameters, like regularization strengths and feature-weighting function parameters) that minimize the CVMSE.
 The minimum-CVMSE choices for $p$ and the hyper-parameters will generally be very close to the choices that lead to the best predictions for new data.
 
-That said, there is one more point to make about over-fitting, which is that, when your data set is small, it is possible to over-fit even your cross-validation.
+That said, there is one more point to make about over-fitting, which is that, when our data set is small, it is possible to over-fit the cross-validation.
 This problem is beyond the scope of this \documentname; all we will say here is that it is not possible to make precise settings of many hyper-parameters through cross validation.
-Because in cross validation you are making use of your data to set the properties of your regression, there are dangers of over-adapting your method to your data.
-It is safer to have a fully independent validation data set, but this is rarely practical (and it doesn't completely protect you either; see \citealt{cifar10}).
+Because in cross validation we are making use of our data to set the properties of our regression, there are dangers of over-adapting our method to our data.
+It is safer to have a fully independent validation data set, but this is rarely practical (and it doesn't completely protect us either; see \citealt{cifar10}).
 
-By the way, you might have felt uncomfortable with dropping individual points in this problem, since the points are sort-of regularly spaced in the location space (the $t$ space) to begin with, and become more irregularly spaced when you leave one out.
-How much does this matter?
-It probably \emph{does} matter in detail, but you don't have much choice in problems like this.
-All empirical measures of predictive accuracy have these kinds of problems.
+%By the way, you might have felt uncomfortable with dropping individual points in this problem, since the points are sort-of regularly spaced in the location space (the $t$ space) to begin with, and become more irregularly spaced when you leave one out.
+%How much does this matter?
+%It probably \emph{does} matter in detail, but you don't have much choice in problems like this.
+%All empirical measures of predictive accuracy have these kinds of problems.
 
@@
 and $K_\ast$ is the same except it is the rectangular kernel matrix between test locations $t_\ast$ and training locations $t_i$;
-the function $k(\cdot,\cdot)$ is a positive semi-definite kernel function.
+the function $k(\cdot,\cdot)$ is a symmetric, positive semi-definite kernel function.
 Stated this simply, the GP looks like magic; our goal here is to connect this to the feature-weighted OLS from \sectionname~\ref{sec:fwols}.
@@
 First, what does it mean for a kernel function $k(\cdot,\cdot)$ to be positive semi-definite?
-It means that no matter what set of $n$ locations $t_i$ you choose, the $n\times n$ kernel matrix $K$ made from the function according to \eqref{eq:Kmatrix} has only non-negative, real eigenvalues.
+It means that for all sets of $n$ locations $\{t_i\}_{i=1}^n$ the $n\times n$ kernel matrix $K$ made from the function according to \eqref{eq:Kmatrix} has only non-negative, real eigenvalues.
 The kernel function must be positive semi-definite because, among other things, it is describing the variance of a process, and variances are always non-negative.
-It turns out that you can guarantee that a kernel function is positive semi-definite if you can show that it is, itself, the Fourier transform of a non-negative function (Bochner's Theorem, see for example \citealt{folland2016course}).\footnote{It is \emph{not} required that the function $k(\cdot,\cdot)$ itself be non-negative; non-negative definiteness is a different condition entirely from non-negativity.}
+It turns out that we can guarantee that a kernel function is positive semi-definite if we can show that it is, itself, the Fourier transform of a non-negative function (Bochner's Theorem, see for example \citealt{folland2016course}).\footnote{It is \emph{not} required that the function $k(\cdot,\cdot)$ itself be non-negative; non-negative definiteness is a different condition entirely from non-negativity.}
 
@@
 When we consider only the mean prediction of the GP, as we do here, then the GP is a kind of linear filter that operates on data $Y$ and predicts or interpolates to new data $Y_\ast$.
-Classically, this linear filter is sometimes called a Wiener filter (more on this in a moment) or \emph{kriging} (possibly because of \citealt{krige}).
+Classically, this linear filter is sometimes called kernel regression, a Wiener filter, or \emph{kriging} (possibly because of \citealt{krige}).
 
@@
 However, if the basis is Fourier, as we chose above in \eqref{eq:basis}, and the spacing between modes ($\Delta\omega =\omega_{j+2}-\omega_j$) is small enough, the kernel approximates the Fourier transform of the square of the weighting function $f(\omega)$ we use to weight the features.
+The convergence of the minimum weighted norm interpolation solution to the kernel-induced solution is formally discussed in recent work (\citealt{li2020generalization}).
 
-That is, in the case of the specific example of weight function $f(\omega)$ given in equation \eqref{eq:f}, we can connect our feature-weighted OLS to an equivalent GP if we know the Fourier transform of the square of $f(\omega)$.
+In the case of the specific example of weight function $f(\omega)$ given in equation \eqref{eq:f}, we can connect our feature-weighted OLS to an equivalent GP if we know the Fourier transform of the square of $f(\omega)$.
 We chose that specific form for $f(\omega)$ because it has a square that is a member of a Fourier-transform pair:
@@
 \end{equation}
-As before, in contexts where you have independent uncertainties on each element $y_i$ of your training data $Y$, $C^{-1}$ would naturally be set to the diagonal matrix containing the inverses of the variances of those uncertainties (so $C$ would contain the variances).
+As before, in contexts where we have independent uncertainties on each element $y_i$ of our training data $Y$, $C^{-1}$ would naturally be set to the diagonal matrix containing the inverses of the variances of those uncertainties (so $C$ would contain the variances).
 This form \eqref{eq:gpC} is used a lot in astronomy and cosmology (for example, \citealt{zaroubi}, \citealt{aigrain}, \citealt{celerite}) and it is also the standard form given for the Wiener filter, where the kernel function generating $K$ is the Fourier transform of the ``signal power'' and the kernel function generating $C$ is the Fourier transform of the ``noise power''.
@@
 
-Often you need to compute not just a prediction, but also an uncertainty on that prediction.
-How faithfully you must compute that uncertainty will depend strongly on the context in which you are doing the fitting or interpolation.
+Often we need to compute not just a prediction, but also an uncertainty on that prediction.
+How faithfully we must compute that uncertainty will depend strongly on the context in which we are doing the fitting or interpolation.
 However, it is often the case in the physical sciences that predictions are required to come with good or conservative estimates of uncertainty.
-There are four-ish sources of uncertainty in the predictions you are making in problems like these:
-(1)~The data points $y_i$ you have are individually noisy.
-(2)~There are finitely many of those data points (there are $n$ of them) and there are gaps between them in the location space $t$.
-(3)~The data points might have uncertain locations or location measurements $t_i$.
-(4)~And the predictions you make depend on hyper-parameter choices, such as the form of the basis, the number of parameters $p$, and any regularization or feature weighting.
+There are four-ish sources of uncertainty in the predictions we are making in problems like these:
+(A)~The data points $y_i$ we have are individually noisy.
+(B)~There are finitely many of those data points (there are $n$ of them) and there are gaps between them in the location space $t$.
+(C)~The data points might have uncertain locations or location measurements $t_i$.
+(D)~And the predictions we make depend on hyper-parameter choices, such as the form of the basis, the number of parameters $p$, and any regularization or feature weighting.
 These four different sources of uncertainty propagate differently and are differently ``simple'' to deal with.
-In particular it turns out that the easiest sources of uncertainty to understand and propagate are those coming from (1)~the noise in the $y_i$ and (2)~the number $n$ and locations $t_i$ of the data.
-The uncertainties coming from (3)~uncertainties in the locations $t_i$, and (4)~model choices, are both much harder to model and propagate.
+In particular it turns out that the easiest sources of uncertainty to understand and propagate are those coming from (A)~the noise in the $y_i$ and (B)~the number $n$ and locations $t_i$ of the data.
+The uncertainties coming from (C)~uncertainties in the locations $t_i$, and (D)~model choices, are both much harder to model and propagate.
 
-In the best-case scenario, you might have accurate estimates of the variances $[C]_{ii} = \sigma_i^2$ of the noise contributions affecting your training data values $y_i$, the noise might be Gaussian with zero mean, you might have locations $t_i$ that are extremely accurately known, and you might have justifiable prior variances $[\Lambda^{-1}]_{jj}$ on your parameters $\beta_j$.
-In this case, you can assume that the linear model with $p$ parameters is a good model for your data, and write down a likelihood function and a prior.
-In this case, you can turn the Bayesian crank and deliver a posterior density for the predicted values $Y_\ast$ at the test locations $t_\ast$.
-The second derivative of the natural logarithm of the posterior density can then be processed into a standard error on the predictions $\hat{Y}_\ast$ (or you can deliver full posterior densities somehow).
+In the best-case scenario, we might have accurate estimates of the variances $[C]_{ii} = \sigma_i^2$ of the noise contributions affecting our training data values $y_i$, the noise might be Gaussian with zero mean, we might have locations $t_i$ that are extremely accurately known, and we might have justifiable prior variances $[\Lambda^{-1}]_{jj}$ on our parameters $\beta_j$.
+In this case, we can assume that the linear model with $p$ parameters is a good model for our data, and write down a likelihood function and a prior.
+In this case, we can turn the Bayesian crank and deliver a posterior density for the predicted values $Y_\ast$ at the test locations $t_\ast$.
+The second derivative of the natural logarithm of the posterior density can then be processed into a standard error on the predictions $\hat{Y}_\ast$ (or we can deliver full posterior densities somehow).
 The details of this are way beyond the scope of this \documentname, but this (or a closely related) problem is discussed in some detail by us elsewhere (\citealt{products}).
@@
 That scenario is best-case, but it does involve a lot of assumptions.
-That is, if you don't trust your estimates of the noise variances, or if you think the noise might be non-Gaussian, then the likelihood approaches will give poor uncertainty estimates.
+That is, if we don't trust our estimates of the noise variances, or if we think the noise might be non-Gaussian, then the likelihood approaches will give poor uncertainty estimates.
 In this sense, it is more conservative to make use of more empirical methods for uncertainty estimation.
@@
 where $\hat{Y}_{\ast i}$ is the estimate of $Y_\ast$ made after \emph{leaving out} the one training point $t_i, y_i$, and $\hat{Y}_\ast$ is the estimate made using \emph{all} the data.
-The pre-factor $(n-1)/n$ in \eqref{eq:jackknife} is not anything like the $1/(n-1)$ that you use when you estimate a standard variance; this difference comes from the fact that the jackknife subsamples are extremely correlated; the pre-factor is computed to amplify the jackknife variance into an unbiased estimate of the variance of the estimator $\hat{Y}_\ast$.
-The square-root of the trace of this uncertainty variance $\hat{\Sigma}$ (that is, what you might call the jackknife estimate of the standard error) is shown in \figurename~\ref{fig:uncertainty}.
+The pre-factor $(n-1)/n$ in \eqref{eq:jackknife} 
+%is not anything like the $1/(n-1)$ that we use when you estimate a standard variance; this difference 
+comes from the fact that the jackknife subsamples are extremely correlated; the pre-factor is computed to amplify the jackknife variance into an unbiased estimate of the variance of the estimator $\hat{Y}_\ast$.
+The square-root of the trace of this uncertainty variance $\hat{\Sigma}$ (that is, what we might call the jackknife estimate of the standard error) is shown in \figurename~\ref{fig:uncertainty}.
 Note the similarity between jackknife and cross-validation; it is relevant and important: These empirical estimates of uncertainty and prediction error are closely related.
@@
 
-These methods---full likelihood analysis and jackknife---take into account (1)~the noise in the data $y_i$ and (2)~the number and spacing of the training data points.
-They do not, by themselves, take into account (3)~the uncertainties on the locations $t_i$.
+These methods---full likelihood analysis and jackknife---take into account (A)~the noise in the data $y_i$ and (B)~the number and spacing of the training data points.
+They do not, by themselves, take into account (C)~the uncertainties on the locations $t_i$.
 There are no simple methods for uncertainty propagation from the locations $t_i$ into the predictions $\hat{Y}_\ast$.
-One option is to resample the $t_i$ according to your uncertainty estimates, and re-do the fits.
+One option is to resample the $t_i$ according to our uncertainty estimates, and re-do the fits.
 That's potentially expensive, and overly conservative (because it ignores the information about the $t_i$ coming from the $y_i$).
@@
 
-Finally, in order to take account of (4)~the uncertainty coming from your choices of basis, number $p$, and regularization, you might have to know (or learn) the distribution over \emph{these} things.
+Finally, in order to take account of (D)~the uncertainty coming from our choices of basis, number $p$, and regularization, we might have to know (or learn) the distribution over \emph{these} things.
 Since these choices are hyper-parameters, any inference that propagates uncertainties coming from these choices would have to be hierarchical in structure.
-That is way, way out of scope.
+That is also out of scope.
 
@@
 The condition number, for our purposes, is the ratio of the largest eigenvalue (for non-negative definite matrices) to the smallest \emph{non-zero} eigenvalue.
-For rectangular feature matrices it is the ratio of the largest singular value (that is, what you get out of a singular value decomposition) to the smallest nonzero singular value.
+For rectangular feature matrices it is the ratio of the largest singular value to the smallest nonzero singular value.
 
 When the condition number is large, different linear-algebra approaches will differ.
-For example, the function call \code{solve(A, b)} should give you the best estimate it can for the product $A^{-1}\,b$, whereas the function call \code{dot(inv(A), b)}, which is the same on paper, will give you the dot product between \code{b} and the best estimate that \code{inv()} can find for the inverse of \code{A}.
+For example, the function call \code{solve(A, b)} should give us the best estimate it can for the product $A^{-1}\,b$, whereas the function call \code{dot(inv(A), b)}, which is the same on paper, will give us the dot product between \code{b} and the best estimate that \code{inv()} can find for the inverse of \code{A}.
 When the condition number of $A$ is large, these two values can be very different, and the \code{solve()} will be better.\footnote{This claim contradicts what is stated in the abstract of \citet{solve}, but this claim is based on our real numerical experiments on real matrices, so we stand by it.
 What is uncontroversial is that \code{solve(A, b)} will always perform non-worse than \code{dot(inv(A), b)}; sometimes it will perform far better.}
-Use \code{solve(A, b)} and never \code{dot(inv(A), b)} unless there are compelling code-structure reasons to use the latter, such as repeated calls (but even then, a Cholesky decomposition followed by repeated Cholesky solves is probably a more stable solution).
+We recommend to use \code{solve(A, b)} and never \code{dot(inv(A), b)} unless there are compelling code-structure reasons to use the latter, such as repeated calls (but even then, a Cholesky decomposition followed by repeated Cholesky solves is probably a more stable solution).
 
-If your condition number gets very large, even \code{solve()} can give bad results, because very small eigenvalues of the matrix are being poorly estimated and then inverted.
+If our condition number gets very large, even \code{solve()} can give bad results, because very small eigenvalues of the matrix are being poorly estimated and then inverted.
 That's unstable.
 It is better to zero out those small eigenvalues---it is better to destroy bad information than to use it---and perform a pseudo-inverse in those cases.
-So if you really want to be safe (and you do, here) you should really use \code{lstsq(A, b, rcond=tiny)} instead of \code{solve(A, b)}.
+So if we really want to be safe (and we do, here) we should really use \code{lstsq(A, b, rcond=tiny)} instead of \code{solve(A, b)}.
 The \code{lstsq()} function requires a \code{rcond} input, which says at what (dimensionless) precision to zero-out low eigenvalues.
@@
 
-You might think that all of this is academic, but it really isn't when the number of features $p$ is close to the number of data points $n$.
+One might think that all of this is academic, but it really isn't when the number of features $p$ is close to the number of data points $n$.
 For example, in our toy-data OLS experiments in this paper with $n=23$, the matrix $X^\top X$ has a condition number (ratio of largest eigenvalue to smallest nonzero eigenvalue) that saturates machine precision for the entire range $12 < p < 50$.
@@
 
-Related to this, if you have a choice between formulations that involve an inverse of a square, like $(X^\top X)^{-1}\,X^\top Y$, and formulations that involve a pseudo-inverse, like $X^\dagger\,Y$, you should do the latter, because $X^\top X$ has the \emph{square} of the condition number of $X$.
-When you want to execute $X^\dagger\,Y$, as we do in \eqref{eq:OLS3}, you should again use \code{lstsq()}, which was literally designed for these applications; use \code{lstsq(X, Y, rcond=tiny)}.
+Related to this, if we have a choice between formulations that involve an inverse of a square, like $(X^\top X)^{-1}\,X^\top Y$, and formulations that involve a pseudo-inverse, like $X^\dagger\,Y$, you should do the latter, because $X^\top X$ has the \emph{square} of the condition number of $X$.
+When we want to execute $X^\dagger\,Y$, as we do in \eqref{eq:OLS3}, we should again use \code{lstsq()}, which was literally designed for these applications; we use \code{lstsq(X, Y, rcond=tiny)}.
 This function returns the best estimate it can for $X^\dagger\,Y$, so
@@
 
-Once $p$ is large enough, if you are using a feature weighting with $\Lambda^{-1}$ with diagonal entries $[\Lambda^{-1}]_{jj}$ that decrease to zero with $j$, at some point, at machine precision, the additional columns you are adding to $X$ are effectively all zeros.
+Once $p$ is large enough, if we are using a feature weighting with $\Lambda^{-1}$ with diagonal entries $[\Lambda^{-1}]_{jj}$ that decrease to zero with $j$, at some point, at machine precision, the additional columns we are adding to $X$ are effectively all zeros.
 They will literally underflow the linear-algebra representation.
-That's not a problem if you implement your linear algebra well (that is, use \code{lstsq()} appropriately), but it does mean that your predictions and cross-validations will saturate at some $p$ (as we see them do in \figurename~\ref{fig:cv}).
+That's not a problem if we implement our linear algebra well (that is, use \code{lstsq()} appropriately), but it does mean that our predictions and cross-validations will saturate at some $p$ (as we see them do in \figurename~\ref{fig:cv}).
 
-In multiple places, but especially \eqref{eq:LambdaC1} and \eqref{eq:LambdaC2}, you are performing operations on matrices that are diagonal ($C$ and $\Lambda$ and their inverses are all diagonal).
-You should avoid ever constructing diagonal matrices.
-You can multiply $X$ or $X^\top$ by a diagonal matrix by just multiplying the rows (or columns) by the diagonal entries.
-And you can invert by just inverting the diagonal entries.
-Avoid constructing and operating on operators that are almost entirely zeros, unless you have a very efficient sparse linear algebra implementation and you are a power user.
+In multiple places, but especially \eqref{eq:LambdaC1} and \eqref{eq:LambdaC2}, we are performing operations on matrices that are diagonal ($C$ and $\Lambda$ and their inverses are all diagonal).
+We avoid ever constructing diagonal matrices.
+We multiply $X$ or $X^\top$ by a diagonal matrix by just multiplying the rows (or columns) by the diagonal entries.
+And we invert by just inverting the diagonal entries.
+We recommend to avoid constructing and operating on operators that are almost entirely zeros, unless we are using a very efficient sparse linear algebra implementation.
 
-And finally, it is most numerically stable to operate on the smallest matrices you can.
-For example, when you have the choice between the formulation in equation \eqref{eq:LambdaC1} and that in equation \eqref{eq:LambdaC2}, you should choose the former when $p<n$ and the latter when $p>n$.
-That way you are always doing the heavy linear algebra (\code{solve()} and \code{lstsq()} function calls) at a size $\min(p, n)$, which is both faster and more stable than linear algebra at $\max(p, n)$.
-And it is much faster when you make these choices correctly:
+And finally, it is most numerically stable to operate on the smallest matrices we can.
+For example, when you have the choice between the formulation in equation \eqref{eq:LambdaC1} and that in equation \eqref{eq:LambdaC2}, we should choose the former when $p<n$ and the latter when $p>n$.
+That way we are always doing the heavy linear algebra (\code{solve()} and \code{lstsq()} function calls) at a size $\min(p, n)$, which is both faster and more stable than linear algebra at $\max(p, n)$.
+And it is much faster when we make these choices correctly:
 Linear algebra scales naively as the dimension \emph{cubed}.
@@
 This \documentname\ is about linear fitting with very flexible models, for interpolation, prediction, and de-noising of data.
-We have encouraged you to consider using very big models, but being intentional about regularization.
+We make a case for considering using very big models, but being intentional about regularization.
 These settings (over-parameterized, but carefully regularized) are adaptive and useful, and they connect, as we showed, to Gaussian processes in the limit, which are well-studied workhorses of machine learning and data science.
 
-All the rage these days, is instead \emph{nonlinear fitting}, with \emph{deep learning} and the like (\citealt{deep}, for example).
-We didn't discuss any of that.
+At the present day, most important regression techniques involve \emph{nonlinear fitting}, with the key example being \emph{deep learning} (\citealt{deep}, for example).
+We did not discuss any of that.
 However, many of the high-level lessons in this \documentname\ carry over:
-All of these tools work well when the function space is flexible but also carefully regularized.
+All of these tools work well when the function space is flexible but also carefully regularized (\citealt{belkin2019reconciling}).
 In these nonlinear settings, regularization takes many additional new forms, like early stopping (\citealt{earlystop}), dropout (\citealt{dropout}), and restricted network structure (such as convolutional; see for example \citealt{bishop}).
 
-We only considered the setting in which you care about predicting new data $Y_\ast$ and never the setting in which you care about the internal parameters $\beta$ of the linear fit.
-However, if you are, say, measuring the power spectrum of a process (as we are, often, in cosmology), then you care about these amplitudes themselves.
-In this case, any regularization you apply takes the role of a prior or prior information.
-That prior must be chosen (in those cases) with great care, because the answers you get will be influenced by that choice; when it doesn't properly conform to your true beliefs, your answers will be distorted in bad ways.
-And, technically, when you take this view (that the parameters $\beta$ matter), you also have to get serious about the noise model on the data.
-That is, the beliefs encoded in the data noise variance tensor $C$ also must represent your true beliefs if you don't want your answers distorted in bad ways.
+We only considered the setting in which we care about predicting new data $Y_\ast$ and never the setting in which we care about the internal parameters $\beta$ of the linear fit.
+However, if we are, say, measuring the power spectrum of a process (as we are, often, in cosmology), then we care about these amplitudes themselves.
+In this case, any regularization we apply takes the role of a prior or prior information.
+That prior must be chosen (in those cases) with great care, because the answers we get will be influenced by that choice; when it doesn't properly conform to our true beliefs, our answers will be distorted in bad ways.
+And, technically, when we take this view (that the parameters $\beta$ matter), we also have to get serious about the noise model on the data.
+That is, the beliefs encoded in the data noise variance tensor $C$ also must represent our true beliefs if we don't want our answers distorted in bad ways.
 All of that is out of scope here, but we say things about it all elsewhere (for example, \citealt{fitting}).
@@
 A model that generates both can be used to make predictions $y_\ast$ at new locations $t_\ast$ by executing an inference or inverse problem on the generative model.
-Generative models are generally non-convex---and harder to execute---if you want the relationship between the $t_i$ and the $y_i$ to be nonlinear (for an example of this in astronomy, see, for example, \citealt{thecannon}).
-In these cases you don't get closed-form solutions, and there aren't known guarantees (like the Gauss--Markov theorem) about performance.
+Generative models are generally non-convex---and harder to execute---if we want the relationship between the $t_i$ and the $y_i$ to be nonlinear (for an example of this in astronomy, see, for example, \citealt{thecannon}).
+In these cases we don't get closed-form solutions, and there aren't known guarantees (like the Gauss--Markov theorem) about performance.
 But they are more general, and often more appropriate, especially when both the locations $t_i$ and the data $y_i$ are comparably noisy measurements.
@@
 However, \emph{it is often a great choice}.
-When you choose the Fourier basis (and---importantly---for every cosine term you include the corresponding sine term), the matrix $X\,\Lambda^{-1}\,X^\top$ (and the limiting kernel matrix $K$ at $p\to\infty$) has the property that every matrix element $[X\,\Lambda^{-1}\,X^\top]_{ii'}$ depends on (or can be calculated from) just the absolute difference $|t_i-t_{i'}|$.
+When we choose the Fourier basis (and---importantly---for every cosine term you include the corresponding sine term), the matrix $X\,\Lambda^{-1}\,X^\top$ (and the limiting kernel matrix $K$ at $p\to\infty$) has the property that every matrix element $[X\,\Lambda^{-1}\,X^\top]_{ii'}$ depends on (or can be calculated from) just the absolute difference $|t_i-t_{i'}|$.
 That is, in this basis, all fitting methods become technically \emph{stationary}.
 This all relates to the translation-independence properties of the Fourier basis.
-So although the Fourier basis is just one choice among many, it is the \emph{right choice} when you think your problem has (or might have) certain kinds of translation invariances.
+So although the Fourier basis is just one choice among many, it is the \emph{right choice} when we think our problem has (or might have) certain kinds of translation invariances.
 
 % end matter
-
-{\raggedright
-\setlength{\bibsep}{0pt plus 0.3ex} % trust in Hogg
-\bibliographystyle{authordate1}
-\bibliography{references}
-}
+\paragraph{Acknowledgements:}
+It is a pleasure to thank
+Viviana Acquaviva (CUNY),
+Jed Brown (CU Boulder),
+Edgar Dobriban (UPenn),
+Nestor Espinoza (STScI),
+Dan Foreman-Mackey (Flatiron),
+Alessandro Gentilini,
+Teresa Huang (JHU),
+Weilin Li (NYU),
+Sam Roweis (deceased),
+Adrian Price-Whelan (Flatiron),
+Bernhard Sch\"olkopf (MPI-IS),
+Kate Storey-Fisher (NYU),
+Rachel Ward (UT Austin), and
+Lily Zhao (Yale)
+for valuable conversations and input.
+SV's work on this project was supported by NSF DMS 2044349, EOARD FA9550-18-1-7007, and the NSF--Simons Research Collaboration on the Mathematical and Scientific Foundations of Deep Learning (MoDL) (NSF DMS-2031985).
+All code and data used in this project are available at
+\url{https://github.com/davidwhogg/FlexibleLinearModels}.
 
@@
 
-\section*{Declarations}
-This section completes requirements for submission to \textit{EPJ Data Science}.
-
-\paragraph{Availability of data and materials:}
-All code and data used in this project are available at
-\url{https://github.com/davidwhogg/FlexibleLinearModels}
-
-\paragraph{Competing interests:}
-Does not apply.
-
-\paragraph{Funding:}
-DWH's work on this project was supported by the Flatiron Institute, a division of the Simons Foundation.
-SV's work on this project was supported by NSF DMS 2044349, EOARD FA9550-18-1-7007, and the NSF--Simons Research Collaboration on the Mathematical and Scientific Foundations of Deep Learning (MoDL) (NSF DMS-2031985).
-
-\paragraph{Authors' contributions:}
-The two authors contributed equally to the analysis and writing represented in this work.
-
-\paragraph{Acknowledgements:}
-It is a pleasure to thank
-Jed Brown (CU Boulder),
-Nestor Espinoza (STScI),
-Dan Foreman-Mackey (Flatiron),
-Alessandro Gentilini,
-Teresa Huang (JHU),
-Sam Roweis (deceased),
-Adrian Price-Whelan (Flatiron),
-Bernhard Sch\"olkopf (MPI-IS),
-Kate Storey-Fisher (NYU),
-Rachel Ward (UT Austin), and
-Lily Zhao (Yale)
-for valuable conversations and input.
+{\raggedright
+\setlength{\bibsep}{0pt plus 0.3ex} % trust in Hogg
+\bibliographystyle{authordate1}
+\bibliography{references}
+}
 

### 2021-08-20 paper/response_reviewers.tex
referee comments

\documentclass{amsart}
\title{Fitting very flexible models \\
Response to reviewer}
\author{David W. Hogg and Soledad Villar}
\begin{document}
\maketitle

\textbf{Editor comment:} The referee for your article has provided a very thorough, and rather glowing, review of your excellent tutorial.  As you can see from the referee's comments, the referee has a few recommendations, that are largely of a minor nature, that we would like for you to consider within a revised version of your very informative and useful tutorial.

\textbf{Response:} We thank the reviewer and the editor for the kind comments about our manuscript and the improvement suggestions. We are submitting a revision addressing the suggested changes:
\begin{itemize}
    \item Added a comment on fast implementations of GPs and why one may not always be able to use them. HOGG
    \item Changed the color scheme in many of the figures to make the lines more distinguishable. SOLEDAD
    \item Added a short paragraph discussing jacknife given correlated noise. HOGG
    \item Added a comment about the equivalence of different formulations. HOGG
    \item Fixed typos.
\end{itemize}

\textbf{Reviewer comments:}
``Fitting very flexible models" by Hogg and Villar is an excellent tutorial on the use of linear models for interpolating data. The tutorial is well written, with clear language and mathematics that is not too difficult to follow (I especially commend the authors on building from simple OLS matrix equations to the more complex equations towards the end of the paper without the need for the reader to fill in many of the intermediate steps, as should be the case in a tutorial). The tutorial is accompanied by clear figures and the software used to generate the data and figures is publicly available. In sum, I am grateful that this article exists as I will certainly have research associates read it and implement its methods, and I anticipate building future lectures for classes on the material.

I recommend this tutorial for publication in PASP. In my opinion, it is suitable for publication as is, however, I have a few comments (mostly minor) and one (philosophical?) question that the authors may wish to consider before sending a resubmission.

MAJOR COMMENTS
--------------

  In addition to serving as a tutorial, the article (in my opinion) implores the reader to consider regularized least-squares fitting as a means of interpolating data. I find the arguments convincing. However, the authors also show that the methods described here reproduce a Gaussian process in the limit p goes to infinity. My question: with relatively fast implementations of GPs now available (such as those developed by Foreman-Mackey and collaborators, which the authors cite) – should readers be encouraged to use $O(n^3)$ methods when GPs can be implemented with faster calculations [at least in the 1d case that makes the bulk of this tutorial]?

\textbf{Response:} Thank your for your kind assessment of our work. We agree with your point of view regarding taking advantage of fast algorithms for GPs. Faster algorithms are preferable if available. However, the very fast Gaussian Process is only known for certain kernels and only in 1-dimension. In some cases you may want to use other basis like wavelet basis, or work in higher dimensions, like the sphere. To the best of our knowledge there is no fast implementation of GPs in the sphere. The regularized regression is a general framework.

We made a comment in the end of Section 7 of our manuscript stating this point.

\bigskip

\textbf{Reviewer comments:}
MINOR COMMENTS
--------------

  In Figure 5 the black and purple lines are difficult to distinguish. I would consider alternate colors, or, better yet different line styles to more easily identify the p = 30 and p = 73 curves.

\textbf{Response:} We changed the color scheme so the lines are distinguishable when printed in black and white.
 \bigskip

 \textbf{Reviewer comments:}
   Section 4 begins by refuting the commonly held belief that the number of parameters cannot exceed the number of data points. This (incorrect) folklore is taught because introductory statistics typically ascribes meaning to all the parameters in a model. While early exposure to nuisance parameters would likely benefit our field, the idea is complex and harder to understand than the slope of this line is equal to the gravitational constant. (Now I'm rambling) my point: $p > n$ only works well when meaning is not be ascribed to the parameters. Perhaps it is worth a footnote here to remind the reader of that point? Or perhaps not?

   \textbf{Response:} We agree with this comment and we modified the first paragraph of Section 4 to address it.

  \bigskip
 \textbf{Reviewer comments: }
   Eq 13 and 18 are equivalent (I believe), and this becomes clear from Eq. 23 and 24. Nevertheless I found the differing forms of 13 and 18 confusing the first couple of times I read through the text. It might be useful to add a note in the text or a footnote to Eq 18 stating that it is the same as Eq 13.

 \textbf{Response:} We added a sentence about the equivalence of equations after equation 18.

 \bigskip
  \textbf{Reviewer comments:} There are sigma hat's in Sect 8 that are missing their $*$

   \textbf{Response:} Fixed

 \bigskip
 \textbf{Reviewer comments:}
  Timeseries data, which the authors subtly suggest these methods are useful for by adopting $t_i$ instead of $x_i$, are often correlated over length scales that are larger than the typical separation between the observations. In this case, k=n jackknife estimates of the uncertainty are likely to underestimate the uncertainties in data gaps that are larger than the typical correlation length (which is a common occurrence in astronomical data). The authors may wish to add a note warning the reader about this.

 \textbf{Response:}
 This is a good point. We added a short paragraph about that in the relevant place.

\end{document}

### 2021-08-20 paper/main.tex
referee comments

@@
 % -----
-% - HOGG: Finish going through Acquaviva comments and incorporate / assess.
-% - BOTH: Take one more look through the abstract (and title) and see what needs to be adjusted.
-% - HOGG. It is a kernel even when p \ne \infty! Re-word stuff in section 7.
 % - Should we do a CVMSE vs the s parameter to show that you can choose kernel parameters by CV as well? Let's start by performing an experiment in the notebook. Not for now.
+% - Should we cite more in the regularized and compressed-sensing contexts?
+% - Should we be more explicit about what goes wrong at high dimensions?
+% - Be careful to make it make it clear that we consider cross-validation to be the only empirical method to understand overfitting; check the words we write about over-fitting to match.
+It isn't just about the number of parameters.
 
@@
 
-\paragraph{Abstract:} There are many uses for linear fitting; we consider here the interpolation and denoising of data, as when the goal is to fit a smooth, flexible function to a set of noisy data points.
+\paragraph{Abstract:}
+There are many uses for linear fitting; we consider here the interpolation and denoising of data, as when the goal is to fit a smooth, flexible function to a set of noisy data points.
 Investigators often choose a polynomial basis, or a Fourier basis, or wavelets, or something equally general.
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{./OLS-under.pdf}
+    \includegraphics[width=\figurewidth]{./OLS-under (1).pdf}
     \caption{Ordinary least-squares (OLS) fits (continuous lines) to a set of example data points (black dots).
@@
 The ridge-regularized prediction for new data looks like
-\begin{equation} \label{eq:ridge_sol}
+\begin{equation}\label{eq:ridge_sol}
     \hat{Y}_\ast = X_\ast\,(X^\top X + \lambda\,I)^{-1}\,X^\top Y
@@
 \section{Over-parameterization}\label{sec:overpar}
-
 We are taught folklore, that we can never fit for more parameters than we have data. That is, we can never work at $p>n$.
@@
 Not only is it the case that we \emph{can} work at $p>n$, in many cases we \emph{should} work at $p>n$, and many real-world regressions do.
-But it is true that the $p>n$ regime is indeed strange.
 In the over-parameterized case, there are typically many choices for the parameters $\beta_j$ that will literally zero out the differences between the data $Y$ and the linear prediction $X\,\beta$.
+In the introduction we said that we are considering the case of linear regression in which \emph{we don't care about the values of the parameters}.
+That is, the parameters of our linear fits are just nuisance parameters.
+This means that we don't have very detailed opinions about how these redundancies in the model (redundancies that appear when $p>n$) are resolved.
 The OLS solution, in this case, is defined (somewhat arbitrarily) to be the minimum-norm parameter vector $\beta$ that interpolates the data:
@@
     \begin{mdframed}
-    \includegraphics[width=\figurewidth]{./OLS-over.pdf}
+    \includegraphics[width=\figurewidth]{./OLS-over (1).pdf}
     \caption{Ordinary least-squares (OLS) or min-norm least-squares fits (continuous lines) to a set of example data points (black dots), but now for a few over-parameterized cases.
@@
 \end{equation}
-This can be seen as the prediction for new data resulting from the following optimization (again, assuming the data can be interpolated):
+This equation is a special case of the fully general form we will give below in \eqref{eq:LambdaC2}, and equivalent to a special case of \eqref{eq:foo} above.
+This \eqref{eq:weighted_sol} can be seen as the prediction for new data resulting from the following optimization (again, assuming the data can be interpolated):
 \begin{equation} \label{eq:weighted}
@@
 
+We remark that a naive implementation of the regularized regression using \eqref{eq:gpC} has an $O(n^3)$ time complexity.
+However, Gaussian processes can be implemented in something close to $O(n)$ for certain classes of one-dimensional models (\citealt{ambikasaran2015fast, celerite}).
+Given this, you might ask: Why use $O(n^3)$ feature-weighted over-parameterized regressions when you could just use a fast GP?
+Unfortunately there are not algorithms that are so fast for higher dimensional GPs, and there are no good algorithms at all for many situations (for example GPs on the surface of a sphere).
+Furthermore, the standard GP implementations focus on stationary GPs, which do not encompass all the options that one might construct with non-stationary basis functions.
+Given all this, it is often the case that one should or must use linear-regression frameworks, when appropriate GPs are not available.
+
 \section{Uncertainties on the predictions}\label{sec:uncertainty}
@@
 comes from the fact that the jackknife subsamples are extremely correlated; the pre-factor is computed to amplify the jackknife variance into an unbiased estimate of the variance of the estimator $\hat{Y}_\ast$.
-The square-root of the trace of this uncertainty variance $\hat{\Sigma}$ (that is, what we might call the jackknife estimate of the standard error) is shown in \figurename~\ref{fig:uncertainty}.
+The square-root of the trace of this uncertainty variance $\hat{\Sigma}_\ast$ (that is, what we might call the jackknife estimate of the standard error) is shown in \figurename~\ref{fig:uncertainty}.
 Note the similarity between jackknife and cross-validation; it is relevant and important: These empirical estimates of uncertainty and prediction error are closely related.
@@
     \caption{The jackknife-estimated uncertainty on an ordinary least squares fit.
-What is shown is the diagonal of the empirical jackknife estimate $\hat{\Sigma}$ of the variance tensor on the prediction $\hat{Y}_\ast$ of an OLS fit.
+What is shown is the diagonal of the empirical jackknife estimate $\hat{\Sigma}_\ast$ of the variance tensor on the prediction $\hat{Y}_\ast$ of an OLS fit.
 In other words, the off-diagonal entries of $\hat{\Sigma}_\ast$ are being ignored here; there are important covariances that are hard to visualize (and beyond our scope).
@@
 \end{figure}
+
+DAVID HOGG: write a couple of sentences about correlated timeseries as per refereee.
 
@@
 For instance, if $A$ has full row rank and $Z$ is the nullspace of $A$, if $Z^\top G\, Z$ is positive semidefinite the KKT conditions are sufficient for optimality.
-If $Z^\top G\, Z$ is positive definite we also have that the solution of \eqref{qp} is unique (which is typically the case in the underparameterized linear regression but not in the overparameterized).}
+If $Z^\top G\, Z$ is positive definite we also have that the solution of \eqref{qp} is unique (which is typically the case in the under-parameterized linear regression but not in the over-parameterized).}
 
